### 2018-05-17 Report/notes.tex
this is the first commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Example: Project Report
%
% Source: http://www.howtotex.com
%
% Feel free to distribute this example, but please keep the referral
% to howtotex.com
% Date: March 2011 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edit the title below to update the display in My Documents
%\title{Project Report}
%
%%% Preamble
\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
%\usepackage{fourier}

\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}	
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}	
\usepackage{url}

%%% Custom sectioning
\usepackage{sectsty}
\allsectionsfont{\centering \normalfont\scshape}
\usepackage{tikz}
\usetikzlibrary{chains,shapes.multipart}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

%%% Custom headers/footers (fancyhdr package)
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhead{}											% No page header
\fancyfoot[L]{}											% Empty 
\fancyfoot[C]{}											% Empty
\fancyfoot[R]{\thepage}									% Pagenumbering
\renewcommand{\headrulewidth}{0pt}			% Remove header underlines
\renewcommand{\footrulewidth}{0pt}				% Remove footer underlines
\setlength{\headheight}{13.6pt}

%%% Equation and float numbering
\numberwithin{equation}{section}		% Equationnumbering: section.eq#
\numberwithin{figure}{section}			% Figurenumbering: section.fig#
\numberwithin{table}{section}				% Tablenumbering: section.tab#

%%% Maketitle metadata
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} 	% Horizontal rule

\title{
		%\vspace{-1in} 	
		\usefont{OT1}{bch}{b}{n}
		\normalfont \normalsize \textsc{School of random department names} \\ [25pt]
		\horrule{0.5pt} \\[0.4cm]
		\huge This is the title of the template report \\
		\horrule{2pt} \\[0.5cm]
}
\author{
		\normalfont 								\normalsize
        Firstname Lastname\\[-3pt]		\normalsize
        \today
}
\date{}

%%% Begin document
\begin{document}
\maketitle
\begin{abstract}
	The subject of this internship is first modeling some system  in the PrismGSMP. That is a continuous system with rates instead of probabilistic transition. Transitiom are syncronized with event which follows some probabilistic laws like exponential law or dirac. One good property about the exponenial law is the events are markovian. That is the probability of the event of happening doenst depends on the time already spend.

\end{abstract}
\section{Queue : A toy example}
We considere a M/M/1/n queue (see Kendall notation). 
put some figure here

first model:

\begin{tikzpicture}[start chain=going right,>=latex,node distance=0pt]
% the rectangular shape with vertical lines
\node[rectangle split, rectangle split parts=6,
draw, rectangle split horizontal,text height=1cm,text depth=0.5cm,on chain,inner ysep=0pt] (wa) {};
\fill[white] ([xshift=-\pgflinewidth,yshift=-\pgflinewidth]wa.north west) rectangle ([xshift=-15pt,yshift=\pgflinewidth]wa.south);

% the circle
\node[draw,circle,on chain,minimum size=1.5cm] (se) {$\mu$};

% the arrows and labels
\draw[->] (se.east) -- +(20pt,0);
\draw[<-] (wa.west) -- +(-20pt,0) node[left] {$\lambda$};
\node[align=center,below] at (wa.south) {Producing \\ Area};
\node[align=center,below] at (se.south) {Consume};
\end{tikzpicture}

\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm,
                    semithick]
  \tikzstyle{every state}=[fill=red,draw=none,text=white]

  \node[initial,state] (s0)                    {$0$};
  \node[state]         (s1) [right of=s0] {$1$};
  \node[state]         (s2) [right of=s1] {$2$};
  \node[state]         (s3) [right of=s2] {$3$};
  \node[state]         (s4) [right of=s3]       {$4$};
  \node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
  \node[state]         (sn) [right of=sw]       {$n$};

  \path (s0) edge [bend left]             node {Dirac(t)} (s1)
        (s1) edge [bend left] node {$\lambda$} (s0)
            edge  [bend left]            node {Dirac(t)} (s2)
        (s2) edge [bend left]             node {$\lambda$} (s1)
            edge [bend left]  node {Dirac(t)} (s3)
        (s3) edge [bend left]              node {$\lambda$} (s2)
            edge [bend left]  node {Dirac(t)} (s4)
        (s4) edge [bend left]             node {$\lambda$} (s3)
            edge [bend left]  node {Dirac(t)} (sw)
        (sw) edge [bend left]             node {$\lambda$} (s4)
            edge [bend left]  node {Dirac(t)} (sn)
        (sn) edge [bend left]             node {$\lambda$} (sw);
\end{tikzpicture}

second model(using phase type fitting):

\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.5cm,
                    semithick]
  \tikzstyle{every state}=[fill=red,draw=none,text=white]

  \node[state] (s0)                    {$i$};
  \node[state] (s02) [right of=s0,fill=blue,scale=0.5]                   {};
  \node[state] (s03) [right of=s02,fill=blue,scale=0.5]                    {};
  \node[state] (s04) [right of=s03,fill=blue,scale=0.5]                   {};
  \node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
  \node[state] (s1) [right of=s05]                   {$i+1$};

  \path (s0) edge [bend left]             node {$\lambda_2$} (s02)
        (s02) edge [bend left] node {$\lambda$} (s0)
            edge  [bend left]            node {$\lambda_2$} (s03)
        (s03) edge [bend left]             node {$\lambda$} (s0)
            edge [bend left]  node {$\lambda_2$} (s04)
        (s04) edge [bend left]              node {$\lambda$} (s0)
            edge [bend left]  node {$\lambda_2$} (s05)
        (s05) edge [bend left]             node {$\lambda$} (s0)
            edge [bend left]  node {$\lambda_2$} (s1);

\end{tikzpicture}

\begin{align} 
	\begin{split}
	(x+y)^3 	&= (x+y)^2(x+y)\\
					&=(x^2+2xy+y^2)(x+y)\\
					&=(x^3+2x^2y+xy^2) + (x^2y+2xy^2+y^3)\\
					&=x^3+3x^2y+3xy^2+y^3
	\end{split}					
\end{align}
Phasellus viverra nulla ut metus varius laoreet. Quisque rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies

\subsection{Heading on level 2 (subsection)}
Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
\begin{align}
	A = 
	\begin{bmatrix}
	A_{11} & A_{21} \\
  	A_{21} & A_{22}
	\end{bmatrix}
\end{align}
Aenean commodo ligula eget dolor. Aenean massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec quam felis, ultricies nec, pellentesque eu, pretium quis, sem.

\subsubsection{Heading on level 3 (subsubsection)}
Nulla consequat massa quis enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer tincidunt. Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean leo ligula, porttitor eu, consequat vitae, eleifend ac, enim.

\paragraph{Heading on level 4 (paragraph)}
Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis enim.

\section{Lists}

\subsection{Example for list (3*itemize)}
\begin{itemize}
	\item First item in a list 
		\begin{itemize}
		\item First item in a list 
			\begin{itemize}
			\item First item in a list 
			\item Second item in a list 
			\end{itemize}
		\item Second item in a list 
		\end{itemize}
	\item Second item in a list 
\end{itemize}

\subsection{Example for list (enumerate)}
\begin{enumerate}
	\item First item in a list 
	\item Second item in a list 
	\item Third item in a list
\end{enumerate}
%%% End document
\end{document}\\

### 2018-05-17 Log/sum_line.sh

@@ -1,0 +1,1 @@
+awk '{s+=$1}NR%nb_line==0{print s;s=0}' file

### 2018-05-17 Prism_extract/cmd.sh

@@ -1,0 +1,2 @@
+mkdir ../results
+~/home/thomas/Documents/Stage_CZK/Prism_Gsmp/prism-gsmp/prism ../model/queue_withptf.sm steady_state_prop.pctl >../results/cud_nondet_prop_max.log

### 2018-05-17 Prism_extract/curves.py

@@ -1,0 +1,120 @@
+import matplotlib.pyplot as plt
+from array import array
+
+Nb_var = 50
+N = 1024
+logN = 10
+Hx1=1
+alpha = 0.5
+
+
+
+def curve_10():
+	plt.yscale('linear')
+	plt.xscale('linear')
+	plt.xlabel('time (min)', fontsize=14, color='black')
+	plt.ylabel('Probality', fontsize=14, color='black')
+	plt.title('Steady State Probability for a queue with phase type fitting parameter k')
+	x = range(0,11,1)
+	y_10 = [0.5000000826669286
+,0.39840613145837134
+,0.08095129548959867
+,0.016448323368837333
+,0.0033421012330050923
+,6.790753730597986E-4
+,1.3798015979630204E-4
+,2.8033117549421624E-5
+,5.682420643903797E-6
+,1.1194905967466665E-6
+,1.752216115764016E-7]
+	y_10_2 = [0.500014
+,0.309026
+,0.118037
+,0.0450863
+,0.0172215
+,0.00657809
+,0.00251269
+,0.000959917
+,0.000367035
+,0.000141172
+,5.64702e-05]
+	y_10_5 = [0.500001
+,0.358117
+,0.101622
+,0.028837
+,0.00818304
+,0.00232209
+,0.000658939
+,0.000186987
+,5.30691e-05
+,1.51282e-05
+,4.67613e-06
+]
+	y_10_10 = [0.5
+,0.37746
+,0.0925077
+,0.0226717
+,0.00555637
+,0.00136175
+,0.000333737
+,8.17913e-05
+,2.00432e-05
+,4.92029e-06
+,1.3328e-06]
+	y_10_50 = [0.500008
+,0.394084
+,0.0834748
+,0.0176817
+,0.00374534
+,0.000793339
+,0.000168045
+,3.55952e-05
+,7.53877e-06
+,1.59446e-06
+,3.77647e-07
+]
+	y_10_100 = [0.499981
+,0.396256
+,0.0822304
+,0.0170643
+,0.00354115
+,0.000734852
+,0.000152495
+,3.16453e-05
+,6.56616e-06
+,1.35994e-06
+,3.16008e-07
+]
+	y_10_200 = [0.50004
+,0.39729
+,0.0815864
+,0.0167544
+,0.00344064
+,0.000706561
+,0.000145098
+,2.97969e-05
+,6.11834e-06
[…]

### 2018-05-17 Report/notes.tex
add thing

@@
 \usepackage[T1]{fontenc}
-%\usepackage{fourier}
+\usepackage{fourier}
 
@@
 
+\usepackage{listings}
+\usepackage{color}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+	aboveskip=3mm,
+	belowskip=3mm,
+	showstringspaces=false,
+	columns=flexible,
+	basicstyle={\small\ttfamily\color{red}},
+	numbers=none,
+	numberstyle=\tiny\color{blue},
+	keywordstyle=\color{black},
+	commentstyle=\color{dkgreen},
+	breaklines=true,
+	breakatwhitespace=true,
+	tabsize=3,
+	morekeywords={\;,init,gsmp,dtmc, const, int, double, module, formula, endmodule,->,=} 
+}
 %%% Begin document
@@
 	\end{abstract}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%SECTION1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 	\section{Queue : A toy example}
 	We considere a M/M/1/n queue (see Kendall notation).
-put some figure here
 
-first model:
+	\subsection{first model}
 
+	\begin{figure}
+		\centering
 		\begin{tikzpicture}[start chain=going right,>=latex,node distance=0pt]
@@
 		\end{tikzpicture}
+		\caption{a queue}
+		\label{fig:queue0}
+	\end{figure}
 
-\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm,
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
 		semithick]
@@
 		\end{tikzpicture}
+		\caption{Queue with n capacity, the current size is written on the states}
+		\label{fig:Queue1}
+	\end{figure}
 
-second model(using phase type fitting):
+	\begin{figure}
+		\centering
+		\begin{lstlisting}
+		gsmp
 
-\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.5cm,
+		const int qCapacity = 10;
+
+		const double timeout = 10;
+		const double lambda = 0.2;
+
+		module main
+		event prod = dirac(timeout);
+
+		qSize : [0..qCapacity] init 0;
+
+		[produce] (qSize < qCapacity)--prod -> (qSize' = qSize+1);
+		[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);
+
+		endmodule
+		\end{lstlisting}
+		\caption{Prism code for figure \ref{fig:Queue1}}
+		\label{fig:queuecode1}
+	\end{figure}
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%SECTION2%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	\subsection{second model(using phase type fitting)}
+	The timeout part is replaced by $k$ $\mu$ transition following the exponential law of parameter $\mu$. Here on the figure, k=5, which mean that you need 5 consecutive $\mu$ transition to $produce$.
+
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
 		semithick]
@@
 		\node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
-  \node[state] (s1) [right of=s05]                   {$i+1$};
+		\node[state] (s1) [below of=s0]                   {$i+1$};
 
-  \path (s0) edge [bend left]             node {$\lambda_2$} (s02)
-        (s02) edge [bend left] node {$\lambda$} (s0)
-            edge  [bend left]            node {$\lambda_2$} (s03)
-        (s03) edge [bend left]             node {$\lambda$} (s0)
-            edge [bend left]  node {$\lambda_2$} (s04)
-        (s04) edge [bend left]              node {$\lambda$} (s0)
-            edge [bend left]  node {$\lambda_2$} (s05)
-        (s05) edge [bend left]             node {$\lambda$} (s0)
-            edge [bend left]  node {$\lambda_2$} (s1);
+		\node[state] (s12) [right of=s1,fill=blue,scale=0.5]                   {};
+		\node[state] (s13) [right of=s12,fill=blue,scale=0.5]                    {};
+		\node[state] (s14) [right of=s13,fill=blue,scale=0.5]                   {};
+		\node[state] (s15) [right of=s14,fill=blue,scale=0.5]                    {};
+		\node[state] (s2) [below of=s1]     {$i+2$};
 
+		\node[state] (sw0) [above of=s0,fill=white,text=black]        {...}            {};
+		\node[state] (sw1) [right of=s2,fill=white,text=black]       {...}             {};
+
+		\path (s0) edge   node {$\lambda$} (sw0)
+		edge   node {$\mu$} (s02)
+
+		(s02)   edge   node {$\lambda$} (sw0)
+		edge   node {$\mu$} (s03)
+		(s03)   edge  node {$\lambda$} (sw0)
+		edge   node {$\mu$} (s04)
+		(s04) edge  node {$\lambda$} (sw0)
+		edge   node {$\mu$} (s05)
+		(s05) edge  node {$\lambda$} (sw0)
+		edge   node {$\mu$} (s1)
+		(s1)    edge  node {$\lambda$} (s0)
+		edge   node {$\mu$} (s12)
+		(s12)   edge  node {$\lambda$} (s0)
+		edge   node {$\mu$} (s13)
+		(s13) edge  node {$\lambda$} (s0)
+		edge   node {$\mu$} (s14)
+		(s14) edge  node {$\lambda$} (s0)
+		edge   node {$\mu$} (s15)
+		(s15) edge  node {$\lambda$} (s0)
+		edge   node {$\mu$} (s2)
+		(s2) edge  node {$\lambda$} (s1)
+		edge   node {$\mu$} (sw1)    
+		(sw1) edge  node {$\lambda$} (s1);
 		\end{tikzpicture}
+		\caption{Queue with phase type fitting of parameter k}
+		\label{fig:queueptf1}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
+		semithick]
+		\tikzstyle{every state}=[fill=red,draw=none,text=white]
+
+		\node[state] (s0)                    {$i$};
+		\node[state] (s02) [right of=s0,fill=blue,scale=0.5]                   {};
+		\node[state] (s03) [right of=s02,fill=blue,scale=0.5]                    {};
+		\node[state] (s04) [right of=s03,fill=blue,scale=0.5]                   {};
+		\node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
+		\node[state] (s1) [below of=s0]                   {$i+1$};
+
+		\node[state] (s12) [right of=s1,fill=blue,scale=0.5]                   {};
+		\node[state] (s13) [right of=s12,fill=blue,scale=0.5]                    {};
+		\node[state] (s14) [right of=s13,fill=blue,scale=0.5]                   {};
+		\node[state] (s15) [right of=s14,fill=blue,scale=0.5]                    {};
+		\node[state] (s2) [below of=s1]     {$i+2$};
+
+		\node[state] (sw0) [above of=s0,fill=white,text=black]        {...}            {};
+		\node[state] (sw02) [right of=sw0,fill=white,text=black]        {...}            {};
+		\node[state] (sw03) [right of=sw02,fill=white,text=black]        {...}            {};
+		\node[state] (sw04) [right of=sw03,fill=white,text=black]        {...}            {};
+		\node[state] (sw05) [right of=sw04,fill=white,text=black]        {...}            {};
+		\node[state] (sw1) [right of=s2,fill=white,text=black]       {...}             {};
+
+		\path (s0) edge   node {$\lambda$} (sw0)
+		edge   node {$\mu$} (s02)
+
+		(s02)   edge   node {$\lambda$} (sw02)
+		edge   node {$\mu$} (s03)
+		(s03)   edge  node {$\lambda$} (sw03)
+		edge   node {$\mu$} (s04)
+		(s04) edge  node {$\lambda$} (sw04)
+		edge   node {$\mu$} (s05)
+		(s05) edge  node {$\lambda$} (sw05)
+		edge   node {$\mu$} (s1)
+		(s1)    edge  node {$\lambda$} (s0)
+		edge   node {$\mu$} (s12)
+		(s12)   edge  node {$\lambda$} (s02)
+		edge   node {$\mu$} (s13)
+		(s13) edge  node {$\lambda$} (s03)
+		edge   node {$\mu$} (s14)
+		(s14) edge  node {$\lambda$} (s04)
+		edge   node {$\mu$} (s15)
+		(s15) edge  node {$\lambda$} (s05)
+		edge   node {$\mu$} (s2)
+		(s2) edge  node {$\lambda$} (s1)
+		edge   node {$\mu$} (sw1)    
+		(sw1) edge  node {$\lambda$} (s12);
+		\end{tikzpicture}
+		\caption{Queue with phase type fitting of parameter k}
+		\label{fig:queueptf2}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{lstlisting}
+		gsmp
+
+		const int k = 10;
+		const int qCapacity = 10;
+
+		const double timeout = 10;
+		const double lambda = 0.2;
+
+		module main
+
+		qSize : [0..qCapacity] init 0;
+
+		[produce] (qSize < qCapacity) -> (qSize' = qSize+1);
+		[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);
+
+		endmodule
+
+		module trigger
+
+		i : [1..k+1];
+
+		[] i < k -> k/timeout : (i'=i+1);
+		[produce] i = k -> k/timeout : (i'=1);
+		//[consume] true -> (i'=1);
+
+		endmodule
+
+		\end{lstlisting}
+		\caption{Caption}
+		\label{fig:queuecode2}
+	\end{figure}
+
+	\subsection{finding $\mu$}
+
+	According to Prism documentation on phase type fittimg, we should take $\mu = t/k$. The mean of diract(t) is t, and the mean of exponential($\mu$) is $1/\mu$. Hence $\mu = t/k$.
+
+	\subsection{Results}
+
+	For a queue capacity of 10, we compare the steady state probabilities according to k the parameter of phase type fitting.
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=18cm]{sspqueue.png}
+		\caption{The blue line is the result without phase type fitting}
+		\label{fig:res1}
+	\end{figure}
 

### 2018-05-17 Prism_extract/curves.py

@@ -12,8 +12,8 @@ alpha = 0.5
 def curve_10():
 	plt.yscale('linear')
 	plt.xscale('linear')
-	plt.xlabel('time (min)', fontsize=14, color='black')
-	plt.ylabel('Probality', fontsize=14, color='black')
+	plt.xlabel('Size of the Queue', fontsize=14, color='black')
+	plt.ylabel('P', fontsize=14, color='black')
 	plt.title('Steady State Probability for a queue with phase type fitting parameter k')
 	x = range(0,11,1)
 	y_10 = [0.5000000826669286
@@ -103,9 +103,27 @@ def curve_10():
 	plt.plot(x, y_10_10, label = 'k=10')
 	plt.plot(x, y_10_50, label = 'k=50')
 	plt.plot(x, y_10_100, label = 'k=100')
-	plt.plot(x, y_10_200, label = 'k=2000')
+	plt.plot(x, y_10_200, label = 'k=200')
 
 
+	plt.legend()
+	plt.show()
+	
+	
+	
+	
+def time_10():
+	plt.yscale('log')
+	plt.xscale('linear')
+	plt.xlabel('k', fontsize=14, color='black')
+	plt.ylabel('s', fontsize=14, color='black')
+	plt.title('Steady State Probability time computation versus phase type fitting parameter k')
+	k = [0,2,5,10,50,100,200]
+	time = [0.062,0.004,0.007,0.021,1.092,9.951,109.147]
+	states = [11,22,55,110,550,1100,2200]
+	transition = [22,41,104,209,1049,2099,4199] 
+
+	plt.plot(k, time, label = 'time (s)')
 	plt.legend()
 	plt.show()
 

### 2018-05-17 Report/notes.tex
change

@@
 
-	\begin{align} 
-	\begin{split}
-	(x+y)^3 	&= (x+y)^2(x+y)\\
-	&=(x^2+2xy+y^2)(x+y)\\
-	&=(x^3+2x^2y+xy^2) + (x^2y+2xy^2+y^3)\\
-	&=x^3+3x^2y+3xy^2+y^3
-	\end{split}					
-	\end{align}
-	Phasellus viverra nulla ut metus varius laoreet. Quisque rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
+	\begin{figure}
+		\centering
+		\includegraphics[width=16cm]{time.png}
+		\caption{time of computation versus k}
+		\label{fig:time1}
+	\end{figure}
 
-	\subsection{Heading on level 2 (subsection)}
-	Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-	\begin{align}
-	A = 
-	\begin{bmatrix}
-	A_{11} & A_{21} \\
-	A_{21} & A_{22}
-	\end{bmatrix}
-	\end{align}
-	Aenean commodo ligula eget dolor.
-Aenean massa.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-Donec quam felis, ultricies nec, pellentesque eu, pretium quis, sem.
-
-	\subsubsection{Heading on level 3 (subsubsection)}
-	Nulla consequat massa quis enim.
-Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu.
-In enim justo, rhoncus ut, imperdiet a, venenatis vitae, justo.
-Nullam dictum felis eu pede mollis pretium.
-Integer tincidunt.
-Cras dapibus.
-Vivamus elementum semper nisi.
-Aenean vulputate eleifend tellus.
-Aenean leo ligula, porttitor eu, consequat vitae, eleifend ac, enim.
-
-	\paragraph{Heading on level 4 (paragraph)}
-	Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-Aenean commodo ligula eget dolor.
-Aenean massa.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-Donec quam felis, ultricies nec, pellentesque eu, pretium quis, sem.
-Nulla consequat massa quis enim.
-
-	\section{Lists}
-
-	\subsection{Example for list (3*itemize)}
-	\begin{itemize}
-		\item First item in a list 
-		\begin{itemize}
-			\item First item in a list 
-			\begin{itemize}
-				\item First item in a list 
-				\item Second item in a list 
-			\end{itemize}
-			\item Second item in a list 
-		\end{itemize}
-		\item Second item in a list 
-	\end{itemize}
-
-	\subsection{Example for list (enumerate)}
-	\begin{enumerate}
-		\item First item in a list 
-		\item Second item in a list 
-		\item Third item in a list
-	\end{enumerate}
 	%%% End document

### 2018-05-17 Prism_extract/curves.py

@@ -118,12 +118,13 @@ def time_10():
 	plt.xlabel('k', fontsize=14, color='black')
 	plt.ylabel('s', fontsize=14, color='black')
 	plt.title('Steady State Probability time computation versus phase type fitting parameter k')
-	k = [0,2,5,10,50,100,200]
-	time = [0.062,0.004,0.007,0.021,1.092,9.951,109.147]
+	k = [2,5,10,50,100,200]
+	time = [0.004,0.007,0.021,1.092,9.951,109.147]
+	reftime = [0.062,0.062,0.062,0.062,0.062,0.062]
 	states = [11,22,55,110,550,1100,2200]
 	transition = [22,41,104,209,1049,2099,4199] 
-
-	plt.plot(k, time, label = 'time (s)')
+	plt.plot(k, reftime, label = 'ref (s)')
+	plt.plot(k, time, label = 'time with phase type fitting (s)')
 	plt.legend()
 	plt.show()
 

### 2018-05-17 Report/notes.tex
last modif

@@
 
-\lstset{frame=tb,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily\color{red}},
-	numbers=none,
-	numberstyle=\tiny\color{blue},
-	keywordstyle=\color{black},
-	commentstyle=\color{dkgreen},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3,
-	morekeywords={\;,init,gsmp,dtmc, const, int, double, module, formula, endmodule,->,=} 
+\definecolor{prismgreen}{rgb}{0, 0.6, 0}
+
+%% BEGIN PRISM CODE LISTING 
+\lstdefinelanguage{Prism}{ % syntax highlight via font
+	basicstyle=\color{red}\tiny\ttfamily, % small true type font (like
+	courier)
+	morekeywords={bool,C,ceil,const,ctmc,double,dtmc,endinit,endmodule,endrewards,endsystem,F,false,floor,formula,G,global,I,init,int,label,max,mdp,min,module,nondeterministic,P,Pmin,Pmax,prob,probabilistic,R,rate,rewards,Rmin,Rmax,S,stochastic,system,true,U,X},
+	keywordstyle={\bfseries\color{black}},
+	numberstyle=\tiny\color{black},
+	comment=[l] {//}, morecomment=[s]{/*}{*/}, % single and multi-line
+	commentstyle= \color{prismgreen}, % dark green
+	tabsize=4, % tab treatment (going to be fixed in Prism)
+	captionpos=b, % put captions at the bottom
+	escapechar=@ % write LaTeX comments escaped by @ symbol
 }
+
+%define command \prism with one argument for inline printing of \prismcode
+\newcommand{\prism}[1]{\lstinline[language=Prism,basicstyle=\small
+	\ttfamily]|#1|}
+
+%% END PRISM CODE LISTING
+
+     % Set your language (you can change the language for each code-block optionally)
+
 %%% Begin document
@@
 		\centering
-		\begin{lstlisting}
-		gsmp
+		\lstinputlisting[language=Prism]{../Model/timeoutqueue.sm}
 
-		const int qCapacity = 10;
-
-		const double timeout = 10;
-		const double lambda = 0.2;
-
-		module main
-		event prod = dirac(timeout);
-
-		qSize : [0..qCapacity] init 0;
-
-		[produce] (qSize < qCapacity)--prod -> (qSize' = qSize+1);
-		[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);
-
-		endmodule
-		\end{lstlisting}
 		\caption{Prism code for figure \ref{fig:Queue1}}
@@
 
+	\begin{figure}
+		\centering
+		\includegraphics[width=16cm]{size.png}
+		\caption{size of model versus k}
+		\label{fig:time1}
+	\end{figure}
+
 	%%% End document

### 2018-05-17 Prism_extract/curves.py

@@ -121,15 +121,24 @@ def time_10():
 	k = [2,5,10,50,100,200]
 	time = [0.004,0.007,0.021,1.092,9.951,109.147]
 	reftime = [0.062,0.062,0.062,0.062,0.062,0.062]
-	states = [11,22,55,110,550,1100,2200]
-	transition = [22,41,104,209,1049,2099,4199] 
 	plt.plot(k, reftime, label = 'ref (s)')
 	plt.plot(k, time, label = 'time with phase type fitting (s)')
 	plt.legend()
 	plt.show()
 
-def curve_4_150_0():
-	()
+def size_10():
+	plt.yscale('linear')
+	plt.xscale('linear')
+	plt.xlabel('k', fontsize=14, color='black')
+	plt.ylabel('size', fontsize=14, color='black')
+	plt.title('size of model versus phase type fitting parameter k')
+	k = [0,2,5,10,50,100,200]
+	states = [11,22,55,110,550,1100,2200]
+	transition = [22,41,104,209,1049,2099,4199] 
+	plt.plot(k, states, label = 'states')
+	plt.plot(k, transition, label = 'transistions')
+	plt.legend()
+	plt.show()
 
 def curve_6_150_0():
 	()

### 2018-05-17 Report/notes.tex
add ctcm curve on time

--- 2018-05-17 Report/notes.tex
@@
 	\normalfont 								\normalsize
-	Firstname Lastname\\[-3pt]		\normalsize
+	Thomas Mari, M\'{a}rio Uhr\'{i}k\\[-3pt]		\normalsize
 	\today
@@
 
+%% BEGIN PRISM CODE LISTING 
 \definecolor{dkgreen}{rgb}{0,0.6,0}
 \definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
 
 \lstset{frame=tb,
-	aboveskip=3mm,
-	belowskip=3mm,
+	language=Java,
+	aboveskip=1mm,
+	belowskip=1mm,
 	showstringspaces=false,
 	columns=flexible,
-	basicstyle={\small\ttfamily\color{red}},
+	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
 	numbers=none,
-	numberstyle=\tiny\color{blue},
-	keywordstyle=\color{black},
+	numberstyle=\tiny\color{gray},
+	keywordstyle=\color{blue},
 	commentstyle=\color{dkgreen},
@@
 	tabsize=3,
-	morekeywords={\;,init,gsmp,dtmc, const, int, double, module, formula, endmodule,->,=} 
+	morekeywords={event, gsmp, dirac, exponential, uniform, weibull, erlang,
+		module, init, rewards, endrewards, label, true, endmodule}
 }
+
 %%% Begin document
@@
 		\centering
-		\begin{lstlisting}
-		gsmp
+		\lstinputlisting{../Model/timeoutqueue.sm}
 
-		const int qCapacity = 10;
-
-		const double timeout = 10;
-		const double lambda = 0.2;
-
-		module main
-		event prod = dirac(timeout);
-
-		qSize : [0..qCapacity] init 0;
-
-		[produce] (qSize < qCapacity)--prod -> (qSize' = qSize+1);
-		[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);
-
-		endmodule
-		\end{lstlisting}
 		\caption{Prism code for figure \ref{fig:Queue1}}

### 2018-05-17 Prism_extract/curves.py

@@ -119,10 +119,14 @@ def time_10():
 	plt.ylabel('s', fontsize=14, color='black')
 	plt.title('Steady State Probability time computation versus phase type fitting parameter k')
 	k = [2,5,10,50,100,200]
-	time = [0.004,0.007,0.021,1.092,9.951,109.147]
+	time_noopt = [0.004,0.007,0.021,1.092,9.951,109.147]
+	time_opt = [0.002,0.003,0.006,0.011,0.022,0.045]
+
 	reftime = [0.062,0.062,0.062,0.062,0.062,0.062]
 	plt.plot(k, reftime, label = 'ref (s)')
-	plt.plot(k, time, label = 'time with phase type fitting (s)')
+	plt.plot(k, time_noopt, label = 'gsmp')
+	plt.plot(k, time_opt, label = 'ctmc')
+
 	plt.legend()
 	plt.show()
 

### 2018-05-17 Prism_extract/curves.py
adding curve power

@@ -119,13 +119,15 @@ def time_10():
 	plt.ylabel('s', fontsize=14, color='black')
 	plt.title('Steady State Probability time computation versus phase type fitting parameter k')
 	k = [2,5,10,50,100,200]
-	time_noopt = [0.004,0.007,0.021,1.092,9.951,109.147]
-	time_opt = [0.002,0.003,0.006,0.011,0.022,0.045]
+	time_Jacobi_Explicit = [0.004,0.007,0.021,1.092,9.951,109.147]
+	time_Gauss_Hybrid = [0.002,0.003,0.006,0.011,0.022,0.045]
+	time_Power_Hybrid = [0.004,0.005,0.007,0.113,1.018,9.689]
 
 	reftime = [0.062,0.062,0.062,0.062,0.062,0.062]
-	plt.plot(k, reftime, label = 'ref (s)')
-	plt.plot(k, time_noopt, label = 'gsmp')
-	plt.plot(k, time_opt, label = 'ctmc')
+	plt.plot(k, reftime, label = 'gsmp event model')
+	plt.plot(k, time_Jacobi_Explicit, label = 'gsmp Jacobi Explicit')
+	plt.plot(k, time_Gauss_Hybrid, label = 'ctmc Gauss Hybrid')
+	plt.plot(k, time_Power_Hybrid, label = 'ctmc Power Hybrid')
 
 	plt.legend()
 	plt.show()

### 2018-05-17 Report/notes.tex
Modifications of the report document in an effort to improve readability.

@@
 \usepackage{fourier}
+\usepackage{hyperref}
+
+\hypersetup{
+    colorlinks=true,       % false: boxed links; true: colored links
+    linkcolor=red,          % color of internal links 
+    urlcolor=cyan           % color of external links
+}
 
@@
 	\section{Queue : A toy example}
-	We considere a M/M/1/n queue (see Kendall notation).
+	We consider a D/M/1/n queue.
 
@@
 		\end{tikzpicture}
-		\caption{Queue with n capacity, the current size is written on the states}
+		\caption{D/M/1/n queue with capacity $n$. The Dirac-distributed arrival event does not reset when the exponential service event occurs.}
 		\label{fig:Queue1}
@@
 
-		\caption{Prism code for figure \ref{fig:Queue1}}
+		\caption{PRISM GSMP model of a D/M/1/n queue as shown in \ref{fig:Queue1}.}
 		\label{fig:queuecode1}
@@
 		\end{tikzpicture}
-		\caption{Queue with phase type fitting of parameter k}
+		\caption{Queue with phase type fitting of parameter k.}
 		\label{fig:queueptf1}
@@
 		\end{tikzpicture}
-		\caption{Queue with phase type fitting of parameter k}
+		\caption{Queue with phase type fitting of parameter k.}
 		\label{fig:queueptf2}
@@
 		\end{lstlisting}
-		\caption{Caption}
+		\caption{PRISM CTMC model of the D/M/1/n queue as shown in \ref{fig:Queue1} with phase-type fitting to approximate the deterministic arrivals.
+The phase-type module \emph{trigger} is used as suggested on the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.
+}
 		\label{fig:queuecode2}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=12cm]{faq-erlang.jpg}
+		\caption{The effect of $k$, the number of time points within the sequence of exponential transitions, on the shape of the resulting phase-type distribution.
+Increasing $k$ makes the phase-type distribution more deterministic.
+This picture was taken from the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.}
+		\label{fig:time1}
 	\end{figure}
@@
 		\includegraphics[width=18cm]{sspqueue.png}
-		\caption{The blue line is the result without phase type fitting}
+		\caption{The blue line is the result without phase type fitting.}
 		\label{fig:res1}
@@
 		\includegraphics[width=16cm]{time.png}
-		\caption{time of computation versus k}
+		\caption{Computation time for different values of $k$.
+The growing lines represent computations of models with phase-type distributions.
+For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
 		\label{fig:time1}
@@
 		\includegraphics[width=16cm]{size.png}
-		\caption{size of model versus k}
+		\caption{Size of model for different values of $k$.}
 		\label{fig:time1}

### 2018-05-18 Prism_extract/curves.py
logs

@@ -125,7 +125,7 @@ def time_10():
 
 	reftime = [0.062,0.062,0.062,0.062,0.062,0.062]
 	plt.plot(k, reftime, label = 'gsmp event model')
-	plt.plot(k, time_Jacobi_Explicit, label = 'gsmp Jacobi Explicit')
+	plt.plot(k, time_Jacobi_Explicit, label = 'gsmp Power Explicit')
 	plt.plot(k, time_Gauss_Hybrid, label = 'ctmc Gauss Hybrid')
 	plt.plot(k, time_Power_Hybrid, label = 'ctmc Power Hybrid')
 
@@ -149,6 +149,27 @@ def size_10():
 def curve_6_150_0():
 	()
 
+
+def variance():
+	#give the graph of the k according to t for an erlong variance equal to 10^-5
+	plt.yscale('log')
+	plt.xscale('log')
+	plt.xlabel('timeout', fontsize=14, color='black')
+	plt.ylabel('k', fontsize=14, color='black')
+	plt.title('perfect k versus t')
+	epsilon = 10**(-5)
+	t0 = range(1,100,1)
+	t = []
+	k=[]
+	for e in t0:
+		e_float = float(e)
+		r=e_float/100
+		print r
+		t.append(r)
+		k.append((r**2)/epsilon)
+	plt.plot(t, k, label = 'k vs. t')
+	plt.legend()
+	plt.show()
 
 def main():
 	()

### 2018-05-21 Log/sum_line.sh
script

@@ -1,3 +1,0 @@
-PATH = '/home/Foo/Documents/Programs/ShellScripts/Butler'
-SUBPATH = ''
-awk '{s+=$1}NR%nb_line==0{print s;s=0}' file

### 2018-05-21 Prism_extract/curves.py

@@ -12,101 +12,36 @@ def read_file(filename):
 	return a
 
 
-def curve_10():
+#GLOBAL VARIABLE
+Path = '../Log'
+
+#CURVES
+
+def curve_10_random():
+	Subpath = '/random/'
+	#t=0.1
 	plt.yscale('linear')
 	plt.xscale('linear')
 	plt.xlabel('Size of the Queue', fontsize=14, color='black')
 	plt.ylabel('P', fontsize=14, color='black')
 	plt.title('Steady State Probability for a queue with phase type fitting parameter k')
 	x = range(0,11,1)
-	y_10 = [0.5000000826669286
-,0.39840613145837134
-,0.08095129548959867
-,0.016448323368837333
-,0.0033421012330050923
-,6.790753730597986E-4
-,1.3798015979630204E-4
-,2.8033117549421624E-5
-,5.682420643903797E-6
-,1.1194905967466665E-6
-,1.752216115764016E-7]
-	y_10_2 = [0.500014
-,0.309026
-,0.118037
-,0.0450863
-,0.0172215
-,0.00657809
-,0.00251269
-,0.000959917
-,0.000367035
-,0.000141172
-,5.64702e-05]
-	y_10_5 = [0.500001
-,0.358117
-,0.101622
-,0.028837
-,0.00818304
-,0.00232209
-,0.000658939
-,0.000186987
-,5.30691e-05
-,1.51282e-05
-,4.67613e-06
-]
-	y_10_10 = [0.5
-,0.37746
-,0.0925077
-,0.0226717
-,0.00555637
-,0.00136175
-,0.000333737
-,8.17913e-05
-,2.00432e-05
-,4.92029e-06
-,1.3328e-06]
-	y_10_50 = [0.500008
-,0.394084
-,0.0834748
-,0.0176817
-,0.00374534
-,0.000793339
-,0.000168045
-,3.55952e-05
-,7.53877e-06
-,1.59446e-06
-,3.77647e-07
-]
-	y_10_100 = [0.499981
-,0.396256
-,0.0822304
-,0.0170643
-,0.00354115
-,0.000734852
-,0.000152495
-,3.16453e-05
-,6.56616e-06
-,1.35994e-06
-,3.16008e-07
-]
-	y_10_200 = [0.50004
-,0.39729
-,0.0815864
-,0.0167544
-,0.00344064
-,0.000706561
-,0.000145098
-,2.97969e-05
[…]

### 2018-05-21 Script/sum_line.sh

@@ -1,3 +1,17 @@
-PATH = '../Log'
-SUBPATH = ''
-awk '{s+=$1}NR%nb_line==0{print s;s=0}' file
+PATH='../Log/'
+
+
+
+
+
+
+SUBPATH="TEST/hybrid/"
+folder=$PATH$SUBPATH
+Array=("1" "2" "5" "25" "50" "75" "10" "125" "150" "175" "200" "225" "250" "275" "300" "400" "1000" "2000")
+for var in "${Array[@]}" :
+do
+	file='ph_10_'${var}
+	gawk -v k="${var}" '{s+=$1}NR%"k"==0{print s;s=0}' "${file}" #> "sum""${file}"
+done
+
+

### 2018-05-21 Log/t=0.02/explicit/sum_line.sh
script

@@ -1,13 +1,0 @@
-awk '{s+=$1}NR%5==0{print s;s=0}' ph_10_5 > phsum_10_5
-awk '{s+=$1}NR%25==0{print s;s=0}' ph_10_25 > phsum_10_25
-awk '{s+=$1}NR%50==0{print s;s=0}' ph_10_50 > phsum_10_50
-awk '{s+=$1}NR%75==0{print s;s=0}' ph_10_75 > phsum_10_75
-awk '{s+=$1}NR%100==0{print s;s=0}' ph_10_100 > phsum_10_100
-awk '{s+=$1}NR%125==0{print s;s=0}' ph_10_125 > phsum_10_125
-awk '{s+=$1}NR%150==0{print s;s=0}' ph_10_150 > phsum_10_150
-awk '{s+=$1}NR%175==0{print s;s=0}' ph_10_175 > phsum_10_175
-awk '{s+=$1}NR%200==0{print s;s=0}' ph_10_200 > phsum_10_200
-awk '{s+=$1}NR%225==0{print s;s=0}' ph_10_225 > phsum_10_225
-awk '{s+=$1}NR%250==0{print s;s=0}' ph_10_250 > phsum_10_250
-awk '{s+=$1}NR%275==0{print s;s=0}' ph_10_275 > phsum_10_275
-awk '{s+=$1}NR%300==0{print s;s=0}' ph_10_300 > phsum_10_300

### 2018-05-21 Script/ComputeSum.sh

@@ -1,0 +1,71 @@
+path="../Log/"
+
+
+########################################################################
+############################t0.1########################################
+########################################################################
+
+####################################HYBRID
+subpath="t=0.1/hybrid/"
+for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300 400 1000 2000
+do
+	file=$path$subpath'ph_10_'${var}
+	echo $file
+	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+done
+
+####################################EXPLICIT
+subpath="t=0.1/explicit/"
+for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300
+do
+	file=$path$subpath'ph_10_'${var}
+	echo $file
+	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+done
+
+
+
+########################################################################
+############################t0.001######################################
+########################################################################
+
+####################################HYBRID
+subpath="t=0.001/hybrid/"
+for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300 400 1000 2000
+do
+	file=$path$subpath'ph_10_'${var}
+	echo $file
+	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+done
+
+####################################EXPLICIT
+subpath="t=0.001/explicit/"
+for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300
+do
+	file=$path$subpath'ph_10_'${var}
+	echo $file
+	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+done
+
+########################################################################
+############################t0.02#######################################
+########################################################################
+
+####################################HYBRID
+subpath="t=0.02/hybrid/"
+for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300 400 1000 2000
+do
+	file=$path$subpath'ph_10_'${var}
+	echo $file
+	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+done
+
[…]

### 2018-05-21 Script/sum_line.sh

@@ -1,17 +1,0 @@
-PATH='../Log/'
-
-
-
-
-
-
-SUBPATH="TEST/hybrid/"
-folder=$PATH$SUBPATH
-Array=("1" "2" "5" "25" "50" "75" "10" "125" "150" "175" "200" "225" "250" "275" "300" "400" "1000" "2000")
-for var in "${Array[@]}" :
-do
-	file='ph_10_'${var}
-	gawk -v k="${var}" '{s+=$1}NR%"k"==0{print s;s=0}' "${file}" #> "sum""${file}"
-done
-
-

### 2018-05-21 Prism_extract/diff2.py
moove and renaming python script

@@ -1,43 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import numpy as np
-
-import matplotlib.pyplot as plt
-from array import array
-
-
-
-def read_file(filename):
-	file = open(filename, "r")
-	a = []
-	for line in file:
-		print line
-		a.append(float(line))
-	return a
-
-
-def diff_array(a1,a2):
-	diff = []
-	for i in range(1,len(a1),1):
-		diff.append(abs(a1[i]-a2[i]))
-	return diff
-
-def absolute_norm(a1,a2):
-	return max(diff_array(a1,a2))
-	
-def infinite_norm_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return absolute_norm(a1,a2)
-
-def diff_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return diff_array(a1,a2)
-	
-def main(f1,f2):
-	return diff_file(f1,f2)
-
-file1,file2 = sys.argv[0],sys.argv[1]
-print read_file(str(file1))

### 2018-05-21 python/curves.py

@@ -13,10 +13,9 @@ def read_file(filename):
 
 
 #GLOBAL VARIABLE
-Path = '../Log'
+path = '../Log/'
 
 #CURVES
-
 def curve_10_random():
 	Subpath = '/random/'
 	#t=0.1
@@ -44,6 +43,27 @@ def curve_10_random():
 	#plt.plot(x, y_10_200, label = 'k=200')
 
 
+	plt.legend()
+	plt.show()
+	
+def curve01():	
+	#t=0.1
+	#lambda=1/t
+	#n=10
+
+	
+	subpath = 't=0.1/'
+	plt.yscale('linear')
+	plt.xscale('linear')
+	plt.xlabel('Size of the Queue', fontsize=14, color='black')
+	plt.ylabel('P', fontsize=14, color='black')
+	plt.title('Steady State Probability for a queue with phase type fitting parameter k')
+	x = range(0,11,1)
+	k_array = [1, 2, 5, 25, 50, 75, 100, 125, 150, 175, 200, 225, 250, 275, 300, 400, 1000, 2000]
+	#hybrid
+	for k in k_array:
+		y_k = read_file(path+subpath+'hybrid/sumph_10_'+str(k))
+		plt.plot(x, y_k, label = "k="+str(k),linewidth=0.5)
 	plt.legend()
 	plt.show()
 	

### 2018-05-21 python/diff.py

@@ -39,6 +39,7 @@ def diff_file(f1,f2):
 def main(f1,f2):
 	return diff_file(f1,f2)
 
+
 file1,file2 = sys.argv[0],sys.argv[1]
 
 main(file1,file2)

### 2018-05-21 python/curves.py
Adding a Makefile in python folder

@@ -2,6 +2,8 @@ import matplotlib.pyplot as plt
 from array import array
 import sys
 import numpy as np
+import norm
+import diff
 
 def read_file(filename):
 	file = open(filename, "r")

### 2018-05-21 python/diff.py

@@ -38,8 +38,3 @@ def diff_file(f1,f2):
 	
 def main(f1,f2):
 	return diff_file(f1,f2)
-
-
-file1,file2 = sys.argv[0],sys.argv[1]
-
-main(file1,file2)

### 2018-05-21 python/curves.py
diff graph in python

@@ -2,16 +2,7 @@ import matplotlib.pyplot as plt
 from array import array
 import sys
 import numpy as np
-import norm
-import diff
-
-def read_file(filename):
-	file = open(filename, "r")
-	a = []
-	for line in file:
-		print line
-		a.append(float(line))
-	return a
+from norm import *
 
 
 #GLOBAL VARIABLE
@@ -66,6 +57,29 @@ def curve01():
 	for k in k_array:
 		y_k = read_file(path+subpath+'hybrid/sumph_10_'+str(k))
 		plt.plot(x, y_k, label = "k="+str(k),linewidth=0.5)
+	plt.legend()
+	plt.show()
+	
+def diff_hybrid01():	
+	#t=0.1
+	#lambda=1/t
+	#n=10
+
+	
+	subpath = 't=0.1/'
+	plt.yscale('linear')
+	plt.xscale('linear')
+	plt.xlabel('Size of the Queue', fontsize=14, color='black')
+	plt.ylabel('diff', fontsize=14, color='black')
+	plt.title('diff of Steady State Probability for a queue with phase type fitting parameter k')
+	x = range(0,11,1)
+	k_array = [1, 2, 5, 25, 50, 75, 100, 125, 150, 175, 200, 225, 250, 275, 300, 400, 1000, 2000]
+	#hybrid
+	for k in k_array:
+		y_k = read_file(path+subpath+'hybrid/sumph_10_'+str(k))
+		y_0 = read_file(path+subpath+'ev_10')
+		y = absolute(diff_array(y_0,y_k))
+		plt.plot(x, y, label = "k="+str(k),linewidth=0.5)
 	plt.legend()
 	plt.show()
 	

### 2018-05-21 python/diff.py

@@ -1,40 +1,1 @@
-#!/usr/bin/env python
 
-import sys
-import numpy as np
-
-import matplotlib.pyplot as plt
-from array import array
-
-
-
-def read_file(filename):
-	file = open(filename, "r")
-	a = []
-	for line in file:
-		print line
-		a.append(float(line))
-	return a
-
-
-def diff_array(a1,a2):
-	diff = []
-	for i in range(1,len(a1),1):
-		diff.append(abs(a1[i]-a2[i]))
-	return diff
-
-def absolute_norm(a1,a2):
-	return max(diff_array(a1,a2))
-	
-def infinite_norm_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return absolute_norm(a1,a2)
-
-def diff_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return diff_array(a1,a2)
-	
-def main(f1,f2):
-	return diff_file(f1,f2)

### 2018-05-21 python/norm.py

@@ -1,6 +1,6 @@
 import matplotlib.pyplot as plt
 from array import array
-
+import math
 
 
 def read_file(filename):
@@ -10,25 +10,34 @@ def read_file(filename):
 	   a.append(float(line))
 	return a
 
-
 def diff_array(a1,a2):
 	diff = []
-	for i in range(1,len(a1),1):
-		diff.append(abs(a1[i]-a2[i]))
+	for i in range(0,len(a1),1):
+		diff.append(a1[i]-a2[i])
 	return diff
 
-def absolute_norm(a1,a2):
-	return max(diff_array(a1,a2))
+def norm2(a):
+	s=0
+	for e in a:
+		s += e*e
+	return math.sqrt(s)
 	
-def infinite_norm_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return absolute_norm(a1,a2)
+def infinite_norm(a):
+	return max(a)
+
+def absolute(a):
+	ret = []
+	for i in a:
+		ret.append(abs(i))
+	return ret
 
 def diff_file(f1,f2):
 	a1 = read_file(f1)
 	a2 = read_file(f2)
 	return diff_array(a1,a2)
-	
+
+def abs_diff_file(f1,f2):
+	return absolute(diff_file(f1,f2))
+		
 def main():
 	()

### 2018-05-22 Report/notes.tex
put some order in the report folder

@@
 
+	\subsubsection{parameters}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=18cm]{diff_explicit_01.png}
+		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
+		\label{fig:diff_explicit_01}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=18cm]{diff_explicit_01.png}
+		\caption{Distance of result of the SSP computation between the event model and the PTF model using hybrid engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
+		\label{fig:diff_hybrid_01}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=18cm]{diff_explicit_01.png}
+		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
+		\label{fig:diff_explicit_001}
+	\end{figure}
+
 	%%% End document

### 2018-05-22 python/curves.py

@@ -60,7 +60,7 @@ def curve01():
 	plt.legend()
 	plt.show()
 	
-def diff_hybrid01():	
+def diff_hybrid_01():	
 	#t=0.1
 	#lambda=1/t
 	#n=10
@@ -70,8 +70,8 @@ def diff_hybrid01():
 	plt.yscale('linear')
 	plt.xscale('linear')
 	plt.xlabel('Size of the Queue', fontsize=14, color='black')
-	plt.ylabel('diff', fontsize=14, color='black')
-	plt.title('diff of Steady State Probability for a queue with phase type fitting parameter k')
+	plt.ylabel('Euclidean distance per size', fontsize=14, color='black')
+	plt.title('distance of SSP for a queue versus phase type fitting parameter k\ntimeout=0.1,lambda=1/timeout,engine=hybrid')
 	x = range(0,11,1)
 	k_array = [1, 2, 5, 25, 50, 75, 100, 125, 150, 175, 200, 225, 250, 275, 300, 400, 1000, 2000]
 	#hybrid
@@ -82,8 +82,75 @@ def diff_hybrid01():
 		plt.plot(x, y, label = "k="+str(k),linewidth=0.5)
 	plt.legend()
 	plt.show()
+
+def diff_explicit_01():	
+	#t=0.1
+	#lambda=1/t
+	#n=10
+
 	
+	subpath = 't=0.1/'
+	plt.yscale('linear')
+	plt.xscale('linear')
+	plt.xlabel('Size of the Queue', fontsize=14, color='black')
+	plt.ylabel('Euclidean distance per size', fontsize=14, color='black')
+	plt.title('distance of SSP for a queue versus phase type fitting parameter k\ntimeout=0.1,lambda=1/timeout,engine=explicit')
+	x = range(0,11,1)
+	k_array = [1, 2, 5, 25, 50, 75, 100, 125, 150, 175, 200, 225, 250, 275, 300]
+	#hybrid
+	for k in k_array:
+		y_k = read_file(path+subpath+'explicit/sumph_10_'+str(k))
+		y_0 = read_file(path+subpath+'ev_10')
+		y = absolute(diff_array(y_0,y_k))
+		plt.plot(x, y, label = "k="+str(k),linewidth=0.5)
+	plt.legend()
+	plt.show()
 	
+def diff_hybrid_001():	
+	#t=0.1
+	#lambda=1/t
+	#n=10
+
+	
+	subpath = 't=0.1/'
[…]

### 2018-05-22 Log/t=0.02/explicit/norm.py
ajout des sumph

@@ -1,34 +1,0 @@
-import matplotlib.pyplot as plt
-from array import array
-
-
-
-def read_file(filename):
-	file = open(filename, "r")
-	a = []
-	for line in file:
-	   a.append(float(line))
-	return a
-
-
-def diff_array(a1,a2):
-	diff = []
-	for i in range(1,len(a1),1):
-		diff.append(abs(a1[i]-a2[i]))
-	return diff
-
-def absolute_norm(a1,a2):
-	return max(diff_array(a1,a2))
-	
-def infinite_norm_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return absolute_norm(a1,a2)
-
-def diff_file(f1,f2):
-	a1 = read_file(f1)
-	a2 = read_file(f2)
-	return diff_array(a1,a2)
-	
-def main():
-	()

### 2018-05-22 Report/notes.tex
put some order in the report folder
new plot

@@
 		\centering
-		\includegraphics[width=12cm]{faq-erlang.jpg}
+		\includegraphics[width=12cm]{picture/faq-erlang.jpg}
 		\caption{The effect of $k$, the number of time points within the sequence of exponential transitions, on the shape of the resulting phase-type distribution.
@@
 		\centering
-		\includegraphics[width=18cm]{sspqueue.png}
+		\includegraphics[width=18cm]{picture/sspqueue.png}
 		\caption{The blue line is the result without phase type fitting.}
@@
 		\centering
-		\includegraphics[width=16cm]{time.png}
+		\includegraphics[width=16cm]{picture/time.png}
 		\caption{Computation time for different values of $k$.
@@
 		\centering
-		\includegraphics[width=16cm]{size.png}
+		\includegraphics[width=16cm]{picture/size.png}
 		\caption{Size of model for different values of $k$.}
@@
 		\centering
-		\includegraphics[width=18cm]{diff_explicit_01.png}
+		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
 		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
@@
 		\centering
-		\includegraphics[width=18cm]{diff_explicit_01.png}
+		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
 		\caption{Distance of result of the SSP computation between the event model and the PTF model using hybrid engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
@@
 
+	\begin{figure}
+		\centering
+		\includegraphics[width=18cm]{picture/dist02_explicit_01.png}
+		\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using explicit engine versus the PTF parameter k,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
+		\label{fig:dist02_explicit_001}
+	\end{figure}
+
 	%%% End document

### 2018-05-22 python/norm.py

@@ -23,7 +23,7 @@ def norm2(a):
 	return math.sqrt(s)
 	
 def infinite_norm(a):
-	return max(a)
+	return max(abs(a))
 
 def absolute(a):
 	ret = []

### 2018-05-22 Script/computeSS_for_different_epsilon.sh
I wrote a script computeSS_for_different_epsilon.sh that computes steady state probabilities on the same model for different possible termination epsilons.

@@ -1,0 +1,71 @@
+#compute steady state probabilities for various termination epsilon values.
+#This script must remain in CZK_project/Script !!!
+
+#There are two parameters. 
+#First parameter is t, the timeout inbetween arrivals.
+#Second parameter is k, the number of intermediate points simulating the deterministic distribution.
+
+PRISM_PATH_FROM_SCRIPT="../../../../prismGSMP/prism-gsmp/prism/bin"
+MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
+LOG_PATH_FROM_PRISM="../../../../CZK_project/Log"
+
+reNum='^[0-9]+$'
+if ! [[ $1 =~ $reNum ]]; then
+  echo "Please specify number \"timeout\" as the first parameter!"
+  exit 1
+fi
+
+if ! [[ $2 =~ $reNum ]]; then
+  echo "Please specify number \"k\" as the second parameter!"
+  exit 1
+fi
+
+cd '../Log'
+
+mkdir "t=$1_epsilon"
+cd "t=$1_epsilon"
+mkdir "explicit"
+cd "explicit"
+
+cd $PRISM_PATH_FROM_SCRIPT
+#compute explicit phase type
+for i in 1e-1 1e-2 1e-3 1e-4 1e-5 1e-6 1e-7 1e-8 1e-9
+do
+  ./prism -explicit -epsilon $i -maxiters 10000000 -power -absolute -const k=$2 "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1_epsilon/explicit/ph_10_$2_$i"
+done
+
+#compute explicit event
+./prism -explicit -epsilon 1e-9 -maxiters 10000000 -power -absolute "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1_epsilon/explicit/ev_10_k_1e-9"
+cd -
+
+#write a readme file for explicit computations
+touch readme.txt
+echo "t=$1" >> readme.txt
+echo "lambda=1/t" >> readme.txt
+echo "n=10" >> readme.txt
+echo "naming: ev/ph_n_k_terminationEpsilon" >> readme.txt
+echo "steady state distributions using the GSMP (ctmc with phase type) explicit engine
[…]

### 2018-05-22 Script/computeSS_for_different_k.sh

@@ -8,7 +8,7 @@ LOG_PATH_FROM_PRISM="../../../../CZK_project/Log"
 
 reNum='^[0-9]+$'
 if ! [[ $1 =~ $reNum ]]; then
-  echo "Please specify timeout as the first parameter!"
+  echo "Please specify number \"timeout\" as the first parameter!"
   exit 1
 fi
 
@@ -23,11 +23,11 @@ cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
 for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300
 do
-  ./prism -explicit -epsilon 1e-5 -maxiters 10000000 -const k=$k "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1/explicit/ph_10_$k"
+  ./prism -explicit -epsilon 1e-5 -maxiters 10000000 -power -absolute -const k=$k "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1/explicit/ph_10_$k"
 done
 
 #compute explicit event
-./prism -explicit -epsilon 1e-8 -maxiters 10000000 "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1/explicit/ev_10_k"
+./prism -explicit -epsilon 1e-8 -maxiters 10000000 -power -absolute "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1/explicit/ev_10_k"
 cd -
 
 #write a readme file for explicit computations

### 2018-05-22 Script/computeSS_for_different_epsilon.sh
Script computeSS_for_different_epsilon.sh is now confirmed to work properly.

@@ -9,7 +9,7 @@ PRISM_PATH_FROM_SCRIPT="../../../../prismGSMP/prism-gsmp/prism/bin"
 MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
 LOG_PATH_FROM_PRISM="../../../../CZK_project/Log"
 
-reNum='^[0-9]+$'
+reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]]; then
   echo "Please specify number \"timeout\" as the first parameter!"
   exit 1
@@ -17,7 +17,7 @@ fi
 
 if ! [[ $2 =~ $reNum ]]; then
   echo "Please specify number \"k\" as the second parameter!"
-  exit 1
+  exit 2
 fi
 
 cd '../Log'
@@ -55,7 +55,7 @@ cd $PRISM_PATH_FROM_SCRIPT
 #compute hybrid phase type
 for i in 1e-1 1e-2 1e-3 1e-4 1e-5 1e-6 1e-7 1e-8 1e-9
 do
-  ./prism -hybrid -epsilon $i -maxiters 10000000 -power -absolute -const k=$k "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1_epsilon/hybrid/ph_10_$2_$i"
+  ./prism -hybrid -epsilon $i -maxiters 10000000 -power -absolute -const k=$2 "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1_epsilon/hybrid/ph_10_$2_$i"
 done
 cd -
 

### 2018-05-22 Script/ComputeSum.sh
corrected computesum

@@ -12,6 +12,9 @@ do
 	file=$path$subpath'ph_10_'${var}
 	echo $file
 	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+	head -n -1 $path$subpath'sumph_10_'$var > temp.txt ; mv temp.txt $path$subpath'sumph_10_'$var
+	tail -n1 $file > temp.txt
+	cat temp.txt >>  $path$subpath'sumph_10_'$var 
 done
 
 ####################################EXPLICIT
@@ -21,6 +24,9 @@ do
 	file=$path$subpath'ph_10_'${var}
 	echo $file
 	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+	head -n -1 $path$subpath'sumph_10_'$var > temp.txt ; mv temp.txt $path$subpath'sumph_10_'$var
+	tail -n1 $file > temp.txt
+	cat temp.txt >>  $path$subpath'sumph_10_'$var 
 done
 
 
@@ -36,6 +42,9 @@ do
 	file=$path$subpath'ph_10_'${var}
 	echo $file
 	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+	head -n -1 $path$subpath'sumph_10_'$var > temp.txt ; mv temp.txt $path$subpath'sumph_10_'$var
+	tail -n1 $file > temp.txt
+	cat temp.txt >>  $path$subpath'sumph_10_'$var 
 done
 
 ####################################EXPLICIT
@@ -45,6 +54,9 @@ do
 	file=$path$subpath'ph_10_'${var}
 	echo $file
 	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
+	head -n -1 $path$subpath'sumph_10_'$var > temp.txt ; mv temp.txt $path$subpath'sumph_10_'$var
+	tail -n1 $file > temp.txt
+	cat temp.txt >>  $path$subpath'sumph_10_'$var 
 done
 
 ########################################################################
@@ -58,6 +70,9 @@ do
 	file=$path$subpath'ph_10_'${var}
 	echo $file
[…]

### 2018-05-22 Script/ComputeSum.sh
adding logs and fixing sum script

@@ -1,5 +1,7 @@
 path="../Log/"
-
+one=1
+source=$path$subpath'ph_10_'$var
+target=$path$subpath'sumph_10_'$var
 
 ########################################################################
 ############################t0.1########################################
@@ -8,25 +10,35 @@ path="../Log/"
 ####################################HYBRID
 subpath="t=0.1/hybrid/"
 for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300 400 1000 2000
-do
-	file=$path$subpath'ph_10_'${var}
-	echo $file
-	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
-	head -n -1 $path$subpath'sumph_10_'$var > temp.txt ; mv temp.txt $path$subpath'sumph_10_'$var
-	tail -n1 $file > temp.txt
-	cat temp.txt >>  $path$subpath'sumph_10_'$var 
+do	
+	source=$path$subpath'ph_10_'$var
+	target=$path$subpath'sumph_10_'$var
+	echo $source
+	if [ "$var" = "$one" ]
+	then
+			cat $source > $target
+			echo done
+	else
+			gawk -v k=${var} -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.16f\n", s;s=0}' "${source}" > $target
+			tail -n1 $source >> $target
+	fi
 done
 
 ####################################EXPLICIT
 subpath="t=0.1/explicit/"
 for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300
-do
-	file=$path$subpath'ph_10_'${var}
-	echo $file
-	gawk -v k=${var} '{s+=$1}NR%k==0{print s;s=0}' "${file}" > $path$subpath'sumph_10_'$var 
-	head -n -1 $path$subpath'sumph_10_'$var > temp.txt ; mv temp.txt $path$subpath'sumph_10_'$var
-	tail -n1 $file > temp.txt
-	cat temp.txt >>  $path$subpath'sumph_10_'$var 
+do	
+	source=$path$subpath'ph_10_'$var
+	target=$path$subpath'sumph_10_'$var
+	echo $source
+	if [ "$var" = "$one" ]
+	then
+			cat $source > $target
+			echo done
+	else
[…]

### 2018-05-23 python/curves.py
small dtmc model

@@ -99,7 +99,7 @@ def diff_explicit_01():
 	#hybrid
 	for k in k_array:
 		y_k = read_file(path+subpath+'explicit/sumph_10_'+str(k))
-		y_0 = read_file(path+subpath+'ev_10')
+		y_0 = read_file(path+subpath+'explicit/ev_10_k')
 		y = absolute(diff_array(y_0,y_k))
 		plt.plot(x, y, label = "k="+str(k),linewidth=0.5)
 	plt.legend()

### 2018-05-23 Script/computeSS_for_different_k_median.sh
Wrote a new script computeSS_for_different_k_median.sh. Also, the constants in the models are now all undefined.

@@ -1,13 +1,13 @@
 #compute steady state probabilities for various k values.
 #This script must remain in CZK_project/Script !!!
 #There is only one parameter - floating point number specifying the timeout.
-#Lambda is derived as 1/t.
+#Lambda is derived as (ln 2 / timeout).
 
 PRISM_PATH_FROM_SCRIPT="../../../../prismGSMP/prism-gsmp/prism/bin"
 MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
 LOG_PATH_FROM_PRISM="../../../../CZK_project/Log"
 
-lambda=$(bc <<< "scale=10;1/$1")
+lambda=$(bc <<< "scale=10;0.693147181/$1")
 
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]]; then
@@ -17,8 +17,8 @@ fi
 
 cd '../Log'
 
-mkdir "t=$1"
-cd "t=$1"
+mkdir "t=$1_median"
+cd "t=$1_median"
 mkdir "explicit"
 cd "explicit"
 
@@ -26,17 +26,17 @@ cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
 for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300
 do
-  ./prism -explicit -epsilon 1e-5 -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1/explicit/ph_10_$k"
+  ./prism -explicit -epsilon 1e-5 -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_$k"
 done
 
 #compute explicit event
-./prism -explicit -epsilon 1e-8 -maxiters 10000000 -power -absolute -const timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$LOG_PATH_FROM_PRISM/t=$1/explicit/ev_10_k"
[…]

### 2018-05-24 Script/ComputeSum.sh
upt to 5000

@@ -14,7 +14,7 @@ esp="1E-5"
 
 ####################################HYBRID
 subpath="t=$1/hybrid/"
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp
@@ -30,7 +30,7 @@ done
 
 ####################################EXPLICIT
 subpath="t=$1/explicit/"
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 20000
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp

### 2018-05-24 Script/computeSS_for_different_k.sh

@@ -26,7 +26,7 @@ cd "explicit"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do
 	echo explicit $k $esp
   ./prism -explicit -epsilon ${esp} -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${esp}.log"
@@ -55,7 +55,7 @@ cd "hybrid"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute hybrid phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do
 	echo hybrid $k $esp
   ./prism -hybrid -epsilon 1e-5 -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/hybrid/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/hybrid/ph_10_${k}_${esp}.log"

### 2018-05-24 Script/computeSS_for_different_k_median.sh

@@ -26,7 +26,7 @@ cd "explicit"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do
 	echo explicit $k $esp
   ./prism -explicit -epsilon ${esp} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${esp}.log"
@@ -55,7 +55,7 @@ cd "hybrid"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute hybrid phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do
 	echo hybrid $k $esp
   ./prism -hybrid -epsilon ${esp} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/hybrid/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/hybrid/ph_10_${k}_${esp}.log"

### 2018-05-24 Script/computeTime.sh

@@ -21,7 +21,7 @@ targetk=$path$subpath'k_array'
 touch tempfiletime
 touch tempfilek1
 touch tempfilek2
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do	
 	source=$path$subpath'ph_10_'$var'_1E-5.log'
 	grep "Time for steady-state probability computation" $source >> tempfiletime
@@ -41,7 +41,7 @@ targetk=$path$subpath'k_array'
 touch tempfiletime
 touch tempfilek1
 touch tempfilek2
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do	
 	source=$path$subpath'ph_10_'$var'_1E-5.log'
 	grep "Time for steady-state probability computation" $source >> tempfiletime

### 2018-05-24 Script/ComputeSum_median.sh
adding new plots

@@ -14,7 +14,7 @@ esp="1E-5"
 
 ####################################HYBRID
 subpath="t=$1_median/hybrid/"
-for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300 1000 2000
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp
@@ -30,7 +30,7 @@ done
 
 ####################################EXPLICIT
 subpath="t=$1_median/explicit/"
-for var in 1 2 5 25 50 75 100 125 150 175 200 225 250 275 300
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp

### 2018-05-24 Script/computeTime_median.sh
adding script

@@ -1,0 +1,56 @@
+#####README
+# There is only one parameters, that is t. The logs (for t) must be already computed 
+# Return a file of computation time for hybrid and explicit engine in both of their folders
+# In the result the kline is the time of computation for the ph_n_k_eps
+# naming : phtime_n_epsilon, the folder give the engine and the timeout
+# Are fixed constant : epsilon=1E-5
+path="../Output/t=$1_median/"
+
+
+reNum='^[-+]?[0-9]+\.?[0-9]*$'
+if ! [[ $1 =~ $reNum ]]; then
+  echo "Please specify number \"timeout\" as the first parameter!"
+  exit 1
+fi
+
+
+####################################HYBRID
+subpath="hybrid/"
+targettime=$path$subpath'phtime_10_1E-5'
+targetk=$path$subpath'k_array'
+touch tempfiletime
+touch tempfilek1
+touch tempfilek2
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+do	
+	source=$path$subpath'ph_10_'$var'_1E-5.log'
+	grep "Time for steady-state probability computation" $source >> tempfiletime
+	grep "Command line: prism" $source >> tempfilek1
+done
+grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
+grep -Eo 'k=[0-9]+' tempfilek1 > tempfilek2
+grep -Eo '[0-9]+' tempfilek2 > $targetk
+
+rm -f tempfilek1
+rm -f tempfilek2
+rm -f tempfiletime
+####################################EXPLICIT
+subpath="explicit/"
+targettime=$path$subpath'phtime_10_1E-5'
+targetk=$path$subpath'k_array'
+touch tempfiletime
+touch tempfilek1
+touch tempfilek2
+for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+do	
+	source=$path$subpath'ph_10_'$var'_1E-5.log'
+	grep "Time for steady-state probability computation" $source >> tempfiletime
+	grep "Command line: prism" $source >> tempfilek1
+done
+grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
+grep -Eo 'k=[0-9]+' tempfilek1 > tempfilek2
+grep -Eo '[0-9]+' tempfilek2 > $targetk
+
+rm -f tempfilek1
+rm -f tempfilek2
+rm -f tempfiletime

### 2018-05-24 Python/curves.py
upgrading precision on sum to 1E-20, it shouldn't be a problem now

@@ -8,6 +8,7 @@ from norm import *
 #GLOBAL VARIABLE
 path = '../Output/'
 eps = "1E-5"
+esp_precise = "1E-8"
 
 #CURVES
 def curve_10_random():
@@ -155,43 +156,53 @@ def diff_explicit_001():
 ########################################################################
 #############################DISTANCE (NORM)############################
 
-def norm2_plot(s,median):	
-	#s=timeout
-	#lambda=1/t
-	#n=10
+def distance_plot(t,kind_of_t,norm):	
+	#PARAMETERS : 
+	#1 	t(float) is the timeout in sec
+	#2 	kind_of_t(string) is how t was choosen in {"regular","median"} according to lambda
+	#3 	norm(string) is how the norm that must be use for defining the distance {"norm_2","norm_infinite"}
+
+	#CONSTANT
+	n="10"
 	
-
-	#explicit
-	if (median=="median"):
-		subpath = 't='+s+'_median/explicit/'
+	#DATA
+	if (kind_of_t=="median"):												#set the kind_of_t for naming
+		subpath = 't='+str(t)+'_median/'
 	else:
-		subpath = 't='+s+'/explicit/'
-		
-	y_event = read_file(path+subpath+'ev_10_k_1E-8')
-	k_explicit = read_file(path+subpath+'k_array')
-	result_explicit = np.array([])	
+		subpath = 't='+str(t)+'/'
+	#EVENT
+	engine = "explicit/"												#set the engine for naming
+	y_event = read_file(path+subpath+engine+'ev_'+n+'_k_'+esp_precise) 	#this is the reference distribution
+	#EXPLICIT
+	k_explicit = read_file(path+subpath+engine+'k_array')						#load the bottom line for explicit
+	result_explicit = np.array([])											
 	for k in k_explicit[0:len(k_explicit)-4]:
-		print (path+subpath+'sumph_10_'+str(int(k))+'_'+eps)
-		y_k = read_file(path+subpath+'sumph_10_'+str(int(k))+'_'+eps)
-		result = norm2(diff_array(y_event,y_k))
+		y_k = read_file(path+subpath+engine+'sumph_'+n+'_'+str(int(k))+'_'+eps)
+		if (norm == "norm_2"):
+			result = norm_2(diff_array(y_event,y_k))
+		else:
[…]

### 2018-05-24 Script/computeSum.sh

@@ -23,7 +23,7 @@ do
 	then
 			cat $source > $target
 	else
-			gawk -v k=${var} -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.16f\n", s;s=0}' "${source}" > $target
+			gawk -v k=${var} -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.20lf\n", s;s=0}' "${source}" > $target
 			tail -n1 $source >> $target
 	fi
 done
@@ -39,7 +39,7 @@ do
 	then
 			cat $source > $target
 	else
-			gawk -v k=${var} -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.16f\n", s;s=0}' "${source}" > $target
+			gawk -v k=${var} -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.20lf\n", s;s=0}' "${source}" > $target
 			tail -n1 $source >> $target
 	fi
 done

### 2018-05-24 Script/computeTime_median.sh

@@ -5,7 +5,7 @@
 # naming : phtime_n_epsilon, the folder give the engine and the timeout
 # Are fixed constant : epsilon=1E-5
 path="../Output/t=$1_median/"
-
+eps="1E-5"
 
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]]; then
@@ -53,4 +53,12 @@ grep -Eo '[0-9]+' tempfilek2 > $targetk
 
 rm -f tempfilek1
 rm -f tempfilek2
+rm -f tempfiletime
+
+####################################EVENT
+targettime=$path$subpath'evtime_10_'${eps}
+touch tempfiletime
+source=$path$subpath'ev_10_k_'${eps}'.log'
+grep "Time for steady-state probability computation" $source >> tempfiletime
+grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
 rm -f tempfiletime

### 2018-05-25 Report/notes.tex
renaming picture

@@
 
-		const int k = 10;
+const int k;
 const int qCapacity = 10;
 
-		const double timeout = 10;
-		const double lambda = 0.2;
+const double timeout;
+const double lambda;
 
@@
 
-		[] i < k -> k/timeout : (i'=i+1);
+[] i < k & qSize<qCapacity -> k/timeout : (i'=i+1);
 [produce] i = k -> k/timeout : (i'=1);
-		//[consume] true -> (i'=1);
 
 endmodule
-
 		\end{lstlisting}
@@
 		\centering
-		\includegraphics[width=16cm]{picture/time.png}
+		\includegraphics[width=16cm]{picture/time_of_computation.png}
 		\caption{Computation time for different values of $k$.
@@
 		\includegraphics[width=16cm]{picture/size.png}
-		\caption{Size of model for different values of $k$.}
+		\caption{Size of model for different values of $k$. $\#\{$state$\} = nk+1$}
 		\label{fig:time1}
@@
 		\centering
-		\includegraphics[width=18cm]{picture/dist02_explicit_01.png}
+		\includegraphics[width=18cm]{picture/eucl_distance.png}
 		\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using explicit engine versus the PTF parameter k,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}

### 2018-05-25 Script/computeSS_for_different_k.sh
adding random walking model and log, the script now compute with different seq

@@ -26,7 +26,7 @@ cd "explicit"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for k in $(seq 5 5 95; seq 100 100 5000); #seq First Step Last
 do
 	echo explicit $k $esp
   ./prism -explicit -epsilon ${esp} -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${esp}.log"
@@ -55,7 +55,7 @@ cd "hybrid"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute hybrid phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for k in $(seq 5 5 95; seq 100 100 5000);
 do
 	echo hybrid $k $esp
   ./prism -hybrid -epsilon 1e-5 -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/hybrid/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/hybrid/ph_10_${k}_${esp}.log"

### 2018-05-25 Script/computeSS_for_different_k_median.sh

@@ -26,7 +26,7 @@ cd "explicit"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for k in $(seq 5 5 95; seq 100 100 5000);
 do
 	echo explicit $k $esp
   ./prism -explicit -epsilon ${esp} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${esp}.log"
@@ -55,7 +55,7 @@ cd "hybrid"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute hybrid phase type
-for k in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for k in $(seq 5 5 95; seq 100 100 5000);
 do
 	echo hybrid $k $esp
   ./prism -hybrid -epsilon ${esp} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/hybrid/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/hybrid/ph_10_${k}_${esp}.log"

### 2018-05-25 Script/computeSum.sh

@@ -14,7 +14,7 @@ esp="1E-5"
 
 ####################################HYBRID
 subpath="t=$1/hybrid/"
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp
@@ -30,7 +30,7 @@ done
 
 ####################################EXPLICIT
 subpath="t=$1/explicit/"
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp

### 2018-05-25 Script/computeSum_median.sh

@@ -14,7 +14,7 @@ esp="1E-5"
 
 ####################################HYBRID
 subpath="t=$1_median/hybrid/"
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp
@@ -30,7 +30,7 @@ done
 
 ####################################EXPLICIT
 subpath="t=$1_median/explicit/"
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_'$esp
 	target=$path$subpath'sumph_10_'$var'_'$esp

### 2018-05-25 Script/computeTime.sh

@@ -22,7 +22,7 @@ targetk=$path$subpath'k_array'
 touch tempfiletime
 touch tempfilek1
 touch tempfilek2
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_'${eps}'.log'
 	grep "Time for steady-state probability computation" $source >> tempfiletime
@@ -42,7 +42,7 @@ targetk=$path$subpath'k_array'
 touch tempfiletime
 touch tempfilek1
 touch tempfilek2
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_'${eps}'.log'
 	grep "Time for steady-state probability computation" $source >> tempfiletime

### 2018-05-25 Script/computeTime_median.sh

@@ -21,7 +21,7 @@ targetk=$path$subpath'k_array'
 touch tempfiletime
 touch tempfilek1
 touch tempfilek2
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_1E-5.log'
 	grep "Time for steady-state probability computation" $source >> tempfiletime
@@ -41,7 +41,7 @@ targetk=$path$subpath'k_array'
 touch tempfiletime
 touch tempfilek1
 touch tempfilek2
-for var in 1 2 5 10 25 50 75 100 125 150 175 200 225 250 275 300 500 1000 2000 3000 4000 5000
+for var in $(seq 5 5 95; seq 100 100 5000);
 do	
 	source=$path$subpath'ph_10_'$var'_1E-5.log'
 	grep "Time for steady-state probability computation" $source >> tempfiletime

### 2018-05-25 Python/curves.py
esp ==> esp

@@ -8,7 +8,7 @@ from norm import *
 #GLOBAL VARIABLE
 path = '../Output/'
 eps = "1E-5"
-esp_precise = "1E-8"
+eps_precise = "1E-8"
 
 #CURVES
 def curve_10_random():
@@ -84,72 +84,36 @@ def curve01():
 ########################################################################
 #############################DISTANCE PER POINT#########################
 
-def diff_explicit_01():	
-	#t=0.1
-	#lambda=1/t
+def distance_per_state(t,kind_of_t,norm,engine):	
+	#CONSTANT
 	#n=10
-
+	#PARAMETERS : 
+	#1 	t(float) is the timeout in sec
+	#2 	kind_of_t(string) is how t was choosen in {"regular","median"} according to lambda
+	#3 	norm(string) is how the norm that must be use for defining the distance {"norm_2","norm_infinite"}
+	#4 	engine(string) is the engine used in computation {"explicit","hybrid"}
 	
-	subpath = 't=0.1/'
-	plt.yscale('linear')
-	plt.xscale('linear')
-	plt.xlabel('Size of the Queue', fontsize=14, color='black')
-	plt.ylabel('Euclidean distance per size', fontsize=14, color='black')
-	plt.title('distance of SSP for a queue versus phase type fitting parameter k\ntimeout=0.1,lambda=1/timeout,engine=explicit')
-	x = range(0,11,1)
-	k_array = [1, 2, 5, 25, 50, 75, 100, 125, 150, 175, 200, 225, 250, 275, 300]
-	#hybrid
+	#DATA
+	if (kind_of_t=="median"):												#set the kind_of_t for naming
+		subpath = 't='+str(t)+'_median/'
+	else:
+		subpath = 't='+str(t)+'/'
+
+	states = range(0,11,1)
+	k_explicit = read_file(path+subpath+engine+'k_array')						#load the bottom line for explicit
+	
+	
 	for k in k_array:
 		y_k = read_file(path+subpath+'explicit/sumph_10_'+str(k))
-		y_0 = read_file(path+subpath+'explicit/ev_10_k')
-		y = absolute(diff_array(y_0,y_k))
-		plt.plot(x, y, label = "k="+str(k),linewidth=0.5)
-	plt.legend()
-	plt.show()
-	
-def diff_hybrid_001():	
-	#t=0.1
-	#lambda=1/t
[…]

### 2018-05-25 Python/norm.py

@@ -7,7 +7,7 @@ def read_file(filename):
 	file = open(filename, "r")
 	a = []
 	for line in file:
-	   a.append(float(line))
+		a.append(float(line))
 	return a
 
 def diff_array(a1,a2):

### 2018-05-25 Script/computeSS_for_different_k.sh

@@ -8,8 +8,8 @@ MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
 OUTPUT_PATH_FROM_PRISM="../../../../CZK_project/Output"
 
 lambda=$(bc <<< "scale=10;1/$1")
-esp="1e-5"
-esp_precise="1e-8"
+eps="1e-5"
+eps_precise="1e-8"
 
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]]; then
@@ -28,15 +28,15 @@ cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
 for k in $(seq 5 5 95; seq 100 100 5000); #seq First Step Last
 do
-	echo explicit $k $esp
-  ./prism -explicit -epsilon ${esp} -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${esp}.log"
+	echo explicit $k $eps
+  ./prism -explicit -epsilon ${eps} -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${eps}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${eps}.log"
 done
 
 #compute explicit event
-echo event k $esp_precise
-./prism -explicit -epsilon ${esp_precise} -maxiters 10000000 -power -absolute -const timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ev_10_k_${esp_precise}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ev_10_k_${esp_precise}.log" 
-echo event k $esp
[…]

### 2018-05-25 Script/computeSS_for_different_k_median.sh

@@ -8,8 +8,8 @@ MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
 OUTPUT_PATH_FROM_PRISM="../../../../CZK_project/Output"
 
 lambda=$(bc <<< "scale=10;0.693147181/$1")
-esp="1E-5"
-esp_precise="1E-8"
+eps="1E-5"
+eps_precise="1E-8"
 
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]]; then
@@ -28,15 +28,15 @@ cd $PRISM_PATH_FROM_SCRIPT
 #compute explicit phase type
 for k in $(seq 5 5 95; seq 100 100 5000);
 do
-	echo explicit $k $esp
-  ./prism -explicit -epsilon ${esp} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${esp}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${esp}.log"
+	echo explicit $k $eps
+  ./prism -explicit -epsilon ${eps} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${eps}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ph_10_${k}_${eps}.log"
 done
 
 #compute explicit event
-echo event k $esp_precise
-./prism -explicit -epsilon ${esp_precise} -maxiters 100000000 -power -absolute -const timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ev_10_k_${esp_precise}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/explicit/ev_10_k_${esp_precise}.log"
-echo event k $esp_precise
[…]

### 2018-05-25 Script/computeSum.sh

@@ -6,7 +6,7 @@
 # Are fixed constant : epsilon=1E-5
 path="../Output/"
 one=1
-esp="1E-5"
+eps="1E-5"
 
 ########################################################################
 ############################t###########################################
@@ -16,8 +16,8 @@ esp="1E-5"
 subpath="t=$1/hybrid/"
 for var in $(seq 5 5 95; seq 100 100 5000);
 do	
-	source=$path$subpath'ph_10_'$var'_'$esp
-	target=$path$subpath'sumph_10_'$var'_'$esp
+	source=$path$subpath'ph_10_'$var'_'$eps
+	target=$path$subpath'sumph_10_'$var'_'$eps
 	echo $source
 	if [ "$var" = "$one" ]
 	then
@@ -32,8 +32,8 @@ done
 subpath="t=$1/explicit/"
 for var in $(seq 5 5 95; seq 100 100 5000);
 do	
-	source=$path$subpath'ph_10_'$var'_'$esp
-	target=$path$subpath'sumph_10_'$var'_'$esp
+	source=$path$subpath'ph_10_'$var'_'$eps
+	target=$path$subpath'sumph_10_'$var'_'$eps
 	echo $source
 	if [ "$var" = "$one" ]
 	then

### 2018-05-25 Script/computeSum_median.sh

@@ -6,7 +6,7 @@
 # Are fixed constant : epsilon=1E-5
 path="../Output/"
 one=1
-esp="1E-5"
+eps="1E-5"
 
 ########################################################################
 ############################t###########################################
@@ -16,8 +16,8 @@ esp="1E-5"
 subpath="t=$1_median/hybrid/"
 for var in $(seq 5 5 95; seq 100 100 5000);
 do	
-	source=$path$subpath'ph_10_'$var'_'$esp
-	target=$path$subpath'sumph_10_'$var'_'$esp
+	source=$path$subpath'ph_10_'$var'_'$eps
+	target=$path$subpath'sumph_10_'$var'_'$eps
 	echo $source
 	if [ "$var" = "$one" ]
 	then
@@ -32,8 +32,8 @@ done
 subpath="t=$1_median/explicit/"
 for var in $(seq 5 5 95; seq 100 100 5000);
 do	
-	source=$path$subpath'ph_10_'$var'_'$esp
-	target=$path$subpath'sumph_10_'$var'_'$esp
+	source=$path$subpath'ph_10_'$var'_'$eps
+	target=$path$subpath'sumph_10_'$var'_'$eps
 	echo $source
 	if [ "$var" = "$one" ]
 	then

### 2018-05-25 Report/notes.tex
ajout de courbe

@@
 		\centering
-		\includegraphics[width=18cm]{picture/sspqueue.png}
+		\includegraphics[width=18cm]{picture/ssp_hybrid.png}
 		\caption{The blue line is the result without phase type fitting.}
-		\label{fig:res1}
+		\label{fig:ssp_hybrid}
 	\end{figure}
@@
 		\centering
-		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
-		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
-		\label{fig:diff_explicit_01}
-	\end{figure}
-
-	\begin{figure}
-		\centering
-		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
-		\caption{Distance of result of the SSP computation between the event model and the PTF model using hybrid engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
-		\label{fig:diff_hybrid_01}
-	\end{figure}
-
-	\begin{figure}
-		\centering
-		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
+		\includegraphics[width=18cm]{picture/distance_explicit.png}
 		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}

### 2018-05-25 Python/curves.py

@@ -11,72 +11,32 @@ eps = "1E-5"
 eps_precise = "1E-8"
 
 #CURVES
-def curve_10_random():
-	Subpath = '/random/'
-	#t=0.1
-	plt.yscale('linear')
-	plt.xscale('linear')
-	plt.xlabel('Size of the Queue', fontsize=14, color='black')
-	plt.ylabel('P', fontsize=14, color='black')
-	plt.title('Steady State Probability for a queue with phase type fitting parameter k')
-	x = range(0,11,1)
-	
-	y_10 = read_file(Path+Subpath+'queue_10.res')
-	y_10_2 = read_file('../Log/random/queueptf_10_2.res')
-	y_10_5 = read_file('../Log/random/queueptf_10_2.res')
-	y_10_10 = read_file('../Log/random/queueptf_10_2.res')
-	y_10_50 = read_file('../Log/random/queueptf_10_2.res')
-	y_10_100 = read_file('../Log/random/queueptf_10_2.res')
-	y_10_200 = read_file('../Log/random/queueptf_10_2.res')
-	
-	plt.plot(x, y_10, label = 'k=0',linewidth=7.0)
-	#plt.plot(x, y_10_2, label = 'k=2')
-	#plt.plot(x, y_10_5, label = 'k=5')
-	#plt.plot(x, y_10_10, label = 'k=10')
-	#plt.plot(x, y_10_50, label = 'k=50')
-	#plt.plot(x, y_10_100, label = 'k=100')
-	#plt.plot(x, y_10_200, label = 'k=200')
 
-
-	plt.legend()
-	plt.show()
 	
-def curve01():	
-	#t=0.1
-	#lambda=1/t
+def curve(t,kind_of_t,engine):	
+	#CONSTANT
 	#n=10
-
-	
-	subpath = 't=0.1/'
+	#PARAMETERS : 
+	#1 	t(float) is the timeout in sec
+	#2 	kind_of_t(string) is how t was choosen in {"regular","median"} according to lambda
+	#3 	engine(string) is the engine used in computation {"explicit","hybrid"}
+	if (kind_of_t=="median"):											#set the kind_of_t for naming
+		subpath = 't='+str(t)+'_median/'
+	else:
+		subpath = 't='+str(t)+'/'
 	plt.yscale('linear')
 	plt.xscale('linear')
 	plt.xlabel('Size of the Queue', fontsize=14, color='black')
-	plt.ylabel('P', fontsize=14, color='black')
[…]

### 2018-05-25 Script/computeSS_for_different_k (copie).sh

@@ -1,0 +1,74 @@
+#compute steady state probabilities for various k values.
+#This script must remain in CZK_project/Script !!!
+#There is only one parameter - floating point number specifying the timeout.
+#Lambda is derived as 1/t.
+
+PRISM_PATH_FROM_SCRIPT="../../../../prismGSMP/prism-gsmp/prism/bin"
+MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
+OUTPUT_PATH_FROM_PRISM="../../../../CZK_project/Output"
+
+lambda=$(bc <<< "scale=10;1/$1")
+eps="1e-5"
+eps_precise="1e-8"
+
+reNum='^[-+]?[0-9]+\.?[0-9]*$'
+if ! [[ $1 =~ $reNum ]]; then
+  echo "Please specify number \"timeout\" as the first parameter!"
+  exit 1
+fi
+
+cd '../Output'
+
+mkdir "t=$1"
+cd "t=$1"
+mkdir "explicit"
+cd "explicit"
+
+cd $PRISM_PATH_FROM_SCRIPT
+#compute explicit phase type
+for k in $(seq 5 5 95; seq 100 100 5000); #seq First Step Last
+do
+	echo explicit $k $eps
+  ./prism -explicit -epsilon ${eps} -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${eps}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${eps}.log"
+done
+
+#compute explicit event
+echo event k $eps_precise
+./prism -explicit -epsilon ${eps_precise} -maxiters 10000000 -power -absolute -const timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ev_10_k_${eps_precise}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ev_10_k_${eps_precise}.log" 
+echo event k $eps
[…]

### 2018-05-25 Script/computeSum.sh

@@ -1,3 +1,4 @@
+#!/bin/bash
 #####README
 # There is only one parameters, that is t. The logs (for t) must be already computed 
 # Return a file of the sum of probabilities per state of the queue

### 2018-05-25 Script/computeSS_for_different_k (copie).sh
Delete computeSS_for_different_k (copie).sh

@@ -1,74 +1,0 @@
-#compute steady state probabilities for various k values.
-#This script must remain in CZK_project/Script !!!
-#There is only one parameter - floating point number specifying the timeout.
-#Lambda is derived as 1/t.
-
-PRISM_PATH_FROM_SCRIPT="../../../../prismGSMP/prism-gsmp/prism/bin"
-MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
-OUTPUT_PATH_FROM_PRISM="../../../../CZK_project/Output"
-
-lambda=$(bc <<< "scale=10;1/$1")
-eps="1e-5"
-eps_precise="1e-8"
-
-reNum='^[-+]?[0-9]+\.?[0-9]*$'
-if ! [[ $1 =~ $reNum ]]; then
-  echo "Please specify number \"timeout\" as the first parameter!"
-  exit 1
-fi
-
-cd '../Output'
-
-mkdir "t=$1"
-cd "t=$1"
-mkdir "explicit"
-cd "explicit"
-
-cd $PRISM_PATH_FROM_SCRIPT
-#compute explicit phase type
-for k in $(seq 5 5 95; seq 100 100 5000); #seq First Step Last
-do
-	echo explicit $k $eps
-  ./prism -explicit -epsilon ${eps} -maxiters 10000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_gsmp.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${eps}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ph_10_${k}_${eps}.log"
-done
-
-#compute explicit event
-echo event k $eps_precise
-./prism -explicit -epsilon ${eps_precise} -maxiters 10000000 -power -absolute -const timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/timeoutqueue.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ev_10_k_${eps_precise}" > "$OUTPUT_PATH_FROM_PRISM/t=$1/explicit/ev_10_k_${eps_precise}.log" 
-echo event k $eps
[…]

### 2018-05-28 Python/curves.py
renaming random walking model

@@ -64,7 +64,7 @@ def curve_epsilon(t,engine):
 	y_0 = read_file(path+subpath+'explicit'+'/ev_10_k_'+eps_precise)	#event_model
 	x = range(0,11,1)
 	plt.plot(x, y_0, label = 'event model',linewidth=0.7)
-	eps_array = [50,1000,2000,3000,4000,5000]
+	eps_array = read_file(path+subpath+engine (rè+'/eps_array')
 	for k in k_array:
 		y_k = read_file(path+subpath+engine+'/sumph_10_'+str(k)+'_'+eps)
 		plt.plot(x, y_k, label = "k="+str(k),linewidth=0.7)

### 2018-05-28 Script/computeTime_epsilon.sh

@@ -1,0 +1,71 @@
+#####README
+# There is only one parameters, that is t. The logs (for t) must be already computed 
+# $1 = t(int) the timeout
+# $2 = engine/data in {"event","hybrid","explicit"}
+# Return a file of computation time for hybrid and explicit engine in both of their folders
+# In the result the kline is the time of computation for the ph_n_k_eps
+# naming : phtime_n_epsilon, the folder give the engine and the timeout
+reNum='^[-+]?[0-9]+\.?[0-9]*$'
+if ! [[ $1 =~ $reNum ]]; then
+  echo "Please specify number \"timeout\" as the first parameter!"
+  exit 1
+fi
+if ! [[ $1 =~ $reNum ]]; then
+  echo "Please specify number \"timeout\" as the first parameter!"
+  exit 1
+fi
+
+path="../Output/t=$1_epsilon/"
+
+if [[ $2 =~ 'hybrid' ]]; then
+	subpath="hybrid/"
+else
+	subpath="explicit/"
+fi
+
+if [[ $2 =~ 'event' ]]; then
+	data="ev"
+else
+	data="ph"
+fi
+
+
+
+target_time=$path$subpath$data'time_10'
+target_eps=$path$subpath'eps_array'
+
+touch temp
+touch temp_command
+touch temp_eps
+touch temp_time
+
+echo extracting log ...
+for file in $(ls $path$subpath'ph'*.log);
+do	
+	echo $file
+	cat $file >> temp
+done
+echo done
+
+echo time ...
+grep "Time for steady-state probability computation" temp > temp_time
+grep -Eo '[0-9]+.[0-9]+' temp_time > $target_time
+echo done
+
+echo extracting command
+grep "Command line: prism"  temp > temp_command
+echo done
+
+
+echo eps ...
+grep -Eo '-epsilon 1E-[0-9]+' temp_command > temp_eps
+grep -Eo '1E-[0-9]+' temp_eps > $target_eps
+echo done
+
+echo erasing temps
+rm -f temp_command
+rm -f temp
+rm -f temp_time
+rm -f temp_eps
+echo done
+

### 2018-05-28 Python/curves.py
changing script and adding log for different epsilon

@@ -29,17 +29,17 @@ def curve(t,kind_of_t,engine):
 	plt.ylabel('SSP', fontsize=14, color='black')
 	plt.title('SSP\ntimeout='+str(t)+',lambda='+kind_of_t+',engine='+engine+',epsilon='+eps)
 
-	y_0 = read_file(path+subpath+'explicit'+'/ev_10_k_'+eps_precise)	#event_model
+	y_0 = read_float(path+subpath+'explicit'+'/ev_10_k_'+eps_precise)	#event_model
 	x = range(0,11,1)
 	plt.plot(x, y_0, label = 'event model',linewidth=0.7)
 	k_array = [50,1000,2000,3000,4000,5000]
 	for k in k_array:
-		y_k = read_file(path+subpath+engine+'/sumph_10_'+str(k)+'_'+eps)
+		y_k = read_float(path+subpath+engine+'/sumph_10_'+str(k)+'_'+eps)
 		plt.plot(x, y_k, label = "k="+str(k),linewidth=0.7)
 	plt.legend()
 	plt.show()
 
-def curve_epsilon(t,engine):	
+def curve_epsilon(t,k,engine):	
 	#CONSTANT
 	#n=10
 	#k
@@ -49,25 +49,33 @@ def curve_epsilon(t,engine):
 	#2 	kind_of_t(string) is how t was choosen in {"regular","median"} according to lambda
 	#3 	engine(string) is the engine used in computation {"event","explicit","hybrid"}
 	if (engine=="event"):											#set the kind_of_t for naming
-		subpath = 't='+str(t)+'_median/'
+		subpath = 't='+str(t)+'_epsilon/explicit/'
+		data = 'ev'
 	elif (engine == "explicit"):
-		subpath = 't='+str(t)+'/'
+		subpath = 't='+str(t)+'_epsilon/explicit/'
+		data = 'ph'
 	else:
-		subpath = 't='+str(t)+'/'
+		subpath = 't='+str(t)+'_epsilon/hybrid/'
+		data = 'ph'
 		
-	plt.yscale('linear')
+	plt.yscale('log')
 	plt.xscale('linear')
 	plt.xlabel('Size of the Queue', fontsize=14, color='black')
 	plt.ylabel('SSP', fontsize=14, color='black')
-	plt.title('SSP\ntimeout='+str(t)+',lambda='+kind_of_t+',engine='+engine+',epsilon='+eps)
[…]

### 2018-05-28 Python/norm.py

@@ -7,6 +7,13 @@ def read_file(filename):
 	file = open(filename, "r")
 	a = []
 	for line in file:
+		a.append(str(line).rstrip())
+	return a
+
+def read_float(filename):
+	file = open(filename, "r")
+	a = []
+	for line in file:
 		a.append(float(line))
 	return a
 

### 2018-05-28 Script/computeTime_epsilon.sh

@@ -1,23 +1,21 @@
 #####README
 # There is only one parameters, that is t. The logs (for t) must be already computed 
 # $1 = t(int) the timeout
-# $2 = engine/data in {"event","hybrid","explicit"}
+# $2 = engine/data in {event,hybrid,explicit}
 # Return a file of computation time for hybrid and explicit engine in both of their folders
 # In the result the kline is the time of computation for the ph_n_k_eps
 # naming : phtime_n_epsilon, the folder give the engine and the timeout
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
-if ! [[ $1 =~ $reNum ]]; then
+if ! [[ $1 =~ $reNum ]] ; then
   echo "Please specify number \"timeout\" as the first parameter!"
   exit 1
 fi
-if ! [[ $1 =~ $reNum ]]; then
-  echo "Please specify number \"timeout\" as the first parameter!"
-  exit 1
-fi
+
 
 path="../Output/t=$1_epsilon/"
+engine="$2"
 
-if [[ $2 =~ 'hybrid' ]]; then
+if [ "$2" == "hybrid" ]; then
 	subpath="hybrid/"
 else
 	subpath="explicit/"
@@ -31,8 +29,8 @@ fi
 
 
 
-target_time=$path$subpath$data'time_10'
-target_eps=$path$subpath'eps_array'
+target_time=$path$subpath$data'_time_10'
+target_eps=$path$subpath$data'_eps_array'
 
 touch temp
 touch temp_command
@@ -40,7 +38,7 @@ touch temp_eps
 touch temp_time
 
 echo extracting log ...
-for file in $(ls $path$subpath'ph'*.log);
+for file in $(ls $path$subpath$data*.log);
 do	
 	echo $file
 	cat $file >> temp

### 2018-05-29 Python/curves.py
changing report script and python, add plot to the report and lauched a massive computation

@@ -69,12 +69,13 @@ def curve_epsilon(t,k,engine):
 	#plt.plot(x, y_0, label = 'event model',linewidth=0.7)
 	eps_array = read_file(path+subpath+data+'_eps_array')
 	print eps_array
-	for e in eps_array[0::1]:
+	for i,e in enumerate(eps_array[0::1]):
 		if (data == 'ev'):
 			y_e = read_float(path+subpath+'ev_10_k_'+str(e))
 		else:
 			y_e = read_float(path+subpath+'sumph_10_'+str(k)+'_'+e)
-		plt.plot(x, y_e, label = "eps="+str(e),linewidth=0.7)
+		size = 1/float(1+i)
+		plt.plot(x, y_e, label = "eps="+str(e),linewidth=size)
 
 	plt.legend()
 	plt.show()

### 2018-05-29 Script/computeSS_for_different_k_median.sh

@@ -8,8 +8,8 @@ MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
 OUTPUT_PATH_FROM_PRISM="../../../../CZK_project/Output"
 
 lambda=$(bc <<< "scale=10;0.693147181/$1")
-eps="1E-5"
-eps_precise="1E-8"
+eps="1E-6"
+eps_precise="1E-10"
 
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]]; then
@@ -55,7 +55,7 @@ cd "hybrid"
 
 cd $PRISM_PATH_FROM_SCRIPT
 #compute hybrid phase type
-for k in $(seq 5 5 95; seq 100 100 5000);
+for k in $(seq 5 5 95; seq 100 100 5000;seq 6000 1000 50000);
 do
 	echo hybrid $k $eps
   ./prism -hybrid -epsilon ${eps} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$OUTPUT_PATH_FROM_PRISM/t=$1_median/hybrid/ph_10_${k}_${eps}" > "$OUTPUT_PATH_FROM_PRISM/t=$1_median/hybrid/ph_10_${k}_${eps}.log"

### 2018-05-29 Script/computeTime.sh

@@ -1,65 +1,0 @@
-#####README
-# There is only one parameters, that is t. The logs (for t) must be already computed 
-# Return a file of computation time for hybrid and explicit engine in both of their folders
-# In the result the kline is the time of computation for the ph_n_k_eps
-# naming : phtime_n_epsilon, the folder give the engine and the timeout
-# Are fixed constant : epsilon=1E-5
-path="../Output/t=$1/"
-eps="1E-5"
-
-
-reNum='^[-+]?[0-9]+\.?[0-9]*$'
-if ! [[ $1 =~ $reNum ]]; then
-  echo "Please specify number \"timeout\" as the first parameter!"
-  exit 1
-fi
-
-
-####################################HYBRID
-subpath="hybrid/"
-targettime=$path$subpath'phtime_10_'${eps}
-targetk=$path$subpath'k_array'
-touch tempfiletime
-touch tempfilek1
-touch tempfilek2
-for var in $(seq 5 5 95; seq 100 100 5000);
-do	
-	source=$path$subpath'ph_10_'$var'_'${eps}'.log'
-	grep "Time for steady-state probability computation" $source >> tempfiletime
-	grep "Command line: prism" $source >> tempfilek1
-done
-grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
-grep -Eo 'k=[0-9]+' tempfilek1 > tempfilek2
-grep -Eo '[0-9]+' tempfilek2 > $targetk
-
-rm -f tempfilek1
-rm -f tempfilek2
-rm -f tempfiletime
-####################################EXPLICIT
-subpath="explicit/"
-targettime=$path$subpath'phtime_10_'${eps}
-targetk=$path$subpath'k_array'
-touch tempfiletime
-touch tempfilek1
-touch tempfilek2
-for var in $(seq 5 5 95; seq 100 100 5000);
-do	
-	source=$path$subpath'ph_10_'$var'_'${eps}'.log'
-	grep "Time for steady-state probability computation" $source >> tempfiletime
-	grep "Command line: prism" $source >> tempfilek1
-done
-grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
-grep -Eo 'k=[0-9]+' tempfilek1 > tempfilek2
-grep -Eo '[0-9]+' tempfilek2 > $targetk
-
-rm -f tempfilek1
-rm -f tempfilek2
-rm -f tempfiletime
-
-####################################EVENT
[…]

### 2018-05-29 Script/computeTime_epsilon.sh

@@ -2,6 +2,7 @@
 # There is only one parameters, that is t. The logs (for t) must be already computed 
 # $1 = t(int) the timeout
 # $2 = engine/data in {event,hybrid,explicit}
+# $3 = data_type in {regular,epsilon,median}
 # Return a file of computation time for hybrid and explicit engine in both of their folders
 # In the result the kline is the time of computation for the ph_n_k_eps
 # naming : phtime_n_epsilon, the folder give the engine and the timeout
@@ -11,16 +12,25 @@ if ! [[ $1 =~ $reNum ]] ; then
   exit 1
 fi
 
-
-path="../Output/t=$1_epsilon/"
 engine="$2"
 
+#Path Setting
+if [ "$3" == "regular" ]; then
+	path="../Output/t=$1/"
+elif [ "$3" == "epsilon" ]; then
+	path="../Output/t=$1_epsilon/"
+else
+	path="../Output/t=$1_median/"
+fi
+
+#engine setting
 if [ "$2" == "hybrid" ]; then
 	subpath="hybrid/"
 else
 	subpath="explicit/"
 fi
 
+#data setting
 if [[ $2 =~ 'event' ]]; then
 	data="ev"
 else
@@ -31,17 +41,19 @@ fi
 
 target_time=$path$subpath$data'_time_10'
 target_eps=$path$subpath$data'_eps_array'
+target_k=$path$subpath$data'_k_array'
 
 touch temp
 touch temp_command
 touch temp_eps
 touch temp_time
+touch temp_k
 
 echo extracting log ...
-for file in $(ls $path$subpath$data*.log);
+for file in $(ls -t -r  $path$subpath$data*.log); #the order of modification matter = reverse order of last modification
 do	
 	echo $file
-	cat $file >> temp
+	cat $file >> temp #concat logs in temp
 done
 echo done
 
@@ -60,10 +72,18 @@ grep -Eo '-epsilon 1E-[0-9]+' temp_command > temp_eps
 grep -Eo '1E-[0-9]+' temp_eps > $target_eps
 echo done
 
+if [ "$2" != "event" ]; then
+	grep -Eo 'k=[0-9]+' temp_command > temp_k
+	grep -Eo '[0-9]+' temp_k > $target_k
+fi
+
+
+
 echo erasing temps
 rm -f temp_command
 rm -f temp
 rm -f temp_time
 rm -f temp_eps
+rm -f temp_k
 echo done
 

### 2018-05-29 Script/computeTime_median.sh

@@ -1,64 +1,0 @@
-#####README
-# There is only one parameters, that is t. The logs (for t) must be already computed 
-# Return a file of computation time for hybrid and explicit engine in both of their folders
-# In the result the kline is the time of computation for the ph_n_k_eps
-# naming : phtime_n_epsilon, the folder give the engine and the timeout
-# Are fixed constant : epsilon=1E-5
-path="../Output/t=$1_median/"
-eps="1E-5"
-
-reNum='^[-+]?[0-9]+\.?[0-9]*$'
-if ! [[ $1 =~ $reNum ]]; then
-  echo "Please specify number \"timeout\" as the first parameter!"
-  exit 1
-fi
-
-
-####################################HYBRID
-subpath="hybrid/"
-targettime=$path$subpath'phtime_10_1E-5'
-targetk=$path$subpath'k_array'
-touch tempfiletime
-touch tempfilek1
-touch tempfilek2
-for var in $(seq 5 5 95; seq 100 100 5000);
-do	
-	source=$path$subpath'ph_10_'$var'_1E-5.log'
-	grep "Time for steady-state probability computation" $source >> tempfiletime
-	grep "Command line: prism" $source >> tempfilek1
-done
-grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
-grep -Eo 'k=[0-9]+' tempfilek1 > tempfilek2
-grep -Eo '[0-9]+' tempfilek2 > $targetk
-
-rm -f tempfilek1
-rm -f tempfilek2
-rm -f tempfiletime
-####################################EXPLICIT
-subpath="explicit/"
-targettime=$path$subpath'phtime_10_1E-5'
-targetk=$path$subpath'k_array'
-touch tempfiletime
-touch tempfilek1
-touch tempfilek2
-for var in $(seq 5 5 95; seq 100 100 5000);
-do	
-	source=$path$subpath'ph_10_'$var'_1E-5.log'
-	grep "Time for steady-state probability computation" $source >> tempfiletime
-	grep "Command line: prism" $source >> tempfilek1
-done
-grep -Eo '[0-9]+.[0-9]+' tempfiletime > $targettime
-grep -Eo 'k=[0-9]+' tempfilek1 > tempfilek2
-grep -Eo '[0-9]+' tempfilek2 > $targetk
-
-rm -f tempfilek1
-rm -f tempfilek2
-rm -f tempfiletime
-
-####################################EVENT
[…]

### 2018-05-29 Report/notes.tex
changing report script and python, add plot to the report and lauched a massive computation
change report and and time on logs

@@
 
+\subsection{Changing epsilon termination}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=20cm]{picture/epsilon_event.png}
+		\caption{SSP versus epsilon termination, $t=1$,$\lambda=1/t$}
+		\label{fig:epsilon_event}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=20cm]{picture/epsilon_explicit.png}
+		\caption{SSP versus epsilon termination, PTF parameter k=50,	$t=1$,$\lambda=1/t$}
+		\label{fig:epsilon_explicit}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=20cm]{picture/epsilon_hybrid.png}
+		\caption{SSP versus epsilon termination, PTF parameter k=50,	$t=1$,$\lambda=1/t$}
+		\label{fig:epsilon_hybrid}
+	\end{figure}
+
+		\begin{figure}
+			\centering
+			\includegraphics[width=17cm]{picture/distance_hybrid2.png}
+			\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,	$t=0.02$,$median lambda$,$\epsilon=10^{-6}$}
+			\label{fig:dist_hybrid_50k}
+		\end{figure}
+
 	%%% End document

### 2018-05-29 Python/curves.py

@@ -7,8 +7,8 @@ from norm import *
 
 #GLOBAL VARIABLE
 path = '../Output/'
-eps = "1E-5"
-eps_precise = "1E-8"
+eps = "1E-6"
+eps_precise = "1E-10"
 
 ########################################################################
 ###################################CURVES###############################
@@ -138,15 +138,15 @@ def distance_plot(t,kind_of_t,norm):
 	engine = "explicit/"												#set the engine for naming
 	y_event = read_float(path+subpath+engine+'ev_'+n+'_k_'+eps_precise) 	#this is the reference distribution
 	#EXPLICIT
-	k_explicit = read_float(path+subpath+engine+'k_array')						#load the bottom line for explicit
-	result_explicit = np.array([])											
-	for k in k_explicit:
-		y_k = read_float(path+subpath+engine+'sumph_'+n+'_'+str(int(k))+'_'+eps)
-		if (norm == "norm_2"):
-			result = norm_2(diff_array(y_event,y_k))
-		else:
-			result = norm_infinite(diff_array(y_event,y_k))
-		result_explicit = np.append(result_explicit, [result], axis=0)
+#	k_explicit = read_float(path+subpath+engine+'ph_k_array')						#load the bottom line for explicit
+#	result_explicit = np.array([])											
+#	for k in k_explicit:
+#		y_k = read_float(path+subpath+engine+'sumph_'+n+'_'+str(int(k))+'_'+eps)
+#		if (norm == "norm_2"):
+#			result = norm_2(diff_array(y_event,y_k))
+#		else:
+#			result = norm_infinite(diff_array(y_event,y_k))
+#		result_explicit = np.append(result_explicit, [result], axis=0)
 	#HYBRID
 	engine = "hybrid/"													#set the naming for naming
 	if (kind_of_t=="median"):												#set the_kind_of_t for naming
@@ -154,7 +154,7 @@ def distance_plot(t,kind_of_t,norm):
 	else:
 		subpath = 't='+str(t)+'/'
 		
-	k_hybrid = read_float(path+subpath+engine+'k_array')						#load the bottom line for explicit
+	k_hybrid = read_float(path+subpath+engine+'ph_k_array')						#load the bottom line for explicit
 	result_hybrid = np.array([])	
 	for k in k_hybrid:
 		y_k = read_float(path+subpath+engine+'sumph_'+n+'_'+str(int(k))+'_'+eps)
[…]

### 2018-05-29 Script/computeSum_median.sh

@@ -6,7 +6,7 @@
 # Are fixed constant : epsilon=1E-5
 path="../Output/"
 one=1
-eps="1E-5"
+eps="1E-6"
 
 ########################################################################
 ############################t###########################################
@@ -14,7 +14,7 @@ eps="1E-5"
 
 ####################################HYBRID
 subpath="t=$1_median/hybrid/"
-for var in $(seq 5 5 95; seq 100 100 5000);
+for var in $(seq 5 5 95; seq 100 100 5000;seq 6000 1000 50000);
 do	
 	source=$path$subpath'ph_10_'$var'_'$eps
 	target=$path$subpath'sumph_10_'$var'_'$eps

### 2018-06-04 Report/notes.tex
report and maxima

@@
 \usepackage{url}
+\usepackage{xcolor}
 
@@
 			\includegraphics[width=17cm]{picture/distance_hybrid2.png}
-			\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,	$t=0.02$,$median lambda$,$\epsilon=10^{-6}$}
+			\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,	$t=0.02$,median $\lambda$,$\epsilon=10^{-6}$}
 			\label{fig:dist_hybrid_50k}
+		\end{figure}
+
+\clearpage
+
+\section[What has changed ?]{New Model}
+\subsection{Changes}
+
+	\begin{figure}[!h]
+		\centering
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
+		semithick]
+		\tikzstyle{every state}=[fill=red,draw=none,text=white]
+
+		\node[initial,state] (s0)                    {$0$};
+		\node[state]         (s1) [right of=s0] {$1$};
+		\node[state]         (s2) [right of=s1] {$2$};
+		\node[state]         (s3) [right of=s2] {$3$};
+		\node[state]         (s4) [right of=s3]       {$4$};
+		\node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
+		\node[state]         (sn) [right of=sw]       {$n$};
+
+		\path (s0) edge [bend left]             node {Dirac(t)} (s1)
+		(s1) edge [bend left] node {$\lambda$} (s0)
+		edge  [bend left]            node {Dirac(t)} (s2)
+		(s2) edge [bend left]             node {$\lambda$} (s1)
+		edge [bend left]  node {Dirac(t)} (s3)
+		(s3) edge [bend left]              node {$\lambda$} (s2)
+		edge [bend left]  node {Dirac(t)} (s4)
+		(s4) edge [bend left]             node {$\lambda$} (s3)
+		edge [bend left]  node {Dirac(t)} (sw)
+		(sw) edge [bend left]             node {$\lambda$} (s4)
+		edge [bend left]  node {Dirac(t)} (sn)
+		(sn) edge [bend left]             node {$\lambda$} (sw);
+		\end{tikzpicture}
+		\caption{D/M/1/n queue with capacity $n$.Old Event model.}
+		\label{fig:Queue_old}
+	\end{figure}
+
+	\begin{figure}
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
+		semithick]
+		\tikzstyle{every state}=[fill=red,draw=none,text=white]
+
+		\node[state] (s0)                    {$n-1$};
+		\node[state] (s02) [right of=s0,fill=blue,scale=0.5]                   {};
+		\node[state] (s03) [right of=s02,fill=blue,scale=0.5]                    {};
+		\node[state] (s04) [right of=s03,fill=blue,scale=0.5]                   {};
+		\node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
+		\node[state] (s1) [below of=s0]                   {$n$};
+
+		\node[state] (sw0) [above of=s0,fill=white,text=black]        {...}            {};
+		\node[state] (sw02) [right of=sw0,fill=white,text=black]        {...}            {};
+		\node[state] (sw03) [right of=sw02,fill=white,text=black]        {...}            {};
+		\node[state] (sw04) [right of=sw03,fill=white,text=black]        {...}            {};
+		\node[state] (sw05) [right of=sw04,fill=white,text=black]        {...}            {};
+
+		\path 
+		(s0) 	edge   node {$\lambda$} (sw0)
+				edge   node {$\mu$} (s02)
+		(sw05)  edge   node {$\lambda$} (s0)		
+		(s02)   edge   node {$\lambda$} (sw02)
+				edge   node {$\mu$} (s03)
+		(s03)   edge  node {$\lambda$} (sw03)
+				edge   node {$\mu$} (s04)
+		(s04) 	edge  node {$\lambda$} (sw04)
+				edge   node {$\mu$} (s05)
+		(s05) 	edge  node {$\lambda$} (sw05)
+				edge   node {$\mu$} (s1)
+		(s1)    edge  node {$\lambda$} (s0);
+
+		\end{tikzpicture}
+		\caption{Old Phase Type Model, Production isn't enabled in full queue}
+		\label{fig:queue_new}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
+		semithick]
+		\tikzstyle{every state}=[fill=red,draw=none,text=white]
+
+		\node[initial,state] (s0)                    {$0$};
+		\node[state]         (s1) [right of=s0] {$1$};
+		\node[state]         (s2) [right of=s1] {$2$};
+		\node[state]         (s3) [right of=s2] {$3$};
+		\node[state]         (s4) [right of=s3]       {$4$};
+		\node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
+		\node[state]         (sn) [right of=sw]       {$n$};
+
+		\path 
+		(s0) 	edge [bend left]             node {Dirac(t)} (s1)
+		(s1) 	edge [bend left] node {$\lambda$} (s0)
+				edge  [bend left]            node {Dirac(t)} (s2)
+		(s2)	edge [bend left]             node {$\lambda$} (s1)
+				edge [bend left]  node {Dirac(t)} (s3)
+		(s3) 	edge [bend left]              node {$\lambda$} (s2)
+				edge [bend left]  node {Dirac(t)} (s4)
+		(s4) 	edge [bend left]             node {$\lambda$} (s3)
+				edge [bend left]  node {Dirac(t)} (sw)
+		(sw) 	edge [bend left]             node {$\lambda$} (s4)
+				edge [bend left]  node {Dirac(t)} (sn)
+		(sn) 	edge [bend left]             node {$\lambda$} (sw)
+				edge [loop right]  node {\textcolor{red}{Dirac(t)}} (sn);
+		\end{tikzpicture}
+		\caption{D/M/1/n queue with capacity $n$. New event Model.}
+		\label{fig:event_Queue_new}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
+		semithick]
+		\tikzstyle{every state}=[fill=red,draw=none,text=white]
+
+		\node[state] (s0)                    {$n-1$};
+		\node[state] (s02) [right of=s0,fill=blue,scale=0.5]                   {};
+		\node[state] (s03) [right of=s02,fill=blue,scale=0.5]                    {};
+		\node[state] (s04) [right of=s03,fill=blue,scale=0.5]                   {};
+		\node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
+		\node[state] (s1) [below of=s0]                   {$n$};
+
+		\node[state] (s12) [right of=s1,fill=blue,scale=0.5]                   {};
+		\node[state] (s13) [right of=s12,fill=blue,scale=0.5]                    {};
+		\node[state] (s14) [right of=s13,fill=blue,scale=0.5]                   {};
+		\node[state] (s15) [right of=s14,fill=blue,scale=0.5]                    {};
+
+		\node[state] (sw0) [above of=s0,fill=white,text=black]        {...}            {};
+		\node[state] (sw02) [right of=sw0,fill=white,text=black]        {...}            {};
+		\node[state] (sw03) [right of=sw02,fill=white,text=black]        {...}            {};
+		\node[state] (sw04) [right of=sw03,fill=white,text=black]        {...}            {};
+		\node[state] (sw05) [right of=sw04,fill=white,text=black]        {...}            {};
+
+		\path 
+		(s0) 	edge   node {$\lambda$} (sw0)
+				edge   node {$\mu$} (s02)
+		(sw05)  edge   node {$\lambda$} (s0)		
+		(s02)   edge   node {$\lambda$} (sw02)
+				edge   node {$\mu$} (s03)
+		(s03)   edge  node {$\lambda$} (sw03)
+				edge   node {$\mu$} (s04)
+		(s04) 	edge  node {$\lambda$} (sw04)
+				edge   node {$\mu$} (s05)
+		(s05) 	edge  node {$\lambda$} (sw05)
+				edge   node {$\mu$} (s1)
+		(s1)    edge  node {$\lambda$} (s0)
+				edge [red] node {$\mu$} (s12)
+		(s12)   edge  node {$\lambda$} (s02)
+				edge [red] node {$\mu$} (s13)
+		(s13) 	edge  node {$\lambda$} (s03)
+				edge [red] node {$\mu$} (s14)
+		(s14) 	edge  node {$\lambda$} (s04)
+				edge [red] node {$\mu$} (s15)
+		(s15) 	edge  node {$\lambda$} (s05)
+				edge [red,bend left] node {$\mu$} (s1);
+		\end{tikzpicture}
+		\caption{New Phase type Model}
+		\label{fig:queue_new}
+	\end{figure}
+
+\clearpage
+\subsection{Result}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=15cm]{picture/New_model/distance_constant_1E-5.png}
+	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=0.1$,median $\lambda$,$\epsilon=10^{-5}$}
+	\label{fig:dist_const_1E-5}
+\end{figure}
+
+Something is wrong... Maybe $\epsilon$ too big ?
+
+\begin{figure}
+	\centering
+	\includegraphics[width=17cm]{picture/New_model/distance_epsilon.png}
+	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
+	\label{fig:dist_epsilon_1E-13}
+\end{figure}
+
+\clearpage
+\subsection[epsilon termination]{Condition on epsilon termination}
+$$\epsilon \leq \frac{\epsilon_{wanted}}{k}$$
+$$\forall s \in S, \epsilon \leq Pr(s)$$
+$$\epsilon \leq median(Pr(s))$$
+$$\epsilon \leq 1stQuartile(Pr(s))$$
+$$\epsilon \leq 1stDecile(Pr(s))$$
+$$CDF(t-\delta) \leq \epsilon$$
+$$\epsilon \leq \frac{1}{|S|}$$
+$$\epsilon \leq v = \frac{k}{\lambda^2} = \frac{m^2}{k}$$
+
+\clearpage
+\subsection[epsilon termination]{Dynamic Epsilon}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=17cm]{picture/New_model/distance_explicit_dynamic.png}
+	\caption{Absolute Difference between SSP of event model and of SSP PTF model using explicit engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
+	\label{fig:dist_dynamic_explicit}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=17cm]{picture/New_model/distance_hybrid_dynamic.png}
+	\caption{Absolute Difference between SSP of event model and of SSP PTF model using hybrid engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
+	\label{fig:dist_dynamic_hybrid}
 \end{figure}

### 2018-06-04 Python/curves.py

@@ -6,9 +6,12 @@ from norm import *
 
 
 #GLOBAL VARIABLE
+n='10'
 path = '../Output/'
 eps = "1E-5"
 eps_precise = "1E-10"
+hybrid = 'hybrid'
+explicit = 'explicit'
 
 ########################################################################
 ###################################CURVES###############################
@@ -121,58 +124,66 @@ def distance_per_state(t,kind_of_t,norm,engine,kind_of_epsilon):
 ########################################################################
 #############################DISTANCE (NORM)############################
 
-def distance_plot_k(t,kind_of_t,norm):	
+def distance_plot_k(t,kind_of_t,norm,kind_of_epsilon):	
+	#CONSTANT
+	#n=10
 	#PARAMETERS : 
 	#1 	t(float) is the timeout in sec
 	#2 	kind_of_t(string) is how t was choosen in {"regular","median"} according to lambda
 	#3 	norm(string) is how the norm that must be use for defining the distance {"norm_2","norm_infinite"}
-
-	#CONSTANT
-	n="10"
+	#5 	kind_of_epsilon(string) in {"dynamic","constant"}
 
 
-	if (kind_of_t=="median"):												#set the kind_of_t for naming
-		subpath = 't='+str(t)+'_median/'
+	if (kind_of_t=="median"):											#set the kind_of_t for naming
+		subpath = 't='+str(t)+'_median_'+kind_of_epsilon+'/'
 	else:
-		subpath = 't='+str(t)+'/'
+		subpath = 't='+str(t)+'_regular_'+kind_of_epsilon+'/'
 	#EVENT
-	engine = "explicit/"												#set the engine for naming
-	y_event = read_float(path+subpath+engine+'ev_'+n+'_k_'+eps_precise) 	#this is the reference distribution
-	#EXPLICIT
-#	k_explicit = read_float(path+subpath+engine+'ph_k_array')						#load the bottom line for explicit
-#	result_explicit = np.array([])											
-#	for k in k_explicit:
-#		y_k = read_float(path+subpath+engine+'sumph_'+n+'_'+str(int(k))+'_'+eps)
-#		if (norm == "norm_2"):
-#			result = norm_2(diff_array(y_event,y_k))
-#		else:
-#			result = norm_infinite(diff_array(y_event,y_k))
-#		result_explicit = np.append(result_explicit, [result], axis=0)
[…]

### 2018-06-05 Report/notes.tex
report change

@@
 \begin{figure}
-		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
+	\centering
+	\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.5cm,
 	semithick]
@@
 \end{figure}
+\clearpage
 
@@
 $$\forall s \in S, \epsilon \leq Pr(s)$$
+$$\epsilon \leq \frac{1}{|S|}$$
+$$\epsilon \leq \sigma = \sqrt{v}, v = \frac{k}{\lambda^2} = \frac{m^2}{k}$$
 $$\epsilon \leq median(Pr(s))$$
@@
 $$CDF(t-\delta) \leq \epsilon$$
-$$\epsilon \leq \frac{1}{|S|}$$
-$$\epsilon \leq v = \frac{k}{\lambda^2} = \frac{m^2}{k}$$
 

### 2018-06-05 Script/computeSS_for_different_k.sh

@@ -97,7 +97,8 @@ if [ $engine == "event" ]; then
 elif [ $engine == "explicit" ]; then
 	cd $PRISM_PATH_FROM_OUTPUT
 	echo engine k     epsilon_computation epsilon 
-	for k in $(seq 5 5 95; seq 100 100 5000);
+	#~ for k in $(seq 5 5 95; seq 100 100 5000);
+	for k in $(seq 3800 100 5000);
 		do
 			if [ "$4" == "dynamic" ]; then
 				eps_k=$(awk -v e="$eps" -v kk="$k" 'BEGIN{print (e / kk)}')

### 2018-06-06 Script/computeSS_for_different_k.sh
changing script with classic prism computation

@@ -50,8 +50,11 @@ echo $eps
 eps_precise="1E-10"
 
 PRISM_PATH_FROM_OUTPUT="../../../../prismGSMP/prism-gsmp/prism/bin"
+CLASSIC_PRISM_PATH_FROM_OUTPUT="../../../../prism-4.4-src/bin"
 MODEL_PATH_FROM_PRISM="../../../../CZK_project/Model"
+MODEL_PATH_FROM_CLASSIC_PRISM="../../CZK_project/Model"
 OUTPUT_PATH_FROM_PRISM="../../../../CZK_project/Output"
+OUTPUT_PATH_FROM_CLASSIC_PRISM="../../CZK_project/Output"
 
 #lambda and path setting
 ln_2="0.6931471805599453094" #20 digits
@@ -97,8 +100,8 @@ if [ $engine == "event" ]; then
 elif [ $engine == "explicit" ]; then
 	cd $PRISM_PATH_FROM_OUTPUT
 	echo engine k     epsilon_computation epsilon 
-	#~ for k in $(seq 5 5 95; seq 100 100 5000);
-	for k in $(seq 3800 100 5000);
+	for k in $(seq 5 5 95; seq 100 100 5000);
+	#~ for k in $(seq 3800 100 5000);
 		do
 			if [ "$4" == "dynamic" ]; then
 				eps_k=$(awk -v e="$eps" -v kk="$k" 'BEGIN{print (e / kk)}')
@@ -121,7 +124,8 @@ elif [ $engine == "explicit" ]; then
 
 			
 elif [ $engine == "hybrid" ]; then
-	cd $PRISM_PATH_FROM_OUTPUT
+	#~ cd $PRISM_PATH_FROM_OUTPUT
+	cd $CLASSIC_PRISM_PATH_FROM_OUTPUT
 	echo engine k     epsilon_computation epsilon 
 	#compute hybrid phase type
 	for k in $(seq 5 5 95; seq 100 100 5000);
@@ -132,7 +136,8 @@ elif [ $engine == "hybrid" ]; then
 			eps_k=$eps
 		fi
 		echo hybrid $k $eps_k $eps
[…]

### 2018-06-06 Script/script.sh

@@ -11,5 +11,4 @@
 
 #./computeSum.sh path engine epsilon
 ./computeSum.sh t=0.1_median_dynamic explicit 1E-5
-./computeSum.sh t=0.1_median_dynamic event 1E-5
 ./computeSum.sh t=0.1_median_dynamic hybrid 1E-5

### 2018-06-06 Report/notes.tex
adding curves

@@
 
+\subsection{more data}
+\begin{figure}
+	\centering
+	\includegraphics[width=17cm]{picture/New_model/distance_versus_k.png}
+	\caption{distance (infinite norm) between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
+	\label{fig:dist_versus_k}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=16cm]{picture/New_model/performance_versus_k.png}
+	\caption{Computation time for different values of $k$.
+For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
+	\label{fig:performance}
+\end{figure}
+
 	%%% End document

### 2018-06-06 Python/curves.py

@@ -238,34 +238,35 @@ def distance_plot_epsilon(t,k,norm):
 	plt.show()
 	
 
-def performance(t,kind_of_t):
+def performance(t,kind_of_t,kind_of_epsilon):
+	#CONSTANT
+	#n=10
 	#PARAMETERS : 
 	#1 	t(float) is the timeout in sec
 	#2 	kind_of_t(string) is how t was choosen in {"regular","median"} according to lambda
+	#5 	kind_of_epsilon(string) in {"dynamic","constant"}
 
 	#CONSTANT
 	n="10"
 	
+	#PATH SETTING
+	if (kind_of_t=="median"):											#set the kind_of_t for naming
+		subpath = 't='+str(t)+'_median_'+kind_of_epsilon+'/'
+	else:
+		subpath = 't='+str(t)+'_regular_'+kind_of_epsilon+'/'	
 
 	#EXPLICIT	
-	engine = "explicit/"
-	if (kind_of_t=="median"):
-		subpath = 't='+str(t)+'_median/'+engine
-	else:
-		subpath = 't='+str(t)+'/'+engine
-	
-	y_event = read_float(path+subpath+'evtime_10_'+eps)
-	y_explicit = read_float(path+subpath+'phtime_10_'+eps)
-	k_explicit = read_float(path+subpath+'k_array')
+	full_path = path+subpath+"explicit/"
+		
+	y_event = read_float(full_path+'ev_time_10')
+	y_explicit = read_float(full_path+'ph_time_10')
+	k_explicit = read_float(full_path+'ph_k_array')
 	
 	#HYBRID
-	engine = "hybrid/"
-	if (kind_of_t=="median"):
-		subpath = 't='+str(t)+'_median/'+engine
-	else:
-		subpath = 't='+str(t)+'/'+engine
-	y_hybrid = read_float(path+subpath+'phtime_10_'+eps)
-	k_hybrid = read_float(path+subpath+'k_array')
+	full_path = path+subpath+"hybrid/"
+
+	y_hybrid = read_float(full_path+'ph_time_10')
+	k_hybrid = read_float(full_path+'ph_k_array')
 	
 	#DATA
 	if (len(k_hybrid)>len(k_explicit)):
@@ -281,13 +282,14 @@ def performance(t,kind_of_t):
 	plt.xscale('log')
 	plt.xlabel('K Phase Type Fitting Parameter', fontsize=14, color='black')
 	plt.ylabel('Time of Computation (s)', fontsize=14, color='black')
[…]

### 2018-06-06 Python/curves.py
changing curves

@@ -108,7 +108,7 @@ def distance_per_state(t,kind_of_t,norm,engine,kind_of_epsilon):
 	k_array = read_float(path+subpath+engine+'/ph_k_array')					#load the bottom line for explicit
 	y_0 = read_float(path+subpath+'explicit'+'/ev_10_k_'+eps)
 	
-	for k in k_array[0:36:2]:
+	for k in k_array[0::10]+[k_array[-1]]:
 		y_k = read_float(path+subpath+engine+'/sumph_10_'+str(int(k))+'_'+eps)
 		y = absolute(diff_array(y_0,y_k))
 		plt.plot(states, y, label = "k="+str(k),linewidth=0.5)
@@ -124,7 +124,7 @@ def distance_per_state(t,kind_of_t,norm,engine,kind_of_epsilon):
 ########################################################################
 #############################DISTANCE (NORM)############################
 
-def distance_plot_k(t,kind_of_t,norm,kind_of_epsilon):	
+def distance_k(t,kind_of_t,norm,kind_of_epsilon):	
 	#CONSTANT
 	#n=10
 	#PARAMETERS : 
@@ -178,7 +178,7 @@ def distance_plot_k(t,kind_of_t,norm,kind_of_epsilon):
 	plt.xscale('log')
 	plt.xlabel('PTF parameter k', fontsize=14, color='black')
 	plt.ylabel('distance ('+norm+')', fontsize=14, color='black')
-	plt.title('distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, esp ='+eps+', esp ref='+eps_precise)
+	plt.title('distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise)
 	plt.plot(k_hybrid, result_hybrid, label = "hybrid",linewidth=0.5)
 	plt.plot(k_explicit, result_explicit, label = "explicit",linewidth=0.5)
 	plt.plot(k_explicit, [result_event]*len(k_explicit), label = "event",linewidth=0.5)

### 2018-06-07 Python/curves.py
change pictures i report

@@ -15,7 +15,7 @@ explicit = 'explicit'
 
 ########################################################################
 ###################################CURVES###############################
-def curve(t,kind_of_t,engine):	
+def curve(t,kind_of_t,engine):	#out of order
 	#CONSTANT
 	#n=10
 	#PARAMETERS : 
@@ -25,7 +25,7 @@ def curve(t,kind_of_t,engine):
 	if (kind_of_t=="median"):											#set the kind_of_t for naming
 		subpath = 't='+str(t)+'_median/'
 	else:
-		subpath = 't='+str(t)+'/'
+		subpath = 't='+str(t)+'_regular/'
 	plt.yscale('linear')
 	plt.xscale('linear')
 	plt.xlabel('Size of the Queue', fontsize=14, color='black')
@@ -87,7 +87,7 @@ def curve_epsilon(t,k,engine):
 ########################################################################
 #############################DISTANCE PER POINT#########################
 
-def distance_per_state(t,kind_of_t,norm,engine,kind_of_epsilon):	
+def diff_per_state(t,kind_of_t,engine,kind_of_epsilon):	
 	#CONSTANT
 	#n=10
 	#PARAMETERS : 
@@ -107,7 +107,14 @@ def distance_per_state(t,kind_of_t,norm,engine,kind_of_epsilon):
 	states = range(0,11,1)
 	k_array = read_float(path+subpath+engine+'/ph_k_array')					#load the bottom line for explicit
 	y_0 = read_float(path+subpath+'explicit'+'/ev_10_k_'+eps)
-	
+	#invisible plot for scaling
+	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'hybrid'+'/sumph_10_'+str(int(k_array[0]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
+	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'hybrid'+'/sumph_10_'+str(int(k_array[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
+	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'explicit'+'/sumph_10_'+str(int(k_array[0]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
[…]

### 2018-06-07 Python/curves.py
new performance curce

@@ -298,7 +298,7 @@ def performance(t,kind_of_t,kind_of_epsilon):
 	plt.xscale('log')
 	plt.xlabel('K Phase Type Fitting Parameter', fontsize=14, color='black')
 	plt.ylabel('Time of Computation (s)', fontsize=14, color='black')
-	plt.title('Time of computation of the Steady States Probabilities versus k the PTF parameter\n epsilon = '+eps+', '+kind_of_epsilon+' epsilon, t='+str(t)+', '+kind_of_t)
+	plt.title('Time of computation of the SSP versus k the PTF parameter\n epsilon = '+eps+', '+kind_of_epsilon+' epsilon, t='+str(t)+', '+kind_of_t,fontsize=11)
 	
 	plt.plot(k_array, y_event[0:1:1]*len(k_array), label = 'event',linewidth=1.0)
 	plt.plot(k_explicit, y_explicit, label = 'explicit',linewidth=1.0)

### 2018-06-07 Report/notes.tex
infinity norm distance and renaming

@@
 	\centering
-	\includegraphics[width=17cm]{picture/New_model/distance_explicit_dynamic.png}
+	\includegraphics[width=17cm]{picture/New_model/diff_explicit_dynamic.png}
 	\caption{Absolute Difference between SSP of event model and of SSP PTF model using explicit engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
@@
 	\centering
-	\includegraphics[width=17cm]{picture/New_model/distance_hybrid_dynamic.png}
+	\includegraphics[width=17cm]{picture/New_model/diff_hybrid_dynamic.png}
 	\caption{Absolute Difference between SSP of event model and of SSP PTF model using hybrid engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
@@
 	\includegraphics[width=17cm]{picture/New_model/distance_versus_k.png}
-	\caption{distance (infinite norm) between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
+	\caption{infinity norm distance between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
 	\label{fig:dist_versus_k}

### 2018-06-07 Python/curves.py

@@ -189,7 +189,7 @@ def distance_k(t,kind_of_t,norm,kind_of_epsilon):
 	plt.xlabel('PTF parameter k', fontsize=14, color='black')
 	plt.ylabel('distance', fontsize=14, color='black')
 	if (norm=="infinite"):
-		plt.title('Maximum distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise)
+		plt.title('Infinity norm distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise)
 	else:
 		plt.title('Euclidean distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise)
 	plt.plot(k_hybrid, result_hybrid, label = "hybrid",linewidth=0.5)

### 2018-06-07 Script/computeSS_for_different_k.sh

@@ -3,7 +3,7 @@
 #$2 lambda according to t in {regular,median} regular mean lambda = 1/t, and median means t will be the median value of exp(lambda)
 #$3 epsilon you want 
 #$4 kind_of_epsilon in {dynamic, constant} for dynamic you have eps_computation = eps/k 
-#$5 the engine in {event,explicit,hybrid}
+#$5 the engine in {event,explicit,hybrid,storm}
 #compute steady state probabilities for various k values.
 #This script must remain in CZK_project/Script !!!
 #There is only one parameter - floating point number specifying the timeout.
@@ -148,6 +148,34 @@ elif [ $engine == "hybrid" ]; then
 	echo "naming: ph_n_k_epsilon" >> readme.txt
 	echo "steady state distributions using the CTMC with phase type on hybrid engine with Power method
 	absolute termination criteria for termination epsilon 1.0E-5 for phase type." >> readme.txt
+
+
+elif [ $engine == "storm" ]; then
+	#~ cd $PRISM_PATH_FROM_OUTPUT
+	cd $CLASSIC_PRISM_PATH_FROM_OUTPUT
+	echo engine k     epsilon_computation epsilon 
+	#compute hybrid phase type
+	for k in $(seq 5 5 95; seq 100 100 5000);
+	do
+		if [ "$4" == "dynamic" ]; then
+			eps_k=$(awk -v e="$eps" -v kk="$k" 'BEGIN{print (e / kk)}')
+		else
+			eps_k=$eps
+		fi
+		echo storm $k $eps_k $eps
+		storm --prism -hybrid -epsilon ${eps_k} -maxiters 100000000 -power -absolute -const k=$k,timeout=$1,lambda=$lambda "$MODEL_PATH_FROM_CLASSIC_PRISM/queue_withptf_ctmc.sm" -ss -exportss "$OUTPUT_PATH_FROM_CLASSIC_PRISM/${path}/${engine}/ph_10_${k}_${eps}" > "$OUTPUT_PATH_FROM_CLASSIC_PRISM/${path}/${engine}/ph_10_${k}_${eps}.log"
+	done
+	cd -
+	#write a readme file for hybrid computations
+	touch readme.txt
+	echo "t=$1" >> readme.txt
+	echo "lambda=ln(2)/timeout" >> readme.txt
+	echo "n=10" >> readme.txt
+	echo "naming: ph_n_k_epsilon" >> readme.txt
[…]

### 2018-06-21 Script/computeSS_for_different_k_temp.sh
adding computations of the night and new folder storm bug report and change the scipt for computation

@@ -1,0 +1,186 @@
+#PARAMETERS
+#$1 t(s) the timeout
+#$2 lambda according to t in {regular,median} regular mean lambda = 1/t, and median means t will be the median value of exp(lambda)
+#$3 epsilon you want 
+#$4 kind_of_epsilon in {dynamic, constant} for dynamic you have eps_computation = eps/k 
+#$5 the engine in {event,explicit,hybrid,storm}
+#compute steady state probabilities for various k values.
+#This script must remain in CZK_project/Script !!!
+# median means Lambda is derived as (ln 2 / timeout).
+
+
+
+#check parameter
+reNum='^[-+]?[0-9]+\.?[0-9]*$'
+if ! [[ $1 =~ $reNum ]]; then
+  echo "Please specify number \"timeout\" as the first parameter!"
+  exit 1
+fi
+
+if [ -z "$2" ]
+  then
+    echo "kind of lambda not supplied, choose in {regular,median}"
+    exit 1
+fi
+
+if [ -z "$3" ]
+  then
+    echo "epsilon not supplied"
+    exit 1
+fi
+
+if [ -z "$4" ]
+  then
+    echo "kind of epsilon not supplied, choose in {dynamic,constant}"
+    exit 1
+fi
+
+if [ -z "$5" ]
+  then
+    echo "engine not supplied, choose in {event,explicit,hybrid}"
+    exit 1
+fi
+
+#Constant computation
+engine="$5"
+eps=$(awk -v a="$3" 'BEGIN{print (a)}')
+echo $eps
+eps_precise="1E-10"
+
+
+PRISM_PATH_FROM_OUTPUT="../../../../prism-gsmp/prism/bin"
+CLASSIC_PRISM_PATH_FROM_OUTPUT="../../../../prism-4.4-src/bin"
+MODEL_PATH_FROM_PRISM="../../../CZK_project/Model"
+MODEL_PATH_FROM_CLASSIC_PRISM="../../CZK_project/Model"
+OUTPUT_PATH_FROM_PRISM="../../../CZK_project/Output"
+OUTPUT_PATH_FROM_CLASSIC_PRISM="../../CZK_project/Output"
+
+sequence=$(seq 60000 10000 90000; seq 100000 100000 900000; seq 1000000 1000000 10000000);
[…]

### 2018-06-21 Script/script.sh

@@ -1,6 +1,6 @@
 #$1 = t
 #$2=eps
-sequence=$(seq 1 1 1);
+sequence=$(seq 1 1 20);
 for k in $sequence
 	do
 		./computeSS_for_different_k.sh "$1" median "1E-$k" constant event

### 2018-06-21 Python/curves.py
adding post computation

@@ -35,7 +35,7 @@ def curve(t,kind_of_t,engine):	#out of order
 
 	y_0 = read_float(path+subpath+'explicit'+'/ev_10_k_'+eps_precise)	#event_model
 	x = range(0,11,1)
-	plt.plot(x, y_0, label = 'event model',linewidth=0.7)
+	plt.plot(x, y_0, label = 'PRISM ACTMC',linewidth=0.7)
 	k_array = [50,1000,2000,3000,4000,5000]
 	for k in k_array:
 		y_k = read_float(path+subpath+engine+'/sumph_10_'+str(k)+'_'+eps)
@@ -70,7 +70,7 @@ def curve_epsilon(t,k,engine):
 
 	#y_0 = read_float(path+subpath+'explicit'+'/ev_10_k_'+eps_precise)	#event_model
 	x = range(0,11,1)
-	#plt.plot(x, y_0, label = 'event model',linewidth=0.7)
+	#plt.plot(x, y_0, label = 'PRISM ACTMC',linewidth=0.7)
 	eps_array = read_file(path+subpath+data+'_eps_array')
 	print eps_array
 	for i,e in enumerate(eps_array[0::1]):
@@ -254,10 +254,10 @@ def distance_k(t,kind_of_t,norm,eps,kind_of_epsilon,eps_precise):
 		plt.title('Infinity norm distance of SSP for a queue versus PH fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise+','+kind_of_epsilon+' epsilon')
 	else:
 		plt.title('Euclidean distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise)
-	plt.plot(k_hybrid, result_hybrid, label = "hybrid",linewidth=0.5)
-	#~ plt.plot(k_explicit, result_explicit, label = "explicit",linewidth=0.5)
-	plt.plot(k_storm, result_storm, label = "storm -sparse",linewidth=0.5)
-	plt.plot(k_storm, [result_event]*len(k_storm), label = "event",linewidth=0.5)
+	plt.plot(k_hybrid, result_hybrid, label = "PRISM -hybrid",linewidth=0.5)
+	#~ plt.plot(k_explicit, result_explicit, label = "PRISM -explicit",linewidth=0.5)
[…]

### 2018-06-21 Script/computeTime.sh

@@ -128,8 +128,9 @@ else
 			if [[ $2 =~ 'storm' ]]; then
 				grep "Time for model checking:" $file > temp_time
 				grep -Eo '[0-9]+.[0-9]+' temp_time > temp_time2
-				gawk -v k=11 -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.20lf\n", s;s=0}' temp_time2 >> $target_time
-
+				gawk -v k=11 -v CONVFMT=%.17g '{s+=$1}NR%k==0{printf "%.20lf\n", s;s=0}' temp_time2 > temp_time
+				time=$(cat temp_time)
+				echo "scale=2; $time / 11" | bc >> $target_time
 			else
 				grep "Time for steady-state probability computation:" $file > temp_time
 				grep -Eo '[0-9]+.[0-9]+' temp_time >> $target_time

### 2018-06-21 Python/curves.py
changing pictures and adding post computation

@@ -254,10 +254,10 @@ def distance_k(t,kind_of_t,norm,eps,kind_of_epsilon,eps_precise):
 		plt.title('Infinity norm distance of SSP for a queue versus PH fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise+','+kind_of_epsilon+' epsilon')
 	else:
 		plt.title('Euclidean distance of SSP for a queue versus phase type fitting parameter k\ntimeout='+str(t)+','+kind_of_t+' lambda, eps ='+eps+', eps ref='+eps_precise)
-	plt.plot(k_hybrid, result_hybrid, label = "PRISM -hybrid",linewidth=0.5)
-	#~ plt.plot(k_explicit, result_explicit, label = "PRISM -explicit",linewidth=0.5)
-	plt.plot(k_storm, result_storm, label = "STORM -sparse",linewidth=0.5)
 	plt.plot(k_storm, [result_event]*len(k_storm), label = "PRISM ACTMC",linewidth=0.5)
+	plt.plot(k_hybrid, result_hybrid, label = "PRISM -hybrid",linewidth=0.5)
+	plt.plot(k_storm, result_storm, label = "STORM -sparse",linewidth=0.5)
+	#~ plt.plot(k_explicit, result_explicit, label = "PRISM -explicit",linewidth=0.5)
 
 
 	plt.legend()
@@ -378,9 +378,9 @@ def performance(t,kind_of_t,eps,kind_of_epsilon):
 	plt.title('Time of computation of the SSP versus k the PTF parameter\n epsilon = '+eps+', '+kind_of_epsilon+' epsilon, t='+str(t)+', '+kind_of_t,fontsize=11)
 	
 	plt.plot(k_array, y_event[0:1:1]*len(k_storm), label = 'PRISM ACTMC',linewidth=1.0)
-	#~ plt.plot(k_explicit, y_explicit, label = 'PRISM -explicit',linewidth=1.0)
 	plt.plot(k_hybrid, y_hybrid, label = 'PRISM -hybrid',linewidth=1.0)
 	plt.plot(k_storm, y_storm, label = 'STORM -sparse',linewidth=1.0)
+	#~ plt.plot(k_explicit, y_explicit, label = 'PRISM -explicit',linewidth=1.0)
 	plt.legend()
 	plt.show()
 

### 2018-06-21 Python/curves.sh

@@ -1,0 +1,9 @@
+python curves.py
+performance(0.1,"median","1E-10","constant")
+performance(0.1,"median","1E-10","constant")
+performance(0.1,"median","1E-10","dynamic")
+distance_k(0.1,"median","infinite","1E-10","dynamic","1E-20")
+distance_k(0.1,"median","infinite","1E-10","constant","1E-20")
+diff_per_state(0.1,"median","hybrid","1E-6","constant","1E-20")
+diff_per_state(0.1,"median","hybrid","1E-6","dynamic","1E-20")
+diff_per_state(0.1,"median","storm","1E-6","dynamic","1E-20")

### 2018-06-21 Report/tool_paper.tex
Added our paper tex code to the Report folder.

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[article,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% The graphicx package provides the includegraphics command.
\usepackage{graphicx}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{chains,shapes.multipart}

\usepackage{listings}
\usepackage{color}
%% PRISM CODE LISTING 
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\lstset{frame=tb,
	language=Java,
	aboveskip=1mm,
	belowskip=1mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	morekeywords={event, gsmp, dirac, exponential, uniform, weibull, erlang,
		module, init, rewards, endrewards, label, true, endmodule}
}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links 
    urlcolor=cyan           % color of external links
}

\usepackage{float}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

% \journal{Journal Name}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

\title{Efficient modeling of timeouts in PRISM}

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author{John Smith}

\address{California, United States}

\begin{abstract}
Phase-type fitting remains the only way of modeling non-Markovian distributions within PRISM model checker.
When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within reasonable time.
We ran experimental computations and deduced a reasonable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
Lastly, we hint at an entirely different (and arguably better) approach to handling non-Markovian distributions.
\end{abstract}

\begin{keyword}
PRISM model checker \sep CTMC \sep deterministic timeout \sep phase-type distribution \sep modeling \sep analysis
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
\linenumbers

%% main text
\section{Introduction}
\label{S:1}

PRISM \cite{KNP11} and Storm \cite{DBLP:journals/corr/DehnertJK017} are popular tools for modeling and analysis of stochastic systems in continuous time. They use efficient algorithms for analysis of continuous time Markov chains (CTMC). This approach suffers from a severe restriction of modeling power --- the time between transitions must be exponentially distributed. This restriction can be remedied by the use of phase-type distributions, which can approximate any general distribution with arbitrary accuracy by only using exponential distributions \cite{Buchholz:2014:IMP:2683922}. However, the use of phase-type distributions drastically increases the number of states within the CTMC.

In this paper, we experimentally evaluate the precision of the result and required computation time of various approaches to analysis of continuous time stochastic models with deterministic transitions (timeouts). The obtained results are then compared against results of our extension of PRISM capable of efficiently analyzing CTMC with non-Markovian alarms (ACTMC).

% \subsection{Subsection One}

% Quisque elit ipsum, porttitor et imperdiet in, facilisis ac diam. Nunc facilisis interdum felis eget tincidunt. In condimentum fermentum leo, non consequat leo imperdiet pharetra. Fusce ac massa ipsum, vel convallis diam. Quisque eget turpis felis. Curabitur posuere, risus eu placerat porttitor, magna metus mollis ipsum, eu volutpat nisl erat ac justo. Nullam semper, mi at iaculis viverra, nunc velit iaculis nunc, eu tempor ligula eros in nulla. Aenean dapibus eleifend convallis. Cras ut libero tellus. Integer mollis eros eget risus malesuada fringilla mattis leo facilisis. Etiam interdum turpis eget odio ultricies sed convallis magna accumsan. Morbi in leo a mauris sollicitudin molestie at non nisl.

% \begin{table}[h]
% \centering
% \begin{tabular}{l l l}
% \hline
% \textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
% \hline
% Treatment 1 & 0.0003262 & 0.562 \\
% Treatment 2 & 0.0015681 & 0.910 \\
% Treatment 3 & 0.0009271 & 0.296 \\
% \hline
% \end{tabular}
% \caption{Table caption}
% \end{table}

% \subsection{Subsection Two}

% Donec eget ligula venenatis est posuere eleifend in sit amet diam. Vestibulum sollicitudin mauris ac augue blandit ultricies. Nulla facilisi. Etiam ut turpis nunc. Praesent leo orci, tincidunt vitae feugiat eu, feugiat a massa. Duis mauris ipsum, tempor vel condimentum nec, suscipit non mi. Fusce quis urna dictum felis posuere sagittis ac sit amet erat. In in ultrices lectus. Nulla vitae ipsum lectus, a gravida erat. Etiam quam nisl, blandit ut porta in, accumsan a nibh. Phasellus sodales euismod dolor sit amet elementum. Phasellus varius placerat erat, nec gravida libero pellentesque id. Fusce nisi ante, euismod nec cursus at, suscipit a enim. Nulla facilisi.

% \begin{figure}[h]
% \centering\includegraphics[width=0.4\linewidth]{placeholder}
% \caption{Figure caption}
% \end{figure}

% Integer risus dui, condimentum et gravida vitae, adipiscing et enim. Aliquam erat volutpat. Pellentesque diam sapien, egestas eget gravida ut, tempor eu nulla. Vestibulum mollis pretium lacus eget venenatis. Fusce gravida nisl quis est molestie eu luctus ipsum pretium. Maecenas non eros lorem, vel adipiscing odio. Etiam dolor risus, mattis in pellentesque id, pellentesque eu nibh. Mauris nec ante at orci ultricies placerat ac non massa. Aenean imperdiet, ante eu sollicitudin vestibulum, dolor felis dapibus arcu, sit amet fermentum urna nibh sit amet mauris. Suspendisse adipiscing mollis dolor quis lobortis.

% \begin{equation}
% \label{eq:emc}
% e = mc^2
% \end{equation}

\section{Experimental evaluation}
\label{S:2}

	\begin{figure}[H]
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[initial,state] (s0)                    {$0$};
		\node[state]         (s1) [right of=s0] {$1$};
		\node[state]         (s2) [right of=s1] {$2$};
		\node[state]         (s3) [right of=s2] {$3$};
		\node[state]         (s4) [right of=s3]       {$4$};
		\node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
		\node[state]         (sn) [right of=sw]       {$10$};

		\path[->, dashed]  
        (s0) edge [bend left]             node {$t$} (s1);
        \path[->]
		(s1) edge [bend left] node {$\lambda$} (s0);
        \path[->, dashed]
		(s1) edge  [bend left]            node {$t$} (s2);
        \path[->]
		(s2) edge [bend left]             node {$\lambda$} (s1);
        \path[->, dashed]
		(s2) edge [bend left]  node {$t$} (s3);
        \path[->]
		(s3) edge [bend left]              node {$\lambda$} (s2);
        \path[->, dashed]
		(s3) edge [bend left]  node {$t$} (s4);
        \path[->]
		(s4) edge [bend left]             node {$\lambda$} (s3);
        \path[->, dashed]
		(s4) edge [bend left]  node {$t$} (sw);
        \path[->]
		(sw) edge [bend left]             node {$\lambda$} (s4);
        \path[->, dashed]
		(sw) edge [bend left]  node {$t$} (sn);
        \path[->]
		(sn) edge [bend left]             node {$\lambda$} (sw);
        \path[->, dashed]
        (sn) edge [loop right]  node {$t$} (sn);
		\end{tikzpicture}
		\caption{Model of a D/M/1/10 queue with production timeout $t = 0.1$ and service rate $\lambda = \frac{ln(2)}{timeout} \approx 6.931471805599453094$. The deterministic arrival event does not reset when the exponential service event occurs.}
		\label{fig:D/M/1/10}
	\end{figure}

We have chosen to model a D/M/1/10 queue (deterministic arrivals, exponentially distributed service, single server, capacity of 10) as shown in Figure \ref{fig:D/M/1/10}. The deterministic arrivals are approximated by a phase-type distribution, so the model remains a CTMC and can be analyzed by PRISM. The PRISM model we used is shown in Figure \ref{fig:D/M/1/10_PRISM}.
We computed the steady-state distribution with various values of PRISM termination epsilon $\epsilon$ and the number of phases $k$.

	\begin{figure}[H]
		\begin{lstlisting}
ctmc

const int k;
const int qCapacity = 10;
const double timeout = 0.1;
const double lambda = 6.931471805599453094;

module main

qSize : [0..qCapacity] init 0;

[produce] (qSize <= qCapacity) -> (qSize' = min(qSize+1,qCapacity));
[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);

endmodule

module trigger

i : [1..k+1];

[] i < k -> k/timeout : (i'=i+1);
[produce] i = k -> k/timeout : (i'=1);

endmodule
		\end{lstlisting}
		\caption{PRISM CTMC model of the D/M/1/10 queue as shown in Figure \ref{fig:D/M/1/10} with a phase-type distribution approximating the arrival timeout. The phase-type module \emph{trigger} is used as suggested on the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}. Phase-type parameter $k$ represents the number of phases. Increasing $k$ should improve the approximation of the timeout. }
		\label{fig:D/M/1/10_PRISM}
	\end{figure}

\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
\label{S:2.1}

First, we used the PRISM default absolute termination epsilon $\epsilon = 10^{-6}$. The results are shown in Figure \ref{fig:distance_constant_standard_constant_kappa}. For this $\epsilon$, the obtained results are arguably insufficient. Increasing $k$ does little to improve the precision, and only up to about $k \leq 50$, at which point increasing $k$ further starts making the precision worse.

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_constant_1E-6.png}
\end{center}
\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for default absolute termination epsilon $\epsilon = 10^{-6}$. ACTMC results for $\epsilon = 10^{-6}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-6}$.}
\label{fig:distance_constant_standard_constant_kappa}
\end{figure}

\pagebreak
\subsection{Lowering absolute termination epsilon to $\epsilon = 10^{-10}$}
\label{S:2.2}

For much lower $\epsilon = 10^{-10}$, the precision of the result improves only marginally in comparison to the default $\epsilon$ in Section \ref{S:2.1}. The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_constant_1E-10.png}
\end{center}
\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered absolute termination epsilon $\epsilon = 10^{-10}$. ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
\label{fig:distance_constant_1E-10_constant_kappa}
\end{figure}

\pagebreak
\subsection{Adjusting epsilon $\epsilon = 10^{-10}$ to $k$}
\label{S:2.3}

Since increasing $k$ increases the amount of phases (intermediate states) and each phase may have error up to $\epsilon$, the actual potential error for each state of the queue is $\epsilon \cdot k$. To compensate for this, we devise a simple formula
$$\epsilon^{'} = \frac{\epsilon}{k}$$
where $\epsilon^{'}$ is the adjusted epsilon that should be given to PRISM if precision $\epsilon$ is desired for $k$ phases.
Using adjusted epsilon, the results get significantly better, as shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}. What's more, the phase-type fitting results now seem to converge towards the reference steadily as $k$ increases. This indicates that this approach is correct, and that the reference is trustworthy.

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_dynamic_1E-10.png}
\end{center}
\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$. ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
\label{fig:distance_dynamic_1E-10_constant_kappa}
\end{figure}

\subsection{Required computation time to obtain precise results}
\label{S:2.4}

Although we have shown it is possible to obtain relatively precise results using phase-type distributions, the precision comes at a rather steep cost in computation time. This is shown in Figure \ref{fig:performance_dynamic}. Note that even though Storm is one of the fastest available tools, it still struggles to deliver good precision within reasonable time. The computations all ran on the same virtual machine under same conditions\footnote{Running in a virtual machine might have reduced the performance. The virtual machine we used is available at the \href{http://www.stormchecker.org/documentation/vm/vm.html}{Storm website}.}.

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{performance_dynamic.png}
\end{center}
\caption{Time of computation in seconds of the steady-state probabilities against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$, i.e. corresponding to the data shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}. The computation of our PRISM ACTMC is constant in regards to $k$ because it does not use phase-type fitting. }
\label{fig:performance_dynamic}
\end{figure}

\pagebreak
\section{Conclusion}
We have presented a reliable method for high-precision analysis of PRISM CTMC models with phase-type distributions, that is, adjusting the termination epsilon by the number of phases. However, the large number of phases drastically increases the computation time.

For better performance, we suggest usage of more specialized tools that can deal with non-Markovian distributions directly, without phase-type fitting. Our PRISM ACTMC extension\footnote{Our PRISM ACTMC extension is not fully completed yet and lacks optimization. It will be officially released later, but early development version is available at \href{https://github.com/VojtechRehak/prism-gsmp}{https://github.com/VojtechRehak/prism-gsmp}.} has delivered results with sufficient precision a lot faster.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{model1-num-names}
\bibliography{sample.bib}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2018-06-22 Report/notes.tex
put notation in tool paper + change template (but missing bib files => need to add it later

@@
 	\end{abstract}
+	\keywords{CTMC}
+
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\centering
-	\includegraphics[width=15cm]{picture/New_model/distance_constant_1E-5.png}
+	\includegraphics[width=15cm]{picture/New_model/1E-5/distance_constant_1E-5.png}
 	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=0.1$,median $\lambda$,$\epsilon=10^{-5}$}
@@
 	\centering
-	\includegraphics[width=17cm]{picture/New_model/diff_explicit_dynamic.png}
+	\includegraphics[width=17cm]{picture/New_model/1E-5/diff_explicit_dynamic.png}
 	\caption{Absolute Difference between SSP of event model and of SSP PTF model using explicit engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
@@
 	\centering
-	\includegraphics[width=17cm]{picture/New_model/diff_hybrid_dynamic.png}
+	\includegraphics[width=17cm]{picture/New_model/1E-5/diff_hybrid_dynamic.png}
 	\caption{Absolute Difference between SSP of event model and of SSP PTF model using hybrid engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
@@
 	\centering
-	\includegraphics[width=17cm]{picture/New_model/distance_versus_k.png}
+	\includegraphics[width=17cm]{picture/New_model/1E-5/distance_dynamic_1E-5.png}
 	\caption{infinity norm distance between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
@@
 	\centering
-	\includegraphics[width=16cm]{picture/New_model/performance_versus_k.png}
+	\includegraphics[width=16cm]{picture/New_model/1E-5/performance_dynamic.png}
 	\caption{Computation time for different values of $k$.

### 2018-06-22 Report/tool_paper.tex
put notation in tool paper + change template (but missing bib files => need to add it later

@@
-%% This is file `elsarticle-template-1-num.tex',
-%%
-%% Copyright 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%%
-%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
-%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
-%%
-\documentclass[article,12pt]{elsarticle}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% LaTeX Example: Project Report
+%
+% Source: http://www.howtotex.com
+%
+% Feel free to distribute this example, but please keep the referral
+% to howtotex.com
+% Date: March 2011 
+% 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% How to use writeLaTeX: 
+%
+% You edit the source code here on the left, and the preview on the
+% right shows you the result within a few seconds.
+%
+% Bookmark this page and share the URL with your co-authors. They can
+% edit at the same time!
+%
+% You can upload figures, bibliographies, custom classes and
+% styles using the files menu.
+%
+% If you're new to LaTeX, the wikibook is a great place to start:
+% http://en.wikibooks.org/wiki/LaTeX
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Edit the title below to update the display in My Documents
+%\title{Project Report}
+%
+%%% Preamble
+\documentclass[paper=a4, fontsize=11pt]{scrartcl}
+\usepackage[T1]{fontenc}
+\usepackage{fourier}
+\usepackage{hyperref}
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[preprint,review,12pt]{elsarticle}
+\hypersetup{
+	colorlinks=true,       % false: boxed links; true: colored links
+	linkcolor=red,          % color of internal links 
+	urlcolor=cyan           % color of external links
+}
 
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+\usepackage[english]{babel}															% English language/hyphenation
+\usepackage[protrusion=true,expansion=true]{microtype}	
+\usepackage{amsmath,amsfonts,amsthm} % Math packages
+\usepackage[pdftex]{graphicx}	
+\usepackage{url}
+\usepackage{xcolor}
 
-%% The graphicx package provides the includegraphics command.
-\usepackage{graphicx}
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
+%%% Custom sectioning
+\usepackage{sectsty}
+\allsectionsfont{\centering \normalfont\scshape}
+\usepackage{tikz}
+\usetikzlibrary{chains,shapes.multipart}
 \usepackage{pgf}
@@
 \usetikzlibrary{arrows,automata}
-\usetikzlibrary{chains,shapes.multipart}
+
+%%% Custom headers/footers (fancyhdr package)
+\usepackage{fancyhdr}
+\pagestyle{fancyplain}
+\fancyhead{}											% No page header
+\fancyfoot[L]{}											% Empty 
+\fancyfoot[C]{}											% Empty
+\fancyfoot[R]{\thepage}									% Pagenumbering
+\renewcommand{\headrulewidth}{0pt}			% Remove header underlines
+\renewcommand{\footrulewidth}{0pt}				% Remove footer underlines
+\setlength{\headheight}{13.6pt}
+
+%%% Equation and float numbering
+\numberwithin{equation}{section}		% Equationnumbering: section.eq#
+\numberwithin{figure}{section}			% Figurenumbering: section.fig#
+\numberwithin{table}{section}				% Tablenumbering: section.tab#
+
+%%% Maketitle metadata
+\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} 	% Horizontal rule
+
+\title{
+	%\vspace{-1in} 	
+	\usefont{OT1}{bch}{b}{n}
+	\normalfont \normalsize \textsc{School of random department names} \\ [25pt]
+	\horrule{0.5pt} \\[0.4cm]
+	\huge Efficient modeling of timeouts in PRISM \\
+	\horrule{2pt} \\[0.5cm]
+}
+\author{
+	\normalfont 								\normalsize
+	Thomas Mari, M\'{a}rio Uhr\'{i}k\\[-3pt]		\normalsize
+	\today
+}
+\date{}
 
@@
 \usepackage{color}
-%% PRISM CODE LISTING 
+\usepackage{float}
+
+%% BEGIN PRISM CODE LISTING 
 \definecolor{dkgreen}{rgb}{0,0.6,0}
 \definecolor{gray}{rgb}{0.5,0.5,0.5}
+
 \lstset{frame=tb,
@@
 
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,       % false: boxed links; true: colored links
-    linkcolor=red,          % color of internal links 
-    urlcolor=cyan           % color of external links
-}
-
-\usepackage{float}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-\usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-% \biboptions{}
-
-% \journal{Journal Name}
-
+%%% Begin document
 \begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-\title{Efficient modeling of timeouts in PRISM}
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-\author{John Smith}
-
-\address{California, United States}
+	\maketitle
 
@@
 
-\begin{keyword}
-PRISM model checker \sep CTMC \sep deterministic timeout \sep phase-type distribution \sep modeling \sep analysis
+	\begin{description}
+
+		\item[Keywords:] 	PRISM model checker ; CTMC ; deterministic timeout ; phase-type distribution ; modeling ; analysis
+
+	\end{description}
+
 	%% keywords here, in the form: keyword \sep keyword
@@
 	%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%%
-%% Start line numbering here if you want
-%%
-\linenumbers
 
@@
 		\begin{center}
-\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_constant_1E-6.png}
+			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-6/distance_constant_1E-6.png}
 		\end{center}
@@
 		\begin{center}
-\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_constant_1E-10.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/distance_constant_1E-10.png}
 		\end{center}
@@
 		\begin{center}
-\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_dynamic_1E-10.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/distance_dynamic_1E-10.png}
 		\end{center}
@@
 		\begin{center}
-\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{performance_dynamic.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-6/performance_dynamic.png}
 		\end{center}
@@
 
-\end{document}
-
-%%
-%% End of file `elsarticle-template-1-num.tex'.
+\end{document}\\

### 2018-06-22 Report/tool_paper.tex
Corrections within tool_paper

@@
 
+	\subsection{Obtaining trustworthy reference}
+	\label{S:2.1}
+
 	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
-	\label{S:2.1}
+	\label{S:2.2}
 
@@
 		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for default absolute termination epsilon $\epsilon = 10^{-6}$.
-ACTMC results for $\epsilon = 10^{-6}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-6}$.}
+ACTMC results for $\epsilon = 10^{-6}$ are also compared to the reference.}
 		\label{fig:distance_constant_standard_constant_kappa}
@@
 
-	For much lower $\epsilon = 10^{-10}$, the precision of the result improves only marginally in comparison to the default $\epsilon$ in Section \ref{S:2.1}.
+	For much lower $\epsilon = 10^{-10}$, the precision of the result improves.
+However, for higher $k$ the precision continues to deteriorate like in Section \ref{S:2.2}.
 The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.
@@
 		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered absolute termination epsilon $\epsilon = 10^{-10}$.
-ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
+ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference.}
 		\label{fig:distance_constant_1E-10_constant_kappa}
@@
 		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$.
-ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
+ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference.}
 		\label{fig:distance_dynamic_1E-10_constant_kappa}

### 2018-06-22 Report/tool_paper.tex
corrections within tool_paper
We wrote a new subsection about obtaining a trustworthy reference within tool_paper

@@
 		\end{tikzpicture}
-		\caption{Model of a D/M/1/10 queue with production timeout $t = 0.1$ and service rate $\lambda = \frac{ln(2)}{timeout} \approx 6.931471805599453094$.
+		\caption{Model of a D/M/1/10 queue with production timeout $t = 0.1$ and service rate $\lambda = \frac{ln(2)}{t} \approx 6.931471805599453094$.
 The deterministic arrival event does not reset when the exponential service event occurs.}
@@
 
-	\subsection{Obtaining trustworthy reference}
+	\pagebreak
+	\subsection{Obtaining precise results for reference}
 	\label{S:2.1}
 
+%%%	In order to obtain some steady-state probabilities of reference to compare precision of different tools and engines, we computed the same steady-state probabilities two different ways.
+The first one is the phase type fitting method described as above (ref to the first page).
+The second one is by using our PRISM ACTMC implementation with precise termination epsilon.
+%%%	 the computation  results are quite similar as shown in picture citation
+
+%%%	 put picture diff_per_stqte 
+%%%	 explain picture
+
+	%%% little conclusion: we can from now trust the event model as a reference
+
+	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed.
+To achieve this, we used our own PRISM ACTMC implementation, which is capable of analyzing the given model directly without phase-type fitting.
+Using our implementation, we have computed the steady-state probabilities for very precise termination epsilon $\epsilon = 10^{-20}$ and compared it to the steady-state probabilities obtained by PRISM CTMC with phase-type fitting for $\epsilon = 10^{-16}$ and $k = 800000$.
+As shown in Figure \ref{fig:diff_storm_dynamic}, the differences between the computations are smaller than $10^6$.
+Under the hypothesis that the true result is closer to the result obtained from PRISM ACTMC than to the result obtained from Storm, we can conclude that the PRISM ACTMC can serve as reference with precision at least $10^{-6}$.
+
+	 	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/diff_storm_dynamic.png}
+		\end{center}
+		\caption{Absolute difference of steady-state probabilities of the CTMC with phase-type fitting ($\epsilon = 10^{-16}$, $k = 800000$) from PRISM ACTMC ($\epsilon = 10^{-20}$).}
+		\label{fig:diff_storm_dynamic}
+	\end{figure}
+
+	\pagebreak
 	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}

### 2018-06-25 Script/computeSS_for_different_k.sh
adding computation and error about storm

@@ -55,8 +55,9 @@ MODEL_PATH_FROM_CLASSIC_PRISM="../../CZK_project/Model"
 OUTPUT_PATH_FROM_PRISM="../../../CZK_project/Output"
 OUTPUT_PATH_FROM_CLASSIC_PRISM="../../CZK_project/Output"
 
-sequence=$(seq 1 1 9; seq 10 10 90; seq 100 100 900; seq 1000 1000 4000; seq 5000 5000 50000);
-#~ sequence=$(seq 900000 100000 900000; seq 1000000 1000000 10000000);
+#~ sequence=$(seq 1 1 9; seq 10 10 90; seq 100 100 900; seq 1000 1000 4000; seq 5000 5000 50000);
+#~ sequence=$(seq 60000 10000 90000; seq 100000 100000 1000000; seq 1000000 1000000 10000000);
+sequence=$(seq 2000000 2000000 2000000);
 
 #lambda and path setting
 ln_2="0.6931471805599453094" #20 digits

### 2018-06-25 Python/curves.py
modifying repport

@@ -132,6 +132,7 @@ def diff_per_state(t,kind_of_t,engine,eps,kind_of_epsilon,eps_precise):
 
 	#real plotting
 	for k in k_array[0::4]: #1 curve on 4
+	#~ for k in [k_array[-1]]: #1 curve on 4
 		if (engine=="storm"):
 			if (kind_of_epsilon=="standard"):											#set the kind_of_t for naming
 				y_k = read_float(path+subpath+engine+'/ph_10_'+str(int(k))+'_standard')

### 2018-06-25 Python/plot.py

@@ -6,13 +6,13 @@ from norm import *
 from curves import *
 
 for eps in ["1E-5","1E-6","1E-10"]:
-	performance(0.1,"median",eps,"constant")
-	performance(0.1,"median",eps,"dynamic")
-	distance_k(0.1,"median","infinite",eps,"constant","1E-20")
-	distance_k(0.1,"median","infinite",eps,"dynamic","1E-20")
-	diff_per_state(0.1,"median","hybrid",eps,"constant","1E-20")
-	diff_per_state(0.1,"median","hybrid",eps,"dynamic","1E-20")
-	diff_per_state(0.1,"median","storm",eps,"constant","1E-20")
+	#~ performance(0.1,"median",eps,"constant")
+	#~ performance(0.1,"median",eps,"dynamic")
+	#~ distance_k(0.1,"median","infinite",eps,"constant","1E-20")
+	#~ distance_k(0.1,"median","infinite",eps,"dynamic","1E-20")
+	#~ diff_per_state(0.1,"median","hybrid",eps,"constant","1E-20")
+	#~ diff_per_state(0.1,"median","hybrid",eps,"dynamic","1E-20")
+	#~ diff_per_state(0.1,"median","storm",eps,"constant","1E-20")
 	diff_per_state(0.1,"median","storm",eps,"dynamic","1E-20")
 
 def main():

### 2018-06-25 Script/all_computation.sh
adding help option in most scripts

@@ -1,6 +1,14 @@
 #$1 = t
 #$2=eps
 
+if [ "$1" == "help" ]; then
+	echo '2 argument are expected :'
+	echo '$1 is the the timeout in second, the one we choose to run tests was 0.1'
+	echo '$2 is the the precision epsilon in [1-9]+{E-}[1-9]+ format, in prism it is the termination epsilon for power method, in storm it set the --epsilon option (1E-6 is the default value for both PRISM and Storm)'
+	echo 'Result :'
+	echo 'It will compute logs and outputs of computations for both dynamic and constant epsilon for Storm, PRISM and ACTMC PRISM into the Output folder'
+	exit 1
+	fi
 
 #~ ###################################t=0.1
 #./computeSS_for_different_k.sh t lambda eps  eps_type engine

### 2018-06-25 Script/computeSS_for_different_k.sh

@@ -8,7 +8,26 @@
 #This script must remain in CZK_project/Script !!!
 # median means Lambda is derived as (ln 2 / timeout).
 
-
+if [ "$1" == "help" ]; then
+	echo '5 argument are expected :'
+	echo '$1 is the the timeout in second, the one we choose to run tests was 0.1'
+	echo '$2 lambda according to t in {regular,median}'
+	echo '   regular : lambda = 1/t'
+	echo '   median : t will be the median value of the exponential distribution exp(lambda) (ln(2)/t)'
+	echo '$3 is the the precision epsilon in [1-9]+{E-}[1-9]+ format, in prism it is the termination epsilon for power method, in storm it set the --epsilon option (1E-6 is the default value for both PRISM and Storm)'
+	echo '$4 kind_of_epsilon in {dynamic, constant} for dynamic you have eps_computation = eps/k '
+	echo '   constant : the precision epsilon will remain the same for every computations'
+	echo '   dynamic : the precision epsilon will depend on k eps_computation = eps/k'
+	
+	echo '$5 the engine in {event,explicit,hybrid,storm} that will do the computation'
+	echo '   event is the ACTMC model checker'
+	echo '   explicit is the ACTMC model checker for only CTMC model'
+	echo '   hybrid is the PRISM model checker with hybrid engine'
+	echo '   storm is the Storm model checker with sparse engine'
+	echo 'Result :'
+	echo 'It will compute logs and outputs for the specified parameters for a fixed range of k from 1 to 5000 with exponential steps'
+	exit 1
+	fi
 
 #check parameter
 reNum='^[-+]?[0-9]+\.?[0-9]*$'

### 2018-06-25 Script/computeSS_for_different_k_standart_eps.sh

@@ -7,6 +7,21 @@
 #There is only one parameter - floating point number specifying the timeout.
 #Lambda is derived as (ln 2 / timeout).
 
+if [ "$1" == "help" ]; then
+	echo '5 argument are expected :'
+	echo '$1 is the the timeout in second, the one we choose to run tests was 0.1'
+	echo '$2 lambda according to t in {regular,median}'
+	echo '   regular : lambda = 1/t'
+	echo '   median : t will be the median value of the exponential distribution exp(lambda) (ln(2)/t)'
+	echo '$3 the engine in {event,explicit,hybrid,storm} that will do the computation'
+	echo '   event is the ACTMC model checker'
+	echo '   explicit is the ACTMC model checker for only CTMC model'
+	echo '   hybrid is the PRISM model checker with hybrid engine'
+	echo '   storm is the Storm model checker with sparse engine'
+	echo 'Result :'
+	echo 'It will compute logs and outputs for the specified parameters for a fixed range of k from 1 to 5000 with exponential steps without setting any epsilon'
+	exit 1
+	fi
 
 
 #check parameter

### 2018-06-25 Script/computeSum.sh

@@ -8,6 +8,19 @@
 # In the result the kline is the time of computation for the ph_n_k_eps
 # naming : sumph_n_k_epsilon, the folder give the engine and the timeout
 # Are fixed constant : epsilon=1E-5
+
+if [ "$1" == "help" ]; then
+	echo '3 argument are expected :'
+	echo '$1 is the name of the folder which contains the results from "../Output/" example : "t=0.1_median_1E-10_dynamic"'
+	echo '$2 the engine in {explicit,hybrid} that will do the computation'
+	echo '   explicit is the ACTMC model checker for only CTMC model'
+	echo '   hybrid is the PRISM model checker with hybrid engine'
+	echo '$3 is the the precision epsilon in [1-9]+{E-}[1-9]+ format, in prism it is the termination epsilon for power method, in storm it set the --epsilon option (1E-6 is the default value for both PRISM and Storm)'
+	echo 'Result :'
+	echo 'It will compute the compute the steady probability for the set of states with same qSize, in fact we add the probabilities of each states with same qSize, computeTime must be lauched before this script'
+	exit 1
+	fi
+
 path="../Output/"
 subpath=$1
 engine=$2

### 2018-06-25 Script/computeTime.sh

@@ -8,6 +8,29 @@
 # Return a file of computation time for hybrid and explicit engine in both of their folders
 # In the result the kline is the time of computation for the ph_n_k_eps
 # naming : phtime_n_epsilon, the folder give the engine and the timeout
+
+if [ "$1" == "help" ]; then
+	echo '5 argument are expected :'
+	echo '$1 is the the timeout in second, the one we choose to run tests was 0.1'
+	echo '$2 the engine in {event,explicit,hybrid,storm} that will do the computation'
+	echo '   event is the ACTMC model checker'
+	echo '   explicit is the ACTMC model checker for only CTMC model'
+	echo '   hybrid is the PRISM model checker with hybrid engine'
+	echo '   storm is the Storm model checker with sparse engine'
+	echo '$3 lambda according to t in {regular,median}'
+	echo '   regular : lambda = 1/t'
+	echo '   median : t will be the median value of the exponential distribution exp(lambda) (ln(2)/t'
+	echo '$4 is the the precision epsilon in [1-9]+{E-}[1-9]+ format, in prism it is the termination epsilon for power method, in storm it set the --epsilon option (1E-6 is the default value for both PRISM and Storm)'
+	echo '$5 kind_of_epsilon in {dynamic, constant} for dynamic you have eps_computation = eps/k '
+	echo '   constant : the precision epsilon will remain the same for every computations'
+	echo '   dynamic : the precision epsilon will depend on k eps_computation = eps/k'
+	
+
+	echo 'Result :'
+	echo 'It will extract from the logs the time of computation, the result for Storm, the list of ph fiting parameter k used'
+	exit 1
+	fi
+
 reNum='^[-+]?[0-9]+\.?[0-9]*$'
 if ! [[ $1 =~ $reNum ]] ; then
   echo "Please specify number \"timeout\" as the first parameter!"

### 2018-06-25 Script/post_computation.sh

@@ -1,6 +1,17 @@
 #$1 = t
 #$2=eps
 
+
+if [ "$1" == "help" ]; then
+	echo '2 argument are expected :'
+	echo '$1 is the the timeout in second, the one we choose to run tests was 0.1'
+	echo '$2 is the the precision epsilon in [1-9]+{E-}[1-9]+ format, in prism it is the termination epsilon for power method, in storm it set the --epsilon option (1E-6 is the default value for both PRISM and Storm)'
+	echo 'Result :'
+	echo 'It will compute logs and outputs of computations for both dynamic and constant epsilon for Storm, PRISM and ACTMC PRISM into the Output folder'
+	exit 1
+	fi
+	
+	
 ./computeTime.sh "$1" hybrid median "$2" constant
 ./computeTime.sh "$1" hybrid median "$2" dynamic
 

### 2018-06-26 Report/tool_paper.tex
modifying repport
tool_paper change and corrected

@@
 %%% Preamble
-\documentclass[paper=a4, fontsize=11pt]{scrartcl}
-\usepackage[T1]{fontenc}
+\documentclass{article}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+%\documentclass[paper=a4, fontsize=11pt]{scrartcl}
+%\usepackage[T1]{fontenc}
 \usepackage{fourier}
@@
 
+\usepackage[
+backend=biber,
+style=alphabetic,
+citestyle=numeric,
+sorting=none,
+%sortcae=false                  
+%citestyle=authoryear
+]{biblatex}
+
+\addbibresource{tool_paper.bib} %Imports bibliography file
+
 %%% Begin document
@@
 	\section{Introduction}
-	\label{S:1}
+	\label{intro}
 
@@
 	\section{Experimental evaluation}
-	\label{S:2}
+	\label{experimetal_evaluation}
 
@@
 
-	\pagebreak
+	%\pagebreak
 	\subsection{Obtaining precise results for reference}
-	\label{S:2.1}
+	\label{reference}
 
@@
 
+%%	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed.
+To achieve this, we used our own PRISM ACTMC implementation, which is capable of analyzing the given model directly without phase-type fitting.
+Using our implementation, we have computed the steady-state probabilities for very precise termination epsilon $\epsilon = 10^{-20}$ and compared it to the steady-state probabilities obtained by PRISM CTMC with phase-type fitting for $\epsilon = 10^{-16}$ and $k = 1000000$.
+As shown in Figure \ref{fig:diff_storm_dynamic}, the differences between the computations are smaller than $10^6$.
+Under the hypothesis that the true result is closer to the result obtained from PRISM ACTMC than to the result obtained from Storm, we can conclude that the PRISM ACTMC can serve as reference with precision at least $10^{-6}$.%%
+
 	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed.
-To achieve this, we used our own PRISM ACTMC implementation, which is capable of analyzing the given model directly without phase-type fitting.
-Using our implementation, we have computed the steady-state probabilities for very precise termination epsilon $\epsilon = 10^{-20}$ and compared it to the steady-state probabilities obtained by PRISM CTMC with phase-type fitting for $\epsilon = 10^{-16}$ and $k = 800000$.
-As shown in Figure \ref{fig:diff_storm_dynamic}, the differences between the computations are smaller than $10^6$.
-Under the hypothesis that the true result is closer to the result obtained from PRISM ACTMC than to the result obtained from Storm, we can conclude that the PRISM ACTMC can serve as reference with precision at least $10^{-6}$.
+To achieve this, we have modeled the given D/M/1/10 queue in Oris \cite{Bucci2010}.
+The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our PRISM ACTMC implementation up to at least 14 digits.
+Hence, our tool can be considered a trustworthy reference with precision of $10^{-14}$.
 
-	 	\begin{figure}[H]
-		\begin{center}
-			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/diff_storm_dynamic.png}
-		\end{center}
-		\caption{Absolute difference of steady-state probabilities of the CTMC with phase-type fitting ($\epsilon = 10^{-16}$, $k = 800000$) from PRISM ACTMC ($\epsilon = 10^{-20}$).}
-		\label{fig:diff_storm_dynamic}
-	\end{figure}
-
-	\pagebreak
+	%\pagebreak
 	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
-	\label{S:2.2}
+	\label{default_absolute}
 
@@
 	\subsection{Lowering absolute termination epsilon to $\epsilon = 10^{-10}$}
-	\label{S:2.2}
+	\label{lowering}
 
 	For much lower $\epsilon = 10^{-10}$, the precision of the result improves.
-However, for higher $k$ the precision continues to deteriorate like in Section \ref{S:2.2}.
+However, for higher $k$ the precision continues to deteriorate like in Section \ref{lowering}.
 The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.
@@
 
-	\pagebreak
+	%\pagebreak
 	\subsection{Adjusting epsilon $\epsilon = 10^{-10}$ to $k$}
-	\label{S:2.3}
+	\label{adjusting}
 
@@
 	\subsection{Required computation time to obtain precise results}
-	\label{S:2.4}
+	\label{computation_time}
 
@@
 
-	\pagebreak
+	%\pagebreak
 	\section{Conclusion}
@@
 	%% appendix sections are then done as normal sections
-	%% \appendix
+\appendix
 
-	%% \section{}
-	%% \label{}
-
-	%% References
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%REFERENCES%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	%%
@@
 
-	\bibliographystyle{model1-num-names}
-	\bibliography{sample.bib}
+	%\bibliographystyle{model1-num-names}
+	%\bibliographystyle{alpha}	
+	%\bibliography{tool_paper}
+\printbibliography
 

### 2018-06-26 Python/curves.py

@@ -122,17 +122,17 @@ def diff_per_state(t,kind_of_t,engine,eps,kind_of_epsilon,eps_precise):
 				#load the bottom line for explicit
 	y_0 = read_float(path+subpath_ref+'explicit'+'/ev_10_k_'+eps_precise)
 	#invisible plot for scaling
-	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'hybrid'+'/sumph_10_'+str(int(k_hybrid[0]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
-	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'hybrid'+'/sumph_10_'+str(int(k_hybrid[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
+	#~ plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'hybrid'+'/sumph_10_'+str(int(k_hybrid[0]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
+	#~ plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'hybrid'+'/sumph_10_'+str(int(k_hybrid[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
 	#~ plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'explicit'+'/sumph_10_'+str(int(k_array[0]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
 	#~ plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'explicit'+'/sumph_10_'+str(int(k_array[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
-	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'storm'+'/ph_10_'+str(int(k_storm[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
-	plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'storm'+'/ph_10_'+str(int(k_storm[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
+	#~ plt.plot(states,absolute(diff_array(y_0,read_float(path+subpath+'storm'+'/ph_10_'+str(int(k_storm[-1]))+'_'+eps))),'r-', alpha=0.0,linewidth=1.5)
[…]

### 2018-06-26 Report/tool_paper.tex
modification on the repport : removing litteral labelling in bibliography and change the title style

@@
 	%\vspace{-1in} 	
-	\usefont{OT1}{bch}{b}{n}
-	\normalfont \normalsize \textsc{School of random department names} \\ [25pt]
-	\horrule{0.5pt} \\[0.4cm]
-	\huge Efficient modeling of timeouts in PRISM \\
-	\horrule{2pt} \\[0.5cm]
+	%\usefont{OT1}{bch}{b}{n}
+	%\normalfont \normalsize \textsc{School name, institutions,...} \\ [25pt]
+	%\horrule{0.5pt} \\[0.4cm]
+	%\huge Efficient modeling of timeouts in PRISM \\
+	Efficient modeling of timeouts in PRISM \\
+	%\horrule{2pt} \\[0.5cm]
 }
@@
 backend=biber,
-style=alphabetic,
+%this is the label style in the bibliography at the end of document
+style=numeric,
+%this is the label style for each citation in the document
 citestyle=numeric,
@@
 		When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within reasonable time.
-		We ran experimental computations and deduced a reasonable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
+		We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
 		Lastly, we hint at an entirely different (and arguably better) approach to handling non-Markovian distributions.

### 2018-06-27 Report/tool_paper.tex
change in the tool paper

@@
 	tabsize=3,
-	morekeywords={event, gsmp, dirac, exponential, uniform, weibull, erlang,
+	morekeywords={ctmc,event, gsmp, dirac, exponential, uniform, weibull, erlang,
 		module, init, rewards, endrewards, label, true, endmodule}
@@
 		\centering
-		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.67cm,
 		semithick]
@@
 
-		\node[initial,state] (s0)                    {$0$};
+		\node[initial, initial text ={},state] (s0)                    {$0$};
 		\node[state]         (s1) [right of=s0] {$1$};

### 2018-07-11 Script/computeTime.sh
adding computeTime which has previouly disapear

@@ -1,0 +1,181 @@
+#####README
+# The logs (for t) must be already computed 
+# $1 = t(int) the timeout
+# $2 = engine/data in {event,hybrid,explicit,storm}
+# $3 = data_type in {regular,epsilon,median}
+# $4 = epsilon (doesn't count if standard, put "1E-0" or "standard" or anything)
+# $5 kind_of_epsilon in {dynamic, constant, standard} for dynamic you have eps_computation = eps/k 
+# Return a file of computation time for hybrid and explicit engine in both of their folders
+# In the result the kline is the time of computation for the ph_n_k_eps
+# naming : phtime_n_epsilon, the folder give the engine and the timeout
+
+if [ "$1" == "help" ]; then
+	echo '5 argument are expected :'
+	echo '$1 is the the timeout in second, the one we choose to run tests was 0.1'
+	echo '$2 the engine in {event,explicit,hybrid,storm} that will do the computation'
+	echo '   event is the ACTMC model checker'
+	echo '   explicit is the ACTMC model checker for only CTMC model'
+	echo '   hybrid is the PRISM model checker with hybrid engine'
+	echo '   storm is the Storm model checker with sparse engine'
+	echo '$3 lambda according to t in {regular,median}'
+	echo '   regular : lambda = 1/t'
+	echo '   median : t will be the median value of the exponential distribution exp(lambda) (ln(2)/t'
+	echo '$4 is the the precision epsilon in [1-9]+{E-}[1-9]+ format, in prism it is the termination epsilon for power method, in storm it set the --epsilon option (1E-6 is the default value for both PRISM and Storm)'
+	echo '$5 kind_of_epsilon in {dynamic, constant} for dynamic you have eps_computation = eps/k '
+	echo '   constant : the precision epsilon will remain the same for every computations'
+	echo '   dynamic : the precision epsilon will depend on k eps_computation = eps/k'
+	
+
+	echo 'Result :'
[…]

### 2018-07-11 Report/report/paper.tex
updating report

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads,custombib]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

%my package
\usepackage[backend=biber,
%this is the label style in the bibliography at the end of document
style=numeric,
%this is the label style for each citation in the document
citestyle=numeric,
sorting=none,
%sortcae=false                  
%citestyle=authoryear
]{biblatex}
%\usepackage[backend=biber]{biblatex}
\addbibresource{paper.bib} %Imports bibliography file

\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{tikz}
\usetikzlibrary{chains,shapes.multipart}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

\begin{document}
%
\title{Continuous-Time Markov Chain with Alarms analysis and comparaison of tools \thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thomas Mari\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
	Phase-type fitting remains the only way of modeling non-Markovian distributions within PRISM model checker.
	When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within reasonable time.
	We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
	Lastly, we hint at an entirely different (and arguably better) approach to handling non-Markovian distributions.

The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{PRISM model checker \and CTMC \and deterministic timeout \and phase-type distribution \and modeling \and analysis  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}

	PRISM \cite{KNP11} and Storm \cite{DBLP:journals/corr/DehnertJK017} are popular tools for modeling and analysis of stochastic systems in continuous time. They use efficient algorithms for analysis of continuous time Markov chains (CTMC). This approach suffers from a severe restriction of modeling power --- the time between transitions must be exponentially distributed. This restriction can be remedied by the use of phase-type distributions, which can approximate any general distribution with arbitrary accuracy by only using exponential distributions \cite{Buchholz:2014:IMP:2683922}. However, the use of phase-type distributions drastically increases the number of states within the CTMC.

	In this paper, we experimentally evaluate the precision of the result and required computation time of various approaches to analysis of continuous time stochastic models with deterministic transitions (timeouts). The obtained results are then compared against results of our extension of PRISM capable of efficiently analyzing CTMC with non-Markovian alarms (ACTMC).

\subsection{Time distribution}
The model we use are probabilistic continuous time model, which means that the time passed in a state will depend on a time distribution. A time distribution can be depicted by its cumulative distribution function (CDF) $F : \mathbb{R} \rightarrow[0,1]$, $F(t)$ is the probability that the event will happend before the time $t$. The exponential distribution of rate $\lambda$ has a CDF $F(t) = 1 - \exp(-\lambda t)$, it is important to keep in mind that a rate refers to the exponential distribution. The Dirac distribution of timeout $\tau$ has a CDF $F(t) = \chi_{[\tau,+\infty[}(t) = 
\left\{
	\begin{array}{l}
		0 \text{ if } t < \tau\\
		1\text{ else}
	\end{array}
\right.$. In this paper, time distribution which are not exponential will be called non-Markovian distribution.
\subsection{CTMC}
A continuous-time Markov chain (CTMC) is a triple $C = (S,Q,s_{in})$, where 
\begin{itemize}
	\item[$\bullet$] S is a finite set of states
	\item[$\bullet$] $Q : S \times S \rightarrow \mathbb{R}_{\geq 0}$ is a matrix of rates such that $\sum_{s' \in S} Q(s,s')  > 0$ for each $s \in S$
	\item[$\bullet$] $s_{in} \in S$ is an initial state
\end{itemize} 
We define the exit rate of state $s$ as $\lambda_s = \sum_{s' \in S} Q(s,s')$

A run of a CTMC $\mathcal{C}$ is an infinite alternating sequence of states and times $\omega = s_0t_0s_1t_1...$ where 
\begin{itemize}
	\item[$\bullet$] $s_0 = s_{in}$
	\item[$\bullet$] $s_i$ is the i-th state
	\item[$\bullet$] $t_i$ is the time spent in $s_i$
\end{itemize}

For each $i \in \mathbb{N}$ \begin{itemize}
	\item[$\bullet$] $t_i$ is choosen randomly according to the exponential distribution with rate $\lambda_{s_i}$
	\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $\dfrac{Q(s_i,.)}{\lambda_{s_i}}$
\end{itemize}

\subsection{ACTMC}

Continuous-Time Markov Chain with Alarms (ACTMC)s. I won't give the formal semantics which might not fit in this paper. We can see ACTMC as CTMC with some events called alarms that are enabled in disjoints sets of states and those events has their own timer which is active only when inside the enabled set and happend according to some continuous time distribution. Those alarms works concurrently with the exponential transition seen in the CTMC.

$\mathcal{A} = (S,Q,s_{in},A,\langle S_a \rangle,\langle P_a \rangle,\langle F_a \rangle)$
where :
\begin{itemize}
	\item[$\bullet$]$(S,Q,s_{in})$ is a CTMC
	\item[$\bullet$] $A$ is a set of alarms
	\item[$\bullet$] $\langle S_a \rangle = (S_a)_{a \in A}$, the set of states where $a$ is enabled
		\begin{itemize}
			\item[$\bullet$] if $a \neq a'$ then $S_a \bigcap S_{a'} = \emptyset$ 
		\end{itemize}
	\item[$\bullet$]$\langle P_a \rangle = (P_a)_{a \in A}$ where $P_a$ is a probability matrix
	\item[$\bullet$]$\langle F_a \rangle = (F_a)_{a \in A}$ where $F_a$ is a cumulative distribution function (CDF) 
\end{itemize}

Operational Behavior

A run of a ACTMC $\mathcal{A}$ is an infinite alternating sequence of states and times $(s_0,\eta_0)t_0(s_1,\eta_1)t_1...$ where 
\begin{itemize}
	\item[$\bullet$] $s_0 = s_{in}$
	\item[$\bullet$] $s_i$ is the i-th state
	\item[$\bullet$] $t_i$ is the delay in $s_i$, $t_i$ is the time spent in $s_i$ without alarms
	\item[$\bullet$] $\eta_i$ is the value of the timer, the remaining time for the alarm to ring.
\end{itemize}
We define $S_{off} = S\setminus\bigcup_{a \in A} S_a$ the set of states where no alarms are enabled

For initialization
\begin{itemize}
	\item[$\bullet$] $s_0 = s{in}$
	\item[$\bullet$] $\eta_0 =$
	$\left\{
		\begin{array}{l}
		\infty \text{ if } s_0 \in S_{off}\\
		 \text{randomly choosen according to }F_a\text{ if } s_0 \in S_{a}
		\end{array}
		\right.$ 
\end{itemize}
For each $i \in \mathbb{N}, t_i$ is choosen randomly according to the exponential distribution $\lambda_{s_i}$

Two cases are possible, either the alarm ring ($\eta_i \leq t_i$) or $t_i$ is too short and the alarm doesn't ring.

If $\eta_i \leq t_i$, the alarm ring
\begin{itemize}
	\item[$\bullet$] $t_i := \eta_i$ the value of delay is overwritten and match the time spent in $s_i$
	\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $P_a(s_i,.)$
	\item[$\bullet$] $\eta_{i+1} =$
	$\left\{
	\begin{array}{l}
		\infty \text{ if } s_{i+1} \in S_{off}\\
		\text{randomly choosen according to }F_a\text{ if } s_{i+1} \in S_{a}
	\end{array}
	\right.$ 
\end{itemize}

If $\eta_i > t_i$, the alarm does not ring
\begin{itemize}
	\item[$\bullet$] $t_i$ the value of delay remain the same and match the time spent in $s_i$
\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $\dfrac{Q(s_i,.)}{\lambda_{s_i}}$
	\item[$\bullet$] $\eta_{i+1} =$
	$\left\{
	\begin{array}{l}
	\infty \text{ if } s_{i+1} \in S_{off}\\
	\eta_i - t\text{ if }s_{i+1} \in S_{a}\text{ and }s_{i} \in S_{a}\\
	\text{randomly choosen according to }F_a\text{ if }s_{i+1} \in S_{a}\text{ and }s_{i} \notin S_{a}
	\end{array}
	\right.$ 
\end{itemize}
 If the state remain in the set enabled by the alarm, it is updated. Otherwise it is reset according to the new enabled set.

\subsection{Phase Type fitting}
Phase Type fitting (PH fitting) is approaching a non-Markovian distribution by a sequence of exponential distributions. 
Consider an infinite sequence of finite sequences of rates of length k $((\lambda_{i,k})_{i=0}^{k})_{k \in \mathbb{N}}$. We want that the distribution of the sequence of exponential transitions to converge to the non-Markovian distribution.

To obtain analysis on ACTMC, we use PH fitting to create CTMC from ACTMC, and analyse those CTMC Then we deduce results on the ACTMC.  The reason is that Prism or Storm can use CTMC and not ACTMC. Figure \ref{fig:simple_actmc} and figure \ref{fig:simple_ctmc} are a toy example of the PH fitting of a simple ACTMC $\mathcal{A} = (\{A,B\},
\begin{bmatrix}
	1       & 3 \\
	2       & 1 
\end{bmatrix}
,A,\{A\},
\begin{bmatrix}
1       & 0
\end{bmatrix}
,\{d\})$ with constant parameter $k$. The created CTMC is $\mathcal{C} = (\{A,B,1,2,...,k-1,B\},
\begin{bmatrix}
0       & \lambda_{1,k} 	& 0		& 0		& ...		& 0\\
0       & 0 	& \lambda_{2,k}		& 0		& ...		& 0\\
0       & 0 	& 0		& \lambda_{3,k}		& ...		& 0\\
0       & 0 	& 0		& 0		& ...		& 0\\
...       & ... 	& ...		& ...		& ...		& \lambda_{k,k}\\
0       & 0 	& 0		& 0		& 0		& 0
\end{bmatrix}
,A)$

EXIT RATE > 0 §!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
	\begin{figure}
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.80cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[state] (s0)                    {$A$};
		\node[state]         (sn) [right of=s0]       {$B$};
		\path[->, dashed]
		(s0) edge 	node {$d$} (sn);

		\end{tikzpicture}
		\caption{Model of a simple ACTMC $\mathcal{A}$, $d$ is a non-Markovian distribution.}
		\label{fig:simple_actmc}
	\end{figure}

	\begin{figure}
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.80cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[state] (s0)                    {$A$};
		\node[state]         (s1) [right of=s0] {$1$};
		\node[state]         (s2) [right of=s1] {$2$};
		\node[state,draw=none]         (s4) [right of=s2]       {$...$};
		\node[state]         (sw) [right of=s4,fill=white,text=black]       {$k-1$};
		\node[state]         (sn) [right of=sw]       {$B$};

		\path[->]  
		(s0) edge	node {$\lambda_{k,1}$} (s1);
		\path[->]

		[->]
		(s1) edge	node {$\lambda_{k,2}$} (s2);
		\path[->]

		(s2) edge   node {$\lambda_{k,3}$} (s4);
		\path[->]

		(s4) edge   node {$\lambda_{k,k-1}$} (sw);
		\path[->]

		(sw) edge   node {$\lambda_{k,k}$} (sn);
		\path[->];
		\end{tikzpicture}
		\caption{Model of a CTMC obtain by PH fitting of the ACTMC figure \ref{fig:simple_actmc}.}
		\label{fig:simple_ctmc}
	\end{figure}

\section{Related Work}
Maybe talk about the previous work of vojta and lubosh

\section{Contribution}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
\section{Conclusion}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}

\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017

\printbibliography

\end{thebibliography}
\end{document}

### 2018-07-12 Report/report/paper.tex
change in the paper for my institution

@@
 \end{itemize} 
+$Q(s,s')$ is the rate of the transition from $s$ to $s'$.
 We define the exit rate of state $s$ as $\lambda_s = \sum_{s' \in S} Q(s,s')$
@@
 \begin{bmatrix}
-	1       & 3 \\
+	0.5       & 0 \\
 	2       & 1 
@@
 		(s0) edge 	node {$d$} (sn);
+		\path[->]
+		(s0) edge [loop left]	node {0.5} (s0)
 
+		(sn) edge [bend left]	node {2} (s0)
+		edge [loop right]	node {1} (sn);			
 		\end{tikzpicture}
@@
 		\path[->]  
-		(s0) edge	node {$\lambda_{k,1}$} (s1);
+		(s0) edge	node {$\lambda_{k,1}$} (s1)
+			edge [loop above]	node {0.5} (s0);
 		\path[->]
@@
 		[->]
-		(s1) edge	node {$\lambda_{k,2}$} (s2);
+		(s1) edge	node {$\lambda_{k,2}$} (s2)
+			edge [loop above]	node {0.5} (s1);
 		\path[->]
 
-		(s2) edge   node {$\lambda_{k,3}$} (s4);
+		(s2) edge   node {$\lambda_{k,3}$} (s4)
+			edge [loop above]	node {0.5} (s2);
 		\path[->]
 
-		(s4) edge   node {$\lambda_{k,k-1}$} (sw);
+		(s4) edge   node {$\lambda_{k,k-1}$} (sw)
+			edge [loop above]	node {0.5} (s4);
 		\path[->]
 
-		(sw) edge   node {$\lambda_{k,k}$} (sn);
-		\path[->];
+		(sw) edge   node {$\lambda_{k,k}$} (sn)
+			edge [loop above]	node {0.5} (sw);
+		\path[->]
+
+		(sn) edge [bend left]	node {2} (s0)
+		edge [loop right]	node {1} (sn);
 		\end{tikzpicture}

### 2018-07-13 Script/firstRejuvenation/firstRejuvenation.sh
adding the computation of yesterday

@@ -1,6 +1,5 @@
 #Here you can set the sequence of k computed
 sequence=$(seq 1 1 9; seq 10 10 90; seq 100 100 900; seq 1000 1000 4000; seq 5000 5000 5000);
-epsilon = 1E-6
 
 for eps in 1E-6 1E-10 1E-15 1E-20
 	do

### 2018-07-13 Script/firstRejuvenation/computeTime.sh
adding postcomputation

@@ -94,7 +94,7 @@ echo done
 echo epsilon and time ...
 
 if [[ $1 =~ 'event' ]]; then
-	file=$path$subpath$data'_10_k_'$2'.log'
+	file=$path$subpath$data'_k_'$2'.log'
 	echo $file
 	#epsilon
 	grep 'epsilon' $file > temp_eps0

### 2018-07-13 Script/firstRejuvenation/firstRejuvenation.sh

@@ -1,17 +1,35 @@
-#Here you can set the sequence of k computed
-sequence=$(seq 1 1 9; seq 10 10 90; seq 100 100 900; seq 1000 1000 4000; seq 5000 5000 5000);
+#~ #Here you can set the sequence of k computed
+#~ sequence=$(seq 1 1 9; seq 10 10 90; seq 100 100 900; seq 1000 1000 4000; seq 5000 5000 5000);
 
-for eps in 1E-6 1E-10 1E-15 1E-20
-	do
-	./computeSS_firstRejuvenation.sh $eps event
-	done
+#~ for eps in 1E-6 1E-10 1E-15 1E-20
+	#~ do
+	#~ ./computeSS_firstRejuvenation.sh $eps event
+	#~ done
 
 
-for eps in 1E-6 1E-10
-	do
-		for k in $sequence
-			do
-			./computeSS_firstRejuvenation.sh $eps hybrid constant "$k" 
-			./computeSS_firstRejuvenation.sh $eps hybrid dynamic "$k" 
-			done
-	done
+#~ for eps in 1E-6 1E-10
+	#~ do
+		#~ for k in $sequence
+			#~ do
+			#~ ./computeSS_firstRejuvenation.sh $eps hybrid constant "$k" 
+			#~ ./computeSS_firstRejuvenation.sh $eps hybrid dynamic "$k" 
+			#~ done
+	#~ done
+
+#####COMPUTETIME
+	./computeTime.sh event 1E-6 constant
+	./computeTime.sh event 1E-10 constant
+	./computeTime.sh event 1E-15 constant
+	./computeTime.sh event 1E-20 constant
+	
+	./computeTime.sh hybrid 1E-6 constant
+	./computeTime.sh hybrid 1E-10 constant
+	
+	./computeTime.sh hybrid 1E-6 dynamic
+	./computeTime.sh hybrid 1E-10 dynamic
+
+####COMUTESUM
+	./computeSum.sh firstRejuvenation_1E-6_dynamic hybrid 1E-6
+	./computeSum.sh firstRejuvenation_1E-6_constant hybrid 1E-6
+	./computeSum.sh firstRejuvenation_1E-10_dynamic hybrid 1E-10
+	./computeSum.sh firstRejuvenation_1E-10_constant hybrid 1E-10

### 2018-07-23 Report/report/paper.tex
modification of my institution paper

--- 2018-07-11 Report/report/paper.tex
@@
 
+\usepackage{listings}
+\usepackage{color}
+\usepackage{float}
+
+%% BEGIN PRISM CODE LISTING 
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+
+\lstset{frame=tb,
+	language=Java,
+	aboveskip=1mm,
+	belowskip=1mm,
+	showstringspaces=false,
+	columns=flexible,
+	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
+	numbers=none,
+	numberstyle=\tiny\color{gray},
+	keywordstyle=\color{blue},
+	commentstyle=\color{dkgreen},
+	breaklines=true,
+	breakatwhitespace=true,
+	tabsize=3,
+	morekeywords={ctmc,event, gsmp, dirac, exponential, uniform, weibull, erlang,
+		module, init, rewards, endrewards, label, true, endmodule}
+}
+\usepackage{csquotes}
+
+\usepackage{hyperref}
+
 \begin{document}
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+\institute{ENS-Rennes, Campus de Ker lann, Avenue Robert Schuman, 35170 Bruz, France \and
+Masaryk University, Botanická 68A, 602 00 Brno-Královo Pole, Czech republic
 \email{lncs@springer.com}\\
@@
 
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+%The abstract should briefly summarize the contents of the paper in
+%150--250 words.
 
-\keywords{PRISM model checker \and CTMC \and deterministic timeout \and phase-type distribution \and modeling \and analysis  \and Second keyword \and Another keyword.}
+\keywords{PRISM model checker \and CTMC \and deterministic timeout \and phase-type distribution \and modeling \and analysis.}
 \end{abstract}
@@
 They use efficient algorithms for analysis of continuous time Markov chains (CTMC).
-This approach suffers from a severe restriction of modeling power --- the time between transitions must be exponentially distributed.
+This approach suffers from a severe restriction of expressiveness, because the time between transitions must be exponentially distributed.
 This restriction can be remedied by the use of phase-type distributions, which can approximate any general distribution with arbitrary accuracy by only using exponential distributions \cite{Buchholz:2014:IMP:2683922}.
@@
 
-\subsection{Time distribution}
-The model we use are probabilistic continuous time model, which means that the time passed in a state will depend on a time distribution.
-A time distribution can be depicted by its cumulative distribution function (CDF) $F : \mathbb{R} \rightarrow[0,1]$, $F(t)$ is the probability that the event will happend before the time $t$.
-The exponential distribution of rate $\lambda$ has a CDF $F(t) = 1 - \exp(-\lambda t)$, it is important to keep in mind that a rate refers to the exponential distribution.
-The Dirac distribution of timeout $\tau$ has a CDF $F(t) = \chi_{[\tau,+\infty[}(t) =
-\left\{
-	\begin{array}{l}
-		0 \text{ if } t < \tau\\
-		1\text{ else}
-	\end{array}
-\right.$. In this paper, time distribution which are not exponential will be called non-Markovian distribution.
-\subsection{CTMC}
-A continuous-time Markov chain (CTMC) is a triple $C = (S,Q,s_{in})$, where 
-\begin{itemize}
-	\item[$\bullet$] S is a finite set of states
-	\item[$\bullet$] $Q : S \times S \rightarrow \mathbb{R}_{\geq 0}$ is a matrix of rates such that $\sum_{s' \in S} Q(s,s')  > 0$ for each $s \in S$
-	\item[$\bullet$] $s_{in} \in S$ is an initial state
-\end{itemize} 
-We define the exit rate of state $s$ as $\lambda_s = \sum_{s' \in S} Q(s,s')$
+%	BIGGER INTRO
 
-A run of a CTMC $\mathcal{C}$ is an infinite alternating sequence of states and times $\omega = s_0t_0s_1t_1...$ where 
-\begin{itemize}
-	\item[$\bullet$] $s_0 = s_{in}$
-	\item[$\bullet$] $s_i$ is the i-th state
-	\item[$\bullet$] $t_i$ is the time spent in $s_i$
-\end{itemize}
+	We will go through the theoretical bases needed to understand the contribution. CITE LUBOSH'THESIS
 
-For each $i \in \mathbb{N}$ \begin{itemize}
-	\item[$\bullet$] $t_i$ is choosen randomly according to the exponential distribution with rate $\lambda_{s_i}$
-	\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $\dfrac{Q(s_i,.)}{\lambda_{s_i}}$
-\end{itemize}
+\section{Related Work}
+\input{related_work.tex}
 
-\subsection{ACTMC}
+\section{Preliminaries}
+\input{preliminaries.tex}
 
-Continuous-Time Markov Chain with Alarms (ACTMC)s.
-I won't give the formal semantics which might not fit in this paper.
-We can see ACTMC as CTMC with some events called alarms that are enabled in disjoints sets of states and those events has their own timer which is active only when inside the enabled set and happend according to some continuous time distribution.
-Those alarms works concurrently with the exponential transition seen in the CTMC.
+	\section{Experimental evaluation}
+	\label{experimetal_evaluation}
 
-$\mathcal{A} = (S,Q,s_{in},A,\langle S_a \rangle,\langle P_a \rangle,\langle F_a \rangle)$
-where :
-\begin{itemize}
-	\item[$\bullet$]$(S,Q,s_{in})$ is a CTMC
-	\item[$\bullet$] $A$ is a set of alarms
-	\item[$\bullet$] $\langle S_a \rangle = (S_a)_{a \in A}$, the set of states where $a$ is enabled
-		\begin{itemize}
-			\item[$\bullet$] if $a \neq a'$ then $S_a \bigcap S_{a'} = \emptyset$ 
-		\end{itemize}
-	\item[$\bullet$]$\langle P_a \rangle = (P_a)_{a \in A}$ where $P_a$ is a probability matrix
-	\item[$\bullet$]$\langle F_a \rangle = (F_a)_{a \in A}$ where $F_a$ is a cumulative distribution function (CDF) 
-\end{itemize}
-
-Operational Behavior
-
-A run of a ACTMC $\mathcal{A}$ is an infinite alternating sequence of states and times $(s_0,\eta_0)t_0(s_1,\eta_1)t_1...$ where 
-\begin{itemize}
-	\item[$\bullet$] $s_0 = s_{in}$
-	\item[$\bullet$] $s_i$ is the i-th state
-	\item[$\bullet$] $t_i$ is the delay in $s_i$, $t_i$ is the time spent in $s_i$ without alarms
-	\item[$\bullet$] $\eta_i$ is the value of the timer, the remaining time for the alarm to ring.
-\end{itemize}
-We define $S_{off} = S\setminus\bigcup_{a \in A} S_a$ the set of states where no alarms are enabled
-
-For initialization
-\begin{itemize}
-	\item[$\bullet$] $s_0 = s{in}$
-	\item[$\bullet$] $\eta_0 =$
-	$\left\{
-		\begin{array}{l}
-		\infty \text{ if } s_0 \in S_{off}\\
-		 \text{randomly choosen according to }F_a\text{ if } s_0 \in S_{a}
-		\end{array}
-		\right.$ 
-\end{itemize}
-For each $i \in \mathbb{N}, t_i$ is choosen randomly according to the exponential distribution $\lambda_{s_i}$
-
-Two cases are possible, either the alarm ring ($\eta_i \leq t_i$) or $t_i$ is too short and the alarm doesn't ring.
-
-If $\eta_i \leq t_i$, the alarm ring
-\begin{itemize}
-	\item[$\bullet$] $t_i := \eta_i$ the value of delay is overwritten and match the time spent in $s_i$
-	\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $P_a(s_i,.)$
-	\item[$\bullet$] $\eta_{i+1} =$
-	$\left\{
-	\begin{array}{l}
-		\infty \text{ if } s_{i+1} \in S_{off}\\
-		\text{randomly choosen according to }F_a\text{ if } s_{i+1} \in S_{a}
-	\end{array}
-	\right.$ 
-\end{itemize}
-
-If $\eta_i > t_i$, the alarm does not ring
-\begin{itemize}
-	\item[$\bullet$] $t_i$ the value of delay remain the same and match the time spent in $s_i$
-\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $\dfrac{Q(s_i,.)}{\lambda_{s_i}}$
-	\item[$\bullet$] $\eta_{i+1} =$
-	$\left\{
-	\begin{array}{l}
-	\infty \text{ if } s_{i+1} \in S_{off}\\
-	\eta_i - t\text{ if }s_{i+1} \in S_{a}\text{ and }s_{i} \in S_{a}\\
-	\text{randomly choosen according to }F_a\text{ if }s_{i+1} \in S_{a}\text{ and }s_{i} \notin S_{a}
-	\end{array}
-	\right.$ 
-\end{itemize}
- If the state remain in the set enabled by the alarm, it is updated. Otherwise it is reset according to the new enabled set.
-
-\subsection{Phase Type fitting}
-Phase Type fitting (PH fitting) is approaching a non-Markovian distribution by a sequence of exponential distributions. 
-Consider an infinite sequence of finite sequences of rates of length k $((\lambda_{i,k})_{i=0}^{k})_{k \in \mathbb{N}}$.
-We want that the distribution of the sequence of exponential transitions to converge to the non-Markovian distribution.
-
-To obtain analysis on ACTMC, we use PH fitting to create CTMC from ACTMC, and analyse those CTMC Then we deduce results on the ACTMC.
-The reason is that Prism or Storm can use CTMC and not ACTMC.
-Figure \ref{fig:simple_actmc} and figure \ref{fig:simple_ctmc} are a toy example of the PH fitting of a simple ACTMC $\mathcal{A} = (\{A,B\},
-\begin{bmatrix}
-	1       & 3 \\
-	2       & 1 
-\end{bmatrix}
-,A,\{A\},
-\begin{bmatrix}
-1       & 0
-\end{bmatrix}
-,\{d\})$ with constant parameter $k$. The created CTMC is $\mathcal{C} = (\{A,B,1,2,...,k-1,B\},
-\begin{bmatrix}
-0       & \lambda_{1,k} 	& 0		& 0		& ...		& 0\\
-0       & 0 	& \lambda_{2,k}		& 0		& ...		& 0\\
-0       & 0 	& 0		& \lambda_{3,k}		& ...		& 0\\
-0       & 0 	& 0		& 0		& ...		& 0\\
-...       & ... 	& ...		& ...		& ...		& \lambda_{k,k}\\
-0       & 0 	& 0		& 0		& 0		& 0
-\end{bmatrix}
-,A)$
-
-EXIT RATE > 0 §!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-	\begin{figure}
+	\begin{figure}[H]
 		\centering
-		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.80cm,
+		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.67cm,
 		semithick]
@@
 
-		\node[state] (s0)                    {$A$};
-		\node[state]         (sn) [right of=s0]       {$B$};
+		\node[initial, initial text ={},state] (s0)                    {$0$};
+		\node[state]         (s1) [right of=s0] {$1$};
+		\node[state]         (s2) [right of=s1] {$2$};
+		\node[state]         (s3) [right of=s2] {$3$};
+		\node[state]         (s4) [right of=s3]       {$4$};
+		\node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
+		\node[state]         (sn) [right of=sw]       {$10$};
+
 		\path[->, dashed]  
-		(s0) edge 	node {$d$} (sn);
-
+		(s0) edge [bend left]             node {$t$} (s1);
+		\path[->]
+		(s1) edge [bend left] node {$\lambda$} (s0);
+		\path[->, dashed]
+		(s1) edge  [bend left]            node {$t$} (s2);
+		\path[->]
+		(s2) edge [bend left]             node {$\lambda$} (s1);
+		\path[->, dashed]
+		(s2) edge [bend left]  node {$t$} (s3);
+		\path[->]
+		(s3) edge [bend left]              node {$\lambda$} (s2);
+		\path[->, dashed]
+		(s3) edge [bend left]  node {$t$} (s4);
+		\path[->]
+		(s4) edge [bend left]             node {$\lambda$} (s3);
+		\path[->, dashed]
+		(s4) edge [bend left]  node {$t$} (sw);
+		\path[->]
+		(sw) edge [bend left]             node {$\lambda$} (s4);
+		\path[->, dashed]
+		(sw) edge [bend left]  node {$t$} (sn);
+		\path[->]
+		(sn) edge [bend left]             node {$\lambda$} (sw);
+		\path[->, dashed]
+		(sn) edge [loop right]  node {$t$} (sn);
 		\end{tikzpicture}
-		\caption{Model of a simple ACTMC $\mathcal{A}$, $d$ is a non-Markovian distribution.}
-		\label{fig:simple_actmc}
+		\caption{Model of a D/M/1/10 queue with production timeout $t = 0.1$ and service rate $\lambda = \frac{ln(2)}{t} \approx 6.931471805599453094$.
+The deterministic arrival event does not reset when the exponential service event occurs.}
+		\label{fig:D/M/1/10}
 	\end{figure}
 
-	\begin{figure}
-		\centering
-		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.80cm,
-		semithick]
-		\tikzstyle{every state}=[fill=white,draw=black,text=black]
+	We have chosen to model a D/M/1/10 queue (deterministic arrivals, exponentially distributed service, single server, capacity of 10) as shown in Figure \ref{fig:D/M/1/10}.
+The deterministic arrivals are approximated by a phase-type distribution, so the model remains a CTMC and can be analyzed by PRISM.
+The PRISM model we used is shown in Figure \ref{fig:D/M/1/10_PRISM}.
+	We computed the steady-state distribution with various values of PRISM termination epsilon $\epsilon$ and the number of phases $k$.
 
-		\node[state] (s0)                    {$A$};
-		\node[state]         (s1) [right of=s0] {$1$};
-		\node[state]         (s2) [right of=s1] {$2$};
-		\node[state,draw=none]         (s4) [right of=s2]       {$...$};
-		\node[state]         (sw) [right of=s4,fill=white,text=black]       {$k-1$};
-		\node[state]         (sn) [right of=sw]       {$B$};
+	\begin{figure}[H]
+		\begin{lstlisting}
+		ctmc
 
-		\path[->]  
-		(s0) edge	node {$\lambda_{k,1}$} (s1);
-		\path[->]
+		const int k;
+		const int qCapacity = 10;
+		const double timeout = 0.1;
+		const double lambda = 6.931471805599453094;
 
-		[->]
-		(s1) edge	node {$\lambda_{k,2}$} (s2);
-		\path[->]
+		module main
 
-		(s2) edge   node {$\lambda_{k,3}$} (s4);
-		\path[->]
+		qSize : [0..qCapacity] init 0;
 
-		(s4) edge   node {$\lambda_{k,k-1}$} (sw);
-		\path[->]
+		[produce] (qSize <= qCapacity) -> (qSize' = min(qSize+1,qCapacity));
+		[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);
 
-		(sw) edge   node {$\lambda_{k,k}$} (sn);
-		\path[->];
-		\end{tikzpicture}
-		\caption{Model of a CTMC obtain by PH fitting of the ACTMC figure \ref{fig:simple_actmc}.}
-		\label{fig:simple_ctmc}
+		endmodule
+
+		module trigger
+
+		i : [1..k+1];
+
+		[] i < k -> k/timeout : (i'=i+1);
+		[produce] i = k -> k/timeout : (i'=1);
+
+		endmodule
+		\end{lstlisting}
+		\caption{PRISM CTMC model of the D/M/1/10 queue as shown in Figure \ref{fig:D/M/1/10} with a phase-type distribution approximating the arrival timeout.
+The phase-type module \emph{trigger} is used as suggested on the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.
+Phase-type parameter $k$ represents the number of phases.
+Increasing $k$ should improve the approximation of the timeout.
+}
+		\label{fig:D/M/1/10_PRISM}
 	\end{figure}
 
-\section{Related Work}
-Maybe talk about the previous work of vojta and lubosh
+	%\pagebreak
+	\subsection{Obtaining precise results for reference}
+	\label{reference}
 
-\section{Contribution}
+	%%%	In order to obtain some steady-state probabilities of reference to compare precision of different tools and engines, we computed the same steady-state probabilities two different ways.
+The first one is the phase type fitting method described as above (ref to the first page).
+The second one is by using our PRISM ACTMC implementation with precise termination epsilon.
+	%%%	 the computation  results are quite similar as shown in picture citation
+
+	%%%	 put picture diff_per_stqte 
+	%%%	 explain picture
+
+	%%% little conclusion: we can from now trust the event model as a reference
+
+	%%	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed.
+To achieve this, we used our own PRISM ACTMC implementation, which is capable of analyzing the given model directly without phase-type fitting.
+Using our implementation, we have computed the steady-state probabilities for very precise termination epsilon $\epsilon = 10^{-20}$ and compared it to the steady-state probabilities obtained by PRISM CTMC with phase-type fitting for $\epsilon = 10^{-16}$ and $k = 1000000$.
+As shown in Figure \ref{fig:diff_storm_dynamic}, the differences between the computations are smaller than $10^6$.
+Under the hypothesis that the true result is closer to the result obtained from PRISM ACTMC than to the result obtained from Storm, we can conclude that the PRISM ACTMC can serve as reference with precision at least $10^{-6}$.%%
+
+	In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed.
+To achieve this, we have modeled the given D/M/1/10 queue in Oris \cite{Bucci2010}.
+The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our PRISM ACTMC implementation up to at least 14 digits.
+Hence, our tool can be considered a trustworthy reference with precision of $10^{-14}$.
+
+	I THINK AT THIS POINT OF THE ARTICLE, IT IS NOT OBVIOUS THAT OUR TOOL REFER TO PRISM GSMP 
+	%\pagebreak
+	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
+	\label{default_absolute}
+
+	First, we used the PRISM default absolute termination epsilon $\epsilon = 10^{-6}$.
+The results are shown in Figure \ref{fig:distance_constant_standard_constant_kappa}.
+For this $\epsilon$, the obtained results are arguably insufficient.
+Increasing $k$ does little to improve the precision, and only up to about $k \leq 50$, at which point increasing $k$ further starts making the precision worse.
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-6/distance_constant_1E-6.png}
+		\end{center}
+		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for default absolute termination epsilon $\epsilon = 10^{-6}$.
+ACTMC results for $\epsilon = 10^{-6}$ are also compared to the reference.}
+		\label{fig:distance_constant_standard_constant_kappa}
+	\end{figure}
+
+	%\pagebreak
+	\subsection{Lowering absolute termination epsilon to $\epsilon = 10^{-10}$}
+	\label{lowering}
+
+	For much lower $\epsilon = 10^{-10}$, the precision of the result improves.
+However, for higher $k$ the precision continues to deteriorate like in Section \ref{lowering}.
+The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-10/distance_constant_1E-10.png}
+		\end{center}
+		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered absolute termination epsilon $\epsilon = 10^{-10}$.
+ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference.}
+		\label{fig:distance_constant_1E-10_constant_kappa}
+	\end{figure}
+
+	%\pagebreak
+	\subsection{Adjusting epsilon $\epsilon = 10^{-10}$ to $k$}
+	\label{adjusting}
+
+	Since increasing $k$ increases the amount of phases (intermediate states) and each phase may have error up to $\epsilon$, the actual potential error for each state of the queue is $\epsilon \cdot k$.
+To compensate for this, we devise a simple formula
+	$$\epsilon^{'} = \frac{\epsilon}{k}$$
+	where $\epsilon^{'}$ is the adjusted epsilon that should be given to PRISM if precision $\epsilon$ is desired for $k$ phases.
+	Using adjusted epsilon, the results get significantly better, as shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}.
+What's more, the phase-type fitting results now seem to converge towards the reference steadily as $k$ increases.
+This indicates that this approach is correct, and that the reference is trustworthy.
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-10/distance_dynamic_1E-10.png}
+		\end{center}
+		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$.
+ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference.}
+		\label{fig:distance_dynamic_1E-10_constant_kappa}
+	\end{figure}
+
+	\subsection{Required computation time to obtain precise results}
+	\label{computation_time}
+
+	Although we have shown it is possible to obtain relatively precise results using phase-type distributions, the precision comes at a rather steep cost in computation time.
+This is shown in Figure \ref{fig:performance_dynamic}.
+Note that even though Storm is one of the fastest available tools, it still struggles to deliver good precision within reasonable time.
+The computations all ran on the same virtual machine under same conditions\footnote{Running in a virtual machine might have reduced the performance.
+The virtual machine we used is available at the \href{http://www.stormchecker.org/documentation/vm/vm.html}{Storm website}.}.
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-6/performance_dynamic.png}
+		\end{center}
+		\caption{Time of computation in seconds of the steady-state probabilities against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$, i.e.
+corresponding to the data shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}.
+The computation of our PRISM ACTMC is constant in regards to $k$ because it does not use phase-type fitting.
+}
+		\label{fig:performance_dynamic}
+	\end{figure}
+
+	\subsection{Another Model : firstRejuvenation}
+
+	We can observe similar results in terms of lack of precision on another model Figure \ref{fig:fr_1E-10_constant}.
+The precision must also depend on the PH fitting parameter k in this model.
+Here we went through difficulties related to the methods used by the engine in Prism.
+The Power method for computing SSP uses different iterations which are matrix multiplication.
+The number of iteration will strongly depend on the model and its parameter like timeouts and rates.
+In the First Rejuvenation model The convergence for the power method is really slow and the number of iteration required is important.
+In the queue, 100 000 000 iterations was enough to compute the SSP, but here the number of iteration prevent us to compute the SSP for k greater than 1000 with reasonable precision.
+
+	The results of computation are given in the Figure \ref{fig:fr_1E-10_constant}.
+The orange curve is the error versus the number of phase $k$.
+The precision setting of the computation is $10^{-10}$ but the error is much bigger (at least $10^{-3}$).
+This error can be related to the theoretical approximation error of the PH fitting, but also the error of computation of the engine.
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/firstRejuvenation/distance_1E-10_constant.png}
+		\end{center}
+		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$.
+ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference.}
+		\label{fig:fr_1E-10_constant}
+	\end{figure}
+
+	%\pagebreak
+	\section{Conclusion}
+
+%	CHANGE THIS
+
+	We have presented a reliable method for high-precision analysis of PRISM CTMC models with phase-type distributions, that is, adjusting the termination epsilon by the number of phases.
+However, the large number of phases drastically increases the computation time.
+
+	Using the default setting of precision when doing PH fitting is not reliable at all.
+The relation between the experimental precision and the parameter of the model is not trivial.
+We have presented a sufficient condition to increased the precision while increasing the number of phases.
+
+	For better performance, we suggest usage of more specialized tools that can deal with non-Markovian distributions directly, without phase-type fitting.
+Our PRISM ACTMC extension \footnote{Our PRISM ACTMC extension is not fully completed yet and lacks optimization.
+It will be officially released later, but early development version is available at \href{https://github.com/VojtechRehak/prism-gsmp}{https://github.com/VojtechRehak/prism-gsmp}.} has delivered results with sufficient precision a lot faster.
+
+\iffalse
 \subsection{A Subsection Sample}
@@
 
+\end{thebibliography}
+\fi
 \printbibliography
-
-\end{thebibliography}
 \end{document}

### 2018-07-23 Report/report/paper.tex
nex pdf for my institution paper

@@
 %
-\title{Continuous-Time Markov Chain with Alarms analysis and comparaison of tools \thanks{Supported by organization x.}}
+\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{Supported by organization x.}}
 %
@@
 \begin{abstract}
-	Phase-type fitting remains the only way of modeling non-Markovian distributions within PRISM model checker.
-	When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within reasonable time.
+Phase-type fitting is the advised way of modeling non-Markovian distributions within PRISM model checker.
+When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within a reasonable time.
 We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
@@
 	In this paper, we experimentally evaluate the precision of the result and required computation time of various approaches to analysis of continuous time stochastic models with deterministic transitions (timeouts).
-The obtained results are then compared against results of our extension of PRISM capable of efficiently analyzing CTMC with non-Markovian alarms (ACTMC).
+PH fitting results with PRISM are compared with the results of the models in gsmp PRISM, our extension of PRISM, capable of efficiently analyzing CTMC with non-Markovian alarms (ACTMC).
 
@@
 	%\pagebreak
-	\subsection{Obtaining precise results for reference}
+	\subsection{Obtaining precise results}
 	\label{reference}
@@
 	In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed.
-To achieve this, we have modeled the given D/M/1/10 queue in Oris \cite{Bucci2010}.
-The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our PRISM ACTMC implementation up to at least 14 digits.
+To achieve this ground truth, we have modeled the given D/M/1/10 queue in Oris \cite{Bucci2010}.
+The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our PRISM ACTMC with termination epsilon $10^{-20}$ implementation up to at least 14 digits.
 Hence, our tool can be considered a trustworthy reference with precision of $10^{-14}$.
@@
 	%\pagebreak
-	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
+	\subsection{Default parameters}
 	\label{default_absolute}
 
-	First, we used the PRISM default absolute termination epsilon $\epsilon = 10^{-6}$.
-The results are shown in Figure \ref{fig:distance_constant_standard_constant_kappa}.
+	First, we used the PRISM with its default parameter setting.
+The results for increasing $k$ are shown in Figure \ref{fig:distance_constant_standard_constant_kappa}.
 For this $\epsilon$, the obtained results are arguably insufficient.
 Increasing $k$ does little to improve the precision, and only up to about $k \leq 50$, at which point increasing $k$ further starts making the precision worse.
+The reason is that PRISM has a parameter "Termination epsilon" that is set to $10^{-6}$ by default.
+This parameter specifies the precision of certain computation steps of PRISM.
+Increasing $k$ rises the number of states, hence the number of computation steps.
+This yields to increasing the overall error.
 
@@
 		\begin{center}
-			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-6/distance_constant_1E-6.png}
+			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=12cm, clip]{../picture/New_model/1E-6/distance_constant_1E-6.png}
 		\end{center}
@@
 	For much lower $\epsilon = 10^{-10}$, the precision of the result improves.
-However, for higher $k$ the precision continues to deteriorate like in Section \ref{lowering}.
+However, for higher $k$ the precision continues to deteriorate like in Section \ref{default_absolute}.
 The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.
@@
 	%\pagebreak
-	\subsection{Adjusting epsilon $\epsilon = 10^{-10}$ to $k$}
+	\subsection{Adjusting epsilon according to $k$}
 	\label{adjusting}
@@
 What's more, the phase-type fitting results now seem to converge towards the reference steadily as $k$ increases.
-This indicates that this approach is correct, and that the reference is trustworthy.
+This indicates that this approach is correct, and that our ground truth is correct.
 
@@
 This is shown in Figure \ref{fig:performance_dynamic}.
-Note that even though Storm is one of the fastest available tools, it still struggles to deliver good precision within reasonable time.
-The computations all ran on the same virtual machine under same conditions\footnote{Running in a virtual machine might have reduced the performance.
+Note that even though Storm is one of the fastest available tool, it still struggles to deliver good precision within reasonable time.
+All the computations ran on the same virtual machine under same conditions\footnote{Running in a virtual machine might have reduced the performance.
 The virtual machine we used is available at the \href{http://www.stormchecker.org/documentation/vm/vm.html}{Storm website}.}.
@@
 	We can observe similar results in terms of lack of precision on another model Figure \ref{fig:fr_1E-10_constant}.
-The precision must also depend on the PH fitting parameter k in this model.
+The precision must also depend on the PH fitting parameter $k$ in this model.
 Here we went through difficulties related to the methods used by the engine in Prism.

### 2018-07-24 Report/report/paper.tex
last modification of report, almost ready!

@@
 %
-\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{Supported by organization x.}}
+\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{Thanks t}}
 %
@@
 %
-\author{Thomas Mari\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Thomas Mari\inst{1,2}}%\orcidID{0000-1111-2222-3333}}
 %
@@
 Masaryk University, Botanická 68A, 602 00 Brno-Královo Pole, Czech republic
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
+\email{thomas.mari@ens-rennes.fr}\\
+\url{http://perso.eleves.ens-rennes.fr/people/thomas.mari/}
+}
 %
@@
 \begin{abstract}
-Phase-type fitting is the advised way of modeling non-Markovian distributions within PRISM model checker.
-When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within a reasonable time.
+For the analysis of ACTMC, Phase-type fitting is the advised way of modeling non-Markovian distributions within PRISM model checker.
 We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
-Lastly, we hint at an entirely different (and arguably better) approach to handling non-Markovian distributions.
+We aim to compare Phase-type fitting with other approaches that handle directly the non-Marlovian distributions in term of efficiency and precision.
 
@@
 
-\keywords{PRISM model checker \and CTMC \and deterministic timeout \and phase-type distribution \and modeling \and analysis.}
+\keywords{PRISM model checker \and CTMC \and deterministic timeout \and phase-type distribution \and ACTMC \and modeling \and analysis.}
 \end{abstract}
@@
 	In this paper, we experimentally evaluate the precision of the result and required computation time of various approaches to analysis of continuous time stochastic models with deterministic transitions (timeouts).
-PH fitting results with PRISM are compared with the results of the models in gsmp PRISM, our extension of PRISM, capable of efficiently analyzing CTMC with non-Markovian alarms (ACTMC).
+PH fitting results with PRISM are compared with the results of the models in GSMP PRISM, our extension of PRISM, capable of efficiently analyzing CTMC with non-Markovian alarms (ACTMC).
 
 %	BIGGER INTRO
-
-	We will go through the theoretical bases needed to understand the contribution. CITE LUBOSH'THESIS
 
@@
 To achieve this ground truth, we have modeled the given D/M/1/10 queue in Oris \cite{Bucci2010}.
-The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our PRISM ACTMC with termination epsilon $10^{-20}$ implementation up to at least 14 digits.
+The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our GSMP PRISM with termination epsilon $10^{-20}$ implementation up to at least 14 digits.
 Hence, our tool can be considered a trustworthy reference with precision of $10^{-14}$.
 
-	I THINK AT THIS POINT OF THE ARTICLE, IT IS NOT OBVIOUS THAT OUR TOOL REFER TO PRISM GSMP 
-	%\pagebreak
+	In the following, we will compare the distance between the SSP of the different approaches.
+This distance is the largest absolute difference between the distribution and the one computed with GSMP PRISM with termination epsilon $10^{-20}$.
+
 	\subsection{Default parameters}
@@
 The results for increasing $k$ are shown in Figure \ref{fig:distance_constant_standard_constant_kappa}.
-For this $\epsilon$, the obtained results are arguably insufficient.
+The obtained results are arguably insufficient.
 Increasing $k$ does little to improve the precision, and only up to about $k \leq 50$, at which point increasing $k$ further starts making the precision worse.
@@
 
+	The last curve "PRISM ACTMC" is our version of PRISM.
+The absolute termination epsilon used is the same, $10^{-6}$.
+We observe that the error is closed to epsilon.
+Which is what we expect from a precision setting.
+
 	\begin{figure}[H]
 		\begin{center}
-			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=12cm, clip]{../picture/New_model/1E-6/distance_constant_1E-6.png}
+			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=10cm, clip]{../picture/New_model/1E-6/distance_constant_1E-6.png}
 		\end{center}
@@
 The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.
+	Lowering the absolute termination increase the range of the PH parameter $k$ where the results are better.
+But for higher $k$, the precision keeps degrading.
+We have to adjust the precision when changing $k$.
+
+	We observe once more that the error for the GSMP PRISM computation is in the range of the absolute termination epsilon.
 
@@
 		\begin{center}
-			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-10/distance_constant_1E-10.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=10cm, clip]{../picture/New_model/1E-10/distance_constant_1E-10.png}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-10/distance_dynamic_1E-10.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=10cm, clip]{../picture/New_model/1E-10/distance_dynamic_1E-10.png}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/New_model/1E-6/performance_dynamic.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=10cm, clip]{../picture/New_model/1E-6/performance_dynamic.png}
 		\end{center}
@@
 	\subsection{Another Model : firstRejuvenation}
+	The firstRejuvenation model \cite{German:2000:PAC:518204} is originally a Stochastic Petri Net (SPN).
+I took it from a benchmark \cite{benchmark} made for evaluating fd-PRISM which is another version of Prism.
+The SPN graph is available in annexe, Figure \ref{fig:SPN_firstRejuvenation}.
+This model represent some production system that can be degraded with time (exponentially distributed).
+When the system is degraded, it can fail and has to be repaired.
+In the same time the system reset at every tic of a clock which put the system in his original state.
 
@@
 		\begin{center}
-			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{../picture/firstRejuvenation/distance_1E-10_constant.png}
+			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=10cm, clip]{../picture/firstRejuvenation/distance_1E-10_constant.png}
 		\end{center}
@@
 It will be officially released later, but early development version is available at \href{https://github.com/VojtechRehak/prism-gsmp}{https://github.com/VojtechRehak/prism-gsmp}.} has delivered results with sufficient precision a lot faster.
+
+	This experimental statement strengthens the conjecture that further heuristics can increase the efficiency of an analysis with a non-Markovian distributions\cite{DBLP:journals/corr/KorenciakKR14}.
+To some extent GSMP-PRISM is challenging the PH fitting approach.
+Hence it could be interesting to compare the efficiency of GSMP-PRISM with the analysis of SPN with the tool Oris.
+
+\subsubsection*{Acknowledgements}
+I would like to thank Vojtech Reh{\'{a}}k, which has been  my supervisor during this internship.
+Also, I thank M\'{a}rio Uhr\'{i}k for his assistance during this internship and our joint contributions and discussions.
 
@@
 \fi
+\section*{Annexe}
 \printbibliography
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[,width=10cm, clip]{../../Model/benchmark/release/firstRejuvenation/firstRejuvenationPIC.png}
+		\end{center}
+		\caption{SPN model of firstRejuvenation. Grey transitions are deterministic (Dirac) transitions. White filled transitions are exponential transitions.}
+		\label{fig:SPN_firstRejuvenation}
+	\end{figure}
 \end{document}

### 2018-07-24 Report/report/preliminaries.tex
last modification of report, almost ready!

We will go through the theoretical bases needed to understand the contribution. For a complete understanding you can refer to the chapter two of this thesis \cite{Korenciak2018thesis}.
\subsection{Time distribution}
The class of models we use is probabilistic continuous time model, which means that the time passed in a state will depend on a time distribution. A time distribution can be depicted by its cumulative distribution function (CDF) $F : \mathbb{R} \rightarrow[0,1]$, $F(t)$ is the probability that the event will happend before the time $t$. The exponential distribution of rate $\lambda$ has a CDF $F(t) = 1 - \exp(-\lambda t)$, it is important to keep in mind that a rate refers to the exponential distribution. The Dirac distribution of timeout $\tau$ has a CDF $F(t) = 
\left\{
	\begin{array}{l}
		0 \text{ if } t < \tau\\
		1\text{ else}
	\end{array}
\right.$. The keyword deterministic is used when referring to so event following a Dirac distribution.
The Erlang distribution can be seen as the distribution of a sequence of $k$ exponential distribution of parameter $\lambda$. Hence, the Erlang distribution has two parameter $k$ and $\lambda$. 
In this paper, time distribution which are not exponential will be called non-Markovian distribution. Hence, a non-Markovian model will refer to a model with non-Markovian distribution.
\subsection{CTMC}
\label{CTMC_def}
A continuous-time Markov chain (CTMC) is a triple $C = (S,Q,s_{in})$, where 
\begin{itemize}
	\item[$\bullet$] S is a finite set of states
	\item[$\bullet$] $Q : S \times S \rightarrow \mathbb{R}_{\geq 0}$ is a matrix of rates such that $\sum_{s' \in S} Q(s,s')  > 0$ for each $s \in S$
	\item[$\bullet$] $s_{in} \in S$ is an initial state
\end{itemize} 
$Q(s,s')$ is the rate of the transition from $s$ to $s'$.
We define the exit rate of state $s$ as $\lambda_s = \sum_{s' \in S} Q(s,s')$

A run of a CTMC $\mathcal{C}$ is an infinite alternating sequence of states and times $\omega = s_0t_0s_1t_1...$ where 
\begin{itemize}
	\item[$\bullet$] $s_0 = s_{in}$
	\item[$\bullet$] $s_i$ is the i-th state
	\item[$\bullet$] $t_i$ is the time spent in $s_i$
\end{itemize}

For each $i \in \mathbb{N}$ \begin{itemize}
	\item[$\bullet$] $t_i$ is choosen randomly according to the exponential distribution with rate $\lambda_{s_i}$
	\item[$\bullet$] $s_{i+1}$ is choosen according to the discrete distribution $\dfrac{Q(s_i,.)}{\lambda_{s_i}}$
\end{itemize}

Without considering the time spent on each state, CTMC works the same way than discrete time Markov Chain. It is interesting to understand why it is difficult to allow non-Markovian distribution. In this case, when available transitions are not exponential, we cannot pick the next state as easily. We will see an extension of CTMC, where we allow at most one non-Markovian at the same time.

\subsection{ACTMC}

%Continuous-Time Markov Chain with Alarms (ACTMC)s. I won't give the formal semantics which might not fit in this paper. 
We can see ACTMC as CTMC with some events called alarms that are enabled in disjoints sets of states and those events has their own timer which is active only when inside the enabled set and happend according to some continuous time distribution. Those alarms works concurrently with the exponential transition seen in the CTMC.

An ACTMC $\mathcal{A}$ is a tuple $(S,Q,s_{in},A,\langle S_a \rangle,\langle P_a \rangle,\langle F_a \rangle)$
where :
\begin{itemize}
	\item[$\bullet$]$(S,Q,s_{in})$ is a CTMC
	\item[$\bullet$] $A$ is a set of alarms
	\item[$\bullet$] $\langle S_a \rangle = (S_a)_{a \in A}$, the set of states where $a$ is enabled
		\begin{itemize}
			\item[$\bullet$] if $a \neq a'$ then $S_a \bigcap S_{a'} = \emptyset$ 
		\end{itemize}
	\item[$\bullet$]$\langle P_a \rangle = (P_a)_{a \in A}$ where $P_a$ is a probability matrix
	\item[$\bullet$]$\langle F_a \rangle = (F_a)_{a \in A}$ where $F_a$ is a cumulative distribution function (CDF) 
\end{itemize}

The operational behavior of an ACTMC is the following. A run of a ACTMC $\mathcal{A}$ is an infinite alternating sequence of states and times $(s_0,\eta_0)t_0(s_1,\eta_1)t_1...$ where 
$s_i$ is the i-th state, 
$t_i$ is the delay in $s_i$, the time spent in $s_i$ and 
$\eta_i$ is the value of the timer, the remaining time for the alarm to ring.We define $S_{off} = S\setminus\bigcup_{a \in A} S_a$ the set of states where no alarms are enabled

The sequence is defined by induction on $i$. For the initialization $s_0 = s_{in}$. $\text{If } s_0 \in S_{off} \text{ then } \eta_0 =\infty \text{. If } s_0 \in S_{a}\text{, then } \eta_0 \text{ is randomly choosen according to }F_a$. For each $i \in \mathbb{N}, t_i$ is choosen randomly according to the exponential distribution $\lambda_{s_i}$. This value might be overwritten during the induction.

Considering the induction, two cases are possible, either the alarm ring ($\eta_i \leq t_i$) or $t_i$ is too short and the alarm doesn't ring.

%CASE 1
If $\eta_i \leq t_i$, the alarm ring. 
$t_i := \eta_i$ the value of delay is overwritten and match the time spent in $s_i$. 
$s_{i+1}$ is chosen according to the discrete distribution $P_a(s_i,.)$. 
If $s_{i+1} \in S_{off}$, then $\eta_{i+1} =\infty$. 
If $s_{i+1} \in S_{a}$, then $\eta_{i+1}$ is randomly chosen according to $F_a$.

%CASE 2
If $\eta_i > t_i$, the alarm does not ring. 
$t_i$ the value of delay remain the same and match the time spent in $s_i$.
$s_{i+1}$ is chosen according to the discrete distribution $\dfrac{Q(s_i,.)}{\lambda_{s_i}}$.
If $s_{i+1} \in S_{off}$, then  $\eta_{i+1} = \infty$.
If $s_{i+1} \in S_{a}$ and $s_{i} \in S_{a}$, then  $\eta_{i+1} =\eta_i - t$.
If $s_{i+1} \in S_{a}$ and $s_{i} \notin S_{a}$, then
$\eta_{i+1}$ is randomly chosen according to $F_a$. 
If the state remain in the set enabled by the alarm, the timer is updated. Otherwise it is reset according to the new enabled set.

\subsection{Steady State Probability}
In a CTMC, it is important to understand the long term behavior of the system. If the CTMC model some production, we want to know the ratio of time it will spend in critical state or the expected efficiency of the system. It is possible to parametrized a CTMC with a reward system. For each state, we affect a reward that is a real number. During a run, we can computed the payoff of the run by adding the reward of each state multiplied by the time spend in the state. To compute a mean payoff we can use the Steady state Probability (SSP) defined as the expected ratio  of time spent on each state.
%let $p(t)$ be the expected distribution at the time $t$. $p_i(t)$ is the i-th component of the distribution, i.e. the probability of the i-th state at the time $t$.$p = (p_i)_{i=1}^{|S|} = (\lim_{t \rightarrow \infty} p_i(t))_{i = 1}^{|S|}$

We will compare the different tools, models and methods considering only the the SSP computation.

\subsection{Phase Type fitting}
Phase Type fitting (PH fitting) is approaching a non-Markovian distribution F with a CTMC, with a special state T, such that the time to reach T approximates F. PH fitting is used for approaching an ACTMC with a CTMC.

To obtain analysis on ACTMC, we use PH fitting to create CTMC from ACTMC, and analyse those CTMC, then we deduce results on the ACTMC.  The motivation is that PRISM or Storm can use CTMC and not ACTMC. Figure \ref{fig:simple_actmc} and figure \ref{fig:simple_ctmc} are a toy example of the PH fitting of a simple ACTMC $\mathcal{A} = (\{A,B\},
\begin{bmatrix}
	0.5       & 0 \\
	2       & 1 
\end{bmatrix}
,A,\{A\},
\begin{bmatrix}
1       & 0
\end{bmatrix}
,\{d\})$ with PH parameter $k$. The created CTMC is $\mathcal{C} = (\{A,B,1,2,...,k-1,B\},
\begin{bmatrix}
0       & \lambda_{1,k} 	& 0		& 0		& ...		& 0\\
0       & 0 	& \lambda_{2,k}		& 0		& ...		& 0\\
0       & 0 	& 0		& \lambda_{3,k}		& ...		& 0\\
0       & 0 	& 0		& 0		& ...		& 0\\
...       & ... 	& ...		& ...		& ...		& \lambda_{k,k}\\
0       & 0 	& 0		& 0		& 0		& 0
\end{bmatrix}
,A)$

	\begin{figure}
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.80cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[state] (s0)                    {$S$};
		\node[state]         (sn) [right of=s0]       {$T$};
		\path[->, dashed]
		(s0) edge 	node {$F$} (sn);
		\path[->]
		(s0) edge [loop left]	node {0.5} (s0)

		(sn) edge [bend left]	node {2} (s0)
		edge [loop right]	node {1} (sn);			
		\end{tikzpicture}
		\caption{Model of a simple ACTMC $\mathcal{A}$, $F$ is a non-Markovian distribution.}
		\label{fig:simple_actmc}
	\end{figure}

	\begin{figure}
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.80cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[state] (s0)                    {$S$};
		\node[state]         (s1) [right of=s0] {$1$};
		\node[state]         (s2) [right of=s1] {$2$};
		\node[state,draw=none]         (s4) [right of=s2]       {$...$};
		\node[state]         (sw) [right of=s4,fill=white,text=black]       {$k-1$};
		\node[state]         (sn) [right of=sw]       {$T$};

		\path[->]  
		(s0) edge	node {$\lambda_{k,1}$} (s1)
			edge [loop above]	node {0.5} (s0);
		\path[->]

		[->]
		(s1) edge	node {$\lambda_{k,2}$} (s2)
			edge [loop above]	node {0.5} (s1);
		\path[->]

		(s2) edge   node {$\lambda_{k,3}$} (s4)
			edge [loop above]	node {0.5} (s2);
		\path[->]

		(s4) edge   node {$\lambda_{k,k-1}$} (sw)
			edge [loop above]	node {0.5} (s4);
		\path[->]

		(sw) edge   node {$\lambda_{k,k}$} (sn)
			edge [loop above]	node {0.5} (sw);
		\path[->]

		(sn) edge [bend left]	node {2} (s0)
		edge [loop right]	node {1} (sn);
		\end{tikzpicture}
		\caption{Model of a CTMC obtain by PH fitting of the ACTMC figure \ref{fig:simple_actmc}.}
		\label{fig:simple_ctmc}
	\end{figure}
In the case F is a Dirac of parameter $t$, we can set $\lambda_{i,k} = k/t$ for all $i$.
In order to deduce the SSP of Figure \ref{fig:simple_actmc}, we will add the SSP of Figure \ref{fig:simple_ctmc}. The sum of the states $\{A,1,2,...,k-1\}$ will be the probability of the state $S$ in the ACTMC. The probability of the state $T$ in the ACTMC will be the probability of the state $T$ in the CTMC. In Fact, Erlang($k$,$k/t$) is converging to Dirac($t$). This result is the key to Phase-Type deterministic timeouts.

### 2018-07-24 Report/report/related_work.tex
last modification of report, almost ready!

There are various tools and models in the area of probabilistic verification, especially in the analysis of non-Markovian Model. One of those model is stochastic Petri Nets. Oris is a tool for the analysis of stochastic Petri nets \cite{Bucci2010}. Oris allows to analyze Petri net with plenty of time distributions for each event such as exponential, Dirac, Uniform or instant. The expressiveness is sufficient to work on Petri nets that are equivalent to an ACTMC. This tool compute the Steady states probability as well as well as the transient state probability which is state probability at a given time.

A less expressive model is the CTMC defined in Subsection \ref{CTMC_def}, PRISM\cite{KNP11} and Storm \cite{DBLP:journals/corr/DehnertJK017} are both well known tools to analyze CTMC. The engine of those tools are quite efficient for analysis due to the memoryless property of the exponential distribution. Phase-type (PH) approximation can be used to approach a non-Markovian model. The downside of PH approximation is the increase of the number of states which can slow down the process of analysis.  PH Fitting can be challenging depending on the PH distribution\cite{DBLP:journals/corr/KorenciakKR14}.
There is kinds of distributions which requires a lot of phases to be accurately approached by PH fitting. One of those distribution is a shifted exponential distribution, which can be seen as a sequence of a deterministic timeout and a exponential distribution. The motivation of using those distribution is to depict better some events like transmissions that can't happened immediately due to physical limits.

There are automatic tools that do the Phase-Type Fitting like HyperStar \cite{10.1007/978-3-642-40725-3_13}. The power of this tools is to work on real dataset. According the system you want to model it is indeed practical to use real data such that the model depict more precisely the system.

An alternative of PH-approximation is to work directly with a d-CTMC which is a CTMC plus deterministic distribution. This paper \cite{DBLP:journals/corr/BaierDKKR17} depict an efficient approach to analyze ACTMC with distributions where phase-type increase significantly the number of states with reasonable precision. Those distributions are amongst shifted exponential distribution and fixed-delay distribution.

A different objective on the analysis of non-Markovian model is to synthesize optimal parameter. We can add a reward system on the model and computed the optimal parameter, like a timeout on some transitions such that the mean-payoff is $\epsilon$-optimal \cite{DBLP:journals/corr/BaierDKKR17}. The mean-payoff can be seen as the average long term efficiency of the system.

### 2018-07-24 Report/report/paper.tex
last modif on institution paper

@@
 %
-\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{Thanks t}}
+\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{This paper has been written in the context of my internship at the Faculty of Informatics with Vojtech Reh{\'{a}}k at the Masaryk University}}
 %
@@
 %
-\authorrunning{F. Author et al.}
+\titlerunning{ACTMC analysis and comparison of tools}% Part of RIGHT running header
+\authorrunning{Thomas Mari}
 % First names are abbreviated in the running head.
@@
 corresponding to the data shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}.
-The computation of our PRISM ACTMC is constant in regards to $k$ because it does not use phase-type fitting.
+The computation of our PRISM ACTMC is constant in regard to $k$ because it does not use phase-type fitting.
 }
@@
 	For better performance, we suggest usage of more specialized tools that can deal with non-Markovian distributions directly, without phase-type fitting.
-Our PRISM ACTMC extension \footnote{Our PRISM ACTMC extension is not fully completed yet and lacks optimization.
+Our GSMP PRISM extension \footnote{Our GSMP PRISM extension is not fully completed yet and lacks optimization.
 It will be officially released later, but early development version is available at \href{https://github.com/VojtechRehak/prism-gsmp}{https://github.com/VojtechRehak/prism-gsmp}.} has delivered results with sufficient precision a lot faster.
@@
 To some extent GSMP-PRISM is challenging the PH fitting approach.
-Hence it could be interesting to compare the efficiency of GSMP-PRISM with the analysis of SPN with the tool Oris.
+Hence, it could be interesting to compare the efficiency of GSMP-PRISM with the analysis of SPN with the tool Oris.
 

### 2018-07-24 Report/report/preliminaries.tex
last modif on institution paper

@@
 The class of models we use is probabilistic continuous time model, which means that the time passed in a state will depend on a time distribution.
-A time distribution can be depicted by its cumulative distribution function (CDF) $F : \mathbb{R} \rightarrow[0,1]$, $F(t)$ is the probability that the event will happend before the time $t$.
+A time distribution can be depicted by its cumulative distribution function (CDF) $F : \mathbb{R} \rightarrow[0,1]$, $F(t)$ is the probability that the event will happen before the time $t$.
 The exponential distribution of rate $\lambda$ has a CDF $F(t) = 1 - \exp(-\lambda t)$, it is important to keep in mind that a rate refers to the exponential distribution.
@@
 We can see ACTMC as CTMC with some events called alarms that are enabled in disjoints sets of states and those events has their own timer which is active only when inside the enabled set and happend according to some continuous time distribution.
-Those alarms works concurrently with the exponential transition seen in the CTMC.
+Those alarms work concurrently with the exponential transition seen in the CTMC.
 
@@
 $\eta_{i+1}$ is randomly chosen according to $F_a$. 
-If the state remain in the set enabled by the alarm, the timer is updated. Otherwise it is reset according to the new enabled set.
+If the state remain in the set enabled by the alarm, the timer is updated. Otherwise, it is reset according to the new enabled set.
 

### 2018-07-24 Report/report/related_work.tex
last modif on institution paper

@@
 PH Fitting can be challenging depending on the PH distribution\cite{DBLP:journals/corr/KorenciakKR14}.
-There is kinds of distributions which requires a lot of phases to be accurately approached by PH fitting.
-One of those distribution is a shifted exponential distribution, which can be seen as a sequence of a deterministic timeout and a exponential distribution.
-The motivation of using those distribution is to depict better some events like transmissions that can't happened immediately due to physical limits.
+There are kinds of distributions which require a lot of phases to be accurately approached by PH fitting.
+One of those distributions is a shifted exponential distribution, which can be seen as a sequence of a deterministic timeout and a exponential distribution.
+The motivation of using those distributions is to depict better some events like transmissions that can't happen immediately due to physical limits.
 

### 2018-07-24 Report/report/paper.tex
institution final version

@@
 %
-\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{This paper has been written in the context of my internship at the Faculty of Informatics with Vojtech Reh{\'{a}}k at the Masaryk University}}
+\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{This paper has been written in the context of my internship at the Faculty of Informatics with Vojt\v{e}ch \v{R}eh{\'{a}}k at the Masaryk University}}
 %
@@
 \subsubsection*{Acknowledgements}
-I would like to thank Vojtech Reh{\'{a}}k, which has been  my supervisor during this internship.
+I would like to thank Vojt\v{e}ch \v{R}eh{\'{a}}k, which has been  my supervisor during this internship.
 Also, I thank M\'{a}rio Uhr\'{i}k for his assistance during this internship and our joint contributions and discussions.
@@
 \fi
-\section*{Annexe}
+
 \printbibliography
